\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 22.00 – summary\_guided\_gpt/t1626\_gpt.txt}  \label{ex:f2_pos_017}
I ’ve been feeling lonely for about 4–5 \textbf{years} now.
It used to feel like this heavy, constant \textbf{thing} I was dragging around.
I still feel lonely, but over the last six \textbf{months} I ’ve started \textbf{coping} a bit better, and I \textbf{wanted} to \textbf{share} what ’s \textbf{helped} me, in case it \textbf{helps} someone else too.
One \textbf{big} \textbf{thing} was focusing on small, positive \textbf{social} interactions instead of chasing some perfect \textbf{friend} group or \textbf{relationship}.
A short, pleasant chat with a coworker, a barista remembering my order, a quick online conversation that doesn't \textbf{end} in drama – I started counting those as “ wins ” instead of dismissing them as meaningless.
It \textbf{made} me feel less invisible and a bit \textbf{more} confident.
I also started doing \textbf{more} \textbf{things} alone that I genuinely \textbf{enjoy}, not because they ’d \textbf{make} me \textbf{more} “ interesting ” or \textbf{help} me \textbf{meet} people, but just because they feel \textbf{good} in themselves.
That shift \textbf{took} a \textbf{lot} of pressure off hobbies.
It ’s easier to keep going when the reward is built-in, not dependent on whether I \textbf{make} a \textbf{friend}.
Another \textbf{hard} lesson was cutting off people who weren't really there for me.
Keeping “ \textbf{friends} ” who constantly flake, ignore you, or \textbf{only} show up when it ’s convenient just \textbf{made} me feel \textbf{more} alone.
Letting go \textbf{hurt}, but it also \textbf{made} space for the \textbf{idea} that there are so \textbf{many} people in the world, and I don't have to cling to the ones who don't \textbf{treat} me well.
Rejection still sucks.
But I realized that \textbf{avoiding} it doesn't save me from loneliness – it just guarantees it.
Changing my mindset has been slow and uncomfortable, and it hasn't “ cured ” my loneliness, but it ’s \textbf{made} it \textbf{more} bearable.
I feel a little braver about putting myself out there, and that ’s something.

% matched lemmas: avoid, big, cope, end, enjoy, friend, good, hard, help, hurt, idea, lot, make, many, meet, month, more, only, relationship, share, social, take, thing, treat, want, year
\end{textsample}
