\begin{textsample}{POS Dim 2 – human – Score 24.00 – human/t2451\_human.txt}  \label{ex:f2_pos_024}
A few days ago I \textbf{broke} up with my lover, it was very confusing for me to decide how to feel, I didn't \textbf{cry}, but I felt some \textbf{kind} of \textbf{pain} in my chest that I couldn't quite identify.
He was my first, I never was a \textbf{girl} who \textbf{believes} in \textbf{love}, having so \textbf{much} sexual trauma along with \textbf{parents} in a bad marriage, \textbf{left} me denying that \textbf{love} is even real.
We \textbf{met} online 5 \textbf{years} ago so we \textbf{grew} up from being teenagers to \textbf{young} adults together, he admitted his feelings for me last April, it was then I realized how \textbf{much} effects he has on me and how I ’ve never felt like this with any other \textbf{guy}.
I knew this day when we would \textbf{break} up will come, I just didn't expect it to be so soon.
The moment of silence that followed \textbf{made} me realize how lonely my life has my life recently been.
In the 11th grade I \textbf{lost} my \textbf{best} \textbf{friends} of 6 \textbf{years}, back then I felt lonely and devastated but my family had my back, we went to trips and watched movies together.
Me, my \textbf{mom} and my two brothers.
However this changed, quickly.
I don't even remember what happened, we just aren't \textbf{spending} as \textbf{much} \textbf{time} together and everything started to feel \textbf{more} and \textbf{more} formal.
It \textbf{makes} me feel so sad when my therapist ask me to try and \textbf{spend} \textbf{time} with my family, not knowing how to tell her that it ’ll never be the \textbf{same} anymore.
I just \textbf{find} both \textbf{pain} and comfort in my loneliness, I \textbf{want} to \textbf{get} to know people and to listen for other point of views.
But what if I \textbf{get} \textbf{hurt} again?
Every \textbf{relationship} will eventually come to an \textbf{end}, how do I know this \textbf{end} won't \textbf{hurt} me?

% matched lemmas: believe, break, cry, end, find, friend, get, girl, good, grow, guy, hurt, kind, leave, lose, love, make, meet, mom, more, much, pain, parent, relationship, same, spend, time, want, year, young
\end{textsample}
