\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 22.00 – summary\_guided\_gpt/t1785\_gpt.txt}  \label{ex:f2_pos_018}
I feel like I ’ve \textbf{spent} my \textbf{whole} life standing just outside of everyone else ’s circle.
It started in grade \textbf{school}.
My classmates didn't talk to me unless they had to, and even some teachers acted like I wasn't there.
The \textbf{only} person who \textbf{treated} me like a real \textbf{human} being was the cleaning lady, who was \textbf{kind} and actually spoke to me.
That pretty \textbf{much} set the tone for everything that came after.
I tried to \textbf{make} \textbf{friends} in childhood, in my teens, and later at university, but everything stayed on the surface.
People would chat with me in class or in group projects, but they never actually included me in anything.
No one invited me to any graduation parties, and nobody came to mine.
It was like I was always “ nice enough to talk to, ” but never someone they \textbf{thought} to actually \textbf{spend} \textbf{time} with.
Romantic stuff hasn't gone anywhere either.
On the rare occasions someone showed \textbf{interest}, it fizzled out fast.
I ’ve been ghosted after a few \textbf{dates} \textbf{more} than once.
It ’s like as soon as someone \textbf{gets} a slightly closer look, they decide I ’m not worth \textbf{sticking} around for.
Even therapy hasn't really worked out.
One therapist \textbf{ended} \textbf{things} after about five sessions, and another never even scheduled a second one.
That \textbf{hurt} in a \textbf{different} \textbf{way}, like even the people whose job it is to listen and \textbf{help} don't really \textbf{want} to \textbf{deal} with me.
My \textbf{relationships} with family and coworkers are the \textbf{same} : polite, functional, but shallow.
I try to connect, but it never seems to go anywhere deeper.
Over \textbf{time}, I ’ve gone pretty numb to it.
I just expect to be ignored now, and I ’m actually surprised when someone doesn't overlook me.
At this point, my \textbf{only} real \textbf{friends} are my \textbf{parents}.
I ’m grateful for them, but it ’s \textbf{hard} not to feel like that says something about me that no one else ever really chooses me.

% matched lemmas: date, deal, different, end, friend, get, hard, help, human, hurt, interest, kind, make, more, much, only, parent, relationship, same, school, spend, stick, thing, think, time, treat, want, way, whole
\end{textsample}
