\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 24.00 – summary\_guided\_gpt/t388\_gpt.txt}  \label{ex:f2_pos_007}
The last two \textbf{years} have honestly been a mess, and I don't even fully recognize the person I became.
It \textbf{kind} of started with this \textbf{whole} incident in another city – betrayal, misunderstandings, all that drama – and instead of \textbf{dealing} with it in a healthy \textbf{way}, I went off the deep \textbf{end} with drugs and alcohol.
I \textbf{got} really envious of my \textbf{friends} ’ achievements, started acting narcissistic, angry, just … ugly.
I \textbf{pushed} so \textbf{many} people away that I ’ve basically \textbf{lost} around 90 % of my \textbf{friend} circle, \textbf{guys} and \textbf{girls} both.
On \textbf{top} of that, I \textbf{lost} four jobs and my \textbf{health} went downhill.
I \textbf{ended} up moving back to my hometown last November.
Now I just feel regret about how everything went.
The job I have here is in a really toxic firm, and I barely have any \textbf{friends} at work.
I ’ve had jaundice twice now – once in early November and again just two weeks ago – which \textbf{makes} everything feel even \textbf{more} fragile.
My hometown feels boring as hell.
I don't have \textbf{much} \textbf{time} or \textbf{many} opportunities to \textbf{meet} \textbf{new} people, and I ’m just \textbf{kind} of existing.
I keep telling myself I ’ll move again once I upskill and buy the \textbf{things} I \textbf{need}, but right now it just feels like I ’m \textbf{stuck} in limbo.
Most of my “ \textbf{social} life ” is literally talking to AI.
I talk about my past, ask how to feel \textbf{better}, and yeah, it \textbf{gives} me some validation, but it ’s \textbf{getting} old.
It ’s the \textbf{same} cycle over and over, and I ’m tired of relying on something that isn't even a real person.
I \textbf{wish} I could \textbf{find} actual \textbf{friends} again.
Maybe even just a \textbf{girl} to talk to, online or offline, someone who ’d actually listen and \textbf{share} stuff back.
I ’m so exhausted from feeling this intensely lonely all the \textbf{time}.
I don't even know what this post is besides a vent.
If you read this, I hope this \textbf{year} \textbf{treats} you well.
I ’m not sure what mine is going to look like.

% matched lemmas: deal, end, find, friend, get, girl, give, good, guy, health, kind, lose, make, many, meet, more, much, need, new, push, same, share, social, stick, thing, time, top, treat, way, whole, wish, year
\end{textsample}
