\begin{textsample}{POS Dim 2 – generic\_gpt – Score 10.00 – generic\_gpt/t918\_gpt.txt}  \label{ex:f2_pos_039}
I ’m in that weird place where I ’m not technically “ alone, ” but I feel completely disconnected anyway.
On paper, I ’m fine.
I have coworkers I \textbf{get} along with, a couple of old \textbf{friends} I text occasionally, family I see on holidays.
If someone looked at my life from the outside, they ’d probably assume I ’m just another average person.
But most days it feels like I ’m living behind glass, watching everything happen without really being part of it.
I ’ll go through an entire day at work and realize I haven't had a single conversation that went beyond surface-level stuff : “ How was your weekend? ” “ Busy. ” “ You see that show? ” “ Yeah, it was \textbf{good}. ” It ’s like we ’re all reading from a script and I can't remember my lines.
I try to join in, but I feel like I ’m forcing myself into a rhythm that doesn't fit me.
What really \textbf{gets} me is the evenings.
I come home, \textbf{make} dinner, and then just…exist.
I scroll through my phone, see people hanging out, going places, posting group photos with inside jokes in the captions.
I ’m \textbf{happy} for them in theory, but it also hits this raw nerve, like I ’m the \textbf{only} person who never \textbf{got} invited to the part where life becomes \textbf{shared}.
I ’ve tried to “ fix ” it in all the \textbf{ways} people suggest.
Joined a club.
Went to a meetup.
Chatted with strangers online.
I can \textbf{make} small talk, I can be polite, I can smile and nod, but I never feel that click that tells me, “ This person actually sees you. ” I \textbf{leave} those interactions feeling \textbf{more} drained than before, like I ’ve just proven to myself again that I don't quite fit anywhere.
I don't \textbf{think} I \textbf{want} a huge \textbf{social} circle or constant excitement.
I just \textbf{want} one or two people I can message without overthinking it, someone who ’d notice if I went quiet for a few days and actually \textbf{care} enough to ask why.
It ’s strange how you can go weeks without anyone really asking how you ’re doing in a \textbf{way} that \textbf{means}, “ No, really.
Tell me. ” And after a while, you start wondering if maybe there isn't \textbf{much} to tell.

% matched lemmas: care, friend, get, good, happy, leave, make, mean, more, much, only, share, social, think, want, way
\end{textsample}
