\begin{textsample}{POS Dim 2 – generic\_gpt – Score 11.00 – generic\_gpt/t1446\_gpt.txt}  \label{ex:f2_pos_037}
I don't really know how to talk about this in my real life, so I ’m dumping it here instead.
Lately I ’ve been feeling this weird mix of invisible and too visible at the \textbf{same} \textbf{time}.
Invisible because no one really seems to notice when I go quiet, stop replying, or just disappear from group chats for days.
Too visible because when I ’m actually around people, I feel hyper-aware of every word I say, like I ’m performing a version of myself that I don't even like.
I technically have “ people ” in my life—co‑workers, a few old \textbf{friends} from \textbf{school}, family I see on holidays—but it all feels surface level. \textbf{Lots} of “ how ’s work? ” and “ what ’ve you been up to? ” and then the conversation dies if I try to say anything real.
It ’s like everyone else is busy living their lives and I ’m this side character who occasionally walks through the background.
What messes with my head is that from the outside I probably don't look lonely.
I show up to work, I reply to messages ( eventually ), I post the occasional meme.
I know how to be “ fine ” in public.
But then I go home, close the door, and it ’s just this heavy silence.
I \textbf{end} up scrolling for hours, not because it ’s fun, but because it distracts me from how empty everything feels.
The worst part is the feeling that I ’m \textbf{hard} to actually know.
Not because I ’m deep or complicated, but because somewhere along the line I stopped \textbf{believing} people \textbf{wanted} to know me.
So I started editing myself down—cutting out the parts that feel “ too \textbf{much}, ” too needy, too intense.
Now I ’m \textbf{left} with this watered-down version that ’s easier to tolerate but \textbf{harder} to connect with.
I keep \textbf{thinking}, “ If I disappeared, how long would it \textbf{take} anyone to actually notice? ” And I don't \textbf{mean} that in a dramatic, self-harm way—it ’s \textbf{more} like a practical question my brain won't stop asking.
How \textbf{many} missed calls?
How \textbf{many} unread messages?
Would there even be any?
I don't really have a point to this.
I ’m just tired of feeling like I ’m watching my own life from the outside, like I ’m a guest in everyone else ’s story and never the main character in my own.

% matched lemmas: believe, end, friend, hard, leave, lot, many, mean, more, much, same, school, take, think, time, want
\end{textsample}
