\begin{textsample}{POS Dim 2 – human – Score 26.00 – human/t1225\_human.txt}  \label{ex:f2_pos_021}
I have hobbies, a side hustle, and keep myself busy with my studies.
But when im not busy with these \textbf{things}, i feel empty.
I feel so lonely.
I crave for some \textbf{kind} of \textbf{emotional} connection with someone.
I have \textbf{friends} but i never open up with them.
I have trust \textbf{issues}.
I listen to their rants, vents, and their random stories and thoughts but im having a \textbf{hard} \textbf{time} doing the \textbf{same} for them.
Maybe because i know they wouldnt \textbf{understand} me and i live a double life.
I keep a \textbf{lot} of secrets because of my strict religion.
And \textbf{growing} up, i was constantly shamed for almost everything i do.
I \textbf{hate} that i feel such a complex person.
I \textbf{wish} i was normal.
Ever since I had my first heartbreak, i have a \textbf{hard} \textbf{time} being alone.
I always crave to be \textbf{loved}.
Im always talking to some \textbf{guy} and usually it doesnt last.
I had 2 boyfriends within 3 \textbf{years} and each lasted \textbf{only} for a \textbf{year}.
I 'm probably addicted to male attention atp. ( And also, im not allowed to have a bf lol. ) Im probably addicted because \textbf{guys} are so \textbf{good} at pretending to \textbf{care} which i really crave for.
At \textbf{least} i \textbf{got} a safe space to overshare my life TEMPORARILY.
If it doesnt work out I can just \textbf{find} someone else to talk to who can occupy the void in me and repeat.
Ive \textbf{given} up on \textbf{dating} genuinely as well, with all the \textbf{dating} rules on \textbf{social} media like"dont double text","dont show too \textbf{much} affection, theyll \textbf{lose} attraction"etc.
Idek if genuine \textbf{love} is possible these days.
But if \textbf{love} does exist, i dont \textbf{think} i 'll ever \textbf{experience} it.
I dont \textbf{want} \textbf{advice} or anything, i just wanna let feelings out.

% matched lemmas: advice, care, date, emotional, experience, find, friend, get, give, good, grow, guy, hard, hate, issue, kind, least, lose, lot, love, much, only, same, social, thing, think, time, understand, want, wish, year
\end{textsample}
