\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 25.00 – summary\_guided\_gpt/t1371\_gpt.txt}  \label{ex:f2_pos_005}
I feel like I ’m living this weird split life where, on paper, \textbf{things} look almost ideal, and yet I ’m crushed by one missing piece.
I ’m in my 30s now.
I somehow managed to buy a \textbf{house} even though I don't \textbf{make} \textbf{much}.
I have a handful of long-term \textbf{friends} who are genuinely \textbf{good} people.
My job is stable and really aligned with my values, which I know is rare.
I ’ve also \textbf{got} some significant \textbf{health} \textbf{problems}, but I ’m very motivated about managing them and I ’m doing the \textbf{best} I can there.
The \textbf{problem} is that I don't have a romantic partner, and that emptiness feels like it eclipses everything else.
Love has always been a huge \textbf{thing} for me.
My first \textbf{love} was when I was 12, and it was intense in a \textbf{way} that still echoes 20 \textbf{years} later.
It ’s like that \textbf{experience} hard-wired me to \textbf{need} that \textbf{kind} of connection.
I don't \textbf{mean} “ sort of \textbf{want} it, ” I \textbf{mean} it feels like a core \textbf{emotional} \textbf{need} that just never stops aching.
I ’ve been in therapy.
I use DBT skills.
I \textbf{spend} \textbf{time} with my \textbf{friends}, I do \textbf{things} I \textbf{enjoy}, I try to \textbf{build} a meaningful life in every \textbf{way} I can.
My therapist and I have gone over and over whether there ’s some other imbalance or \textbf{issue} I ’m missing, and we keep coming back to the \textbf{same} conclusion : this \textbf{need} for romantic companionship is just extremely strong for me.
And nothing I do seems to touch the \textbf{depression} that comes from that absence.
I don't seem \textbf{able} to “ fill the gap ” with other forms of connection, no matter how \textbf{hard} I try or how \textbf{much} I intellectually \textbf{understand} that I ’m not supposed to rely on one \textbf{thing} for happiness.
I ’m feeling desperate and stuck.
Has anyone else been here and \textbf{found} anything that actually \textbf{helped}?
Any perspectives or approaches I might not have tried yet?

% matched lemmas: able, build, depression, emotional, enjoy, experience, find, friend, get, good, hard, health, help, house, issue, kind, love, make, mean, much, need, problem, same, spend, thing, time, understand, want, way, year
\end{textsample}
