\begin{textsample}{POS Dim 2 – generic\_gpt – Score 11.00 – generic\_gpt/t1709\_gpt.txt}  \label{ex:f2_pos_036}
I ’ve been feeling this weird, heavy \textbf{kind} of loneliness lately that doesn't really fit into any of the usual categories people talk about.
I ’m not totally isolated.
I work, I talk to coworkers, I answer messages in group chats.
On paper I ’m “ connected. ” But it all feels like I ’m playing a role in other people ’s lives instead of actually being in them.
Most of my interactions feel like background noise.
Small talk, memes, work-related stuff, surface-level updates.
I can go days without anyone asking me how I ’m really doing in a \textbf{way} that suggests they actually \textbf{want} to know.
When I try to open up a bit, the conversation either \textbf{gets} redirected or brushed off with a joke.
I \textbf{end} up feeling like I overshared, even if I \textbf{only} said one honest sentence.
What \textbf{makes} it worse is that I used to have people I felt close to.
Not \textbf{many}, but enough that I felt like I had a “ home base ” in the world.
Over \textbf{time}, life just pulled us in \textbf{different} directions.
People moved, \textbf{got} into serious \textbf{relationships}, became busy with \textbf{kids} or careers.
We still “ keep in touch ” in the vaguest sense, but it ’s \textbf{more} like we ’re watching each other ’s lives from the outside rather than living anything together.
I ’ve tried to \textbf{meet} \textbf{new} people, but I ’m at this age where everyone already seems to have their established circle.
I always feel like the extra person tagging along, the one who can be there or not and it wouldn't really change anything.
I ’m present, but not essential.
Replaceable.
The part that really messes with me is how invisible this feels.
From the outside, I probably look fine.
I show up, I smile, I contribute to conversations.
Nobody sees that I go home and just sit in the quiet, scrolling on my phone because I don't know what else to do with myself.
I keep \textbf{wanting} to send a message that just says, “ I feel really alone right now, ” but I don't know who I ’d send it to, or what I ’d even \textbf{want} them to say back.
There ’s this constant ache of \textbf{wanting} to be known, really known, and at the \textbf{same} \textbf{time} feeling like I ’ve forgotten how to let anyone that close.
I ’m not sure if I ’ve \textbf{built} walls or if people just stopped trying to look over them.
Maybe both.
All I know is that I ’m tired of feeling like a side character in my own life.

% matched lemmas: build, different, end, get, kid, kind, make, many, meet, more, new, only, relationship, same, time, want, way
\end{textsample}
