\begin{textsample}{POS Dim 2 – human – Score 22.00 – human/t2287\_human.txt}  \label{ex:f2_pos_029}
I feel really lonely these days, \textbf{big} surprise and my therapist tells me she hears it from \textbf{many} of her clients as well.
I hear it from both sides, I ’ve talked about it with \textbf{women} and male \textbf{friends}, some I ’ve known for 10+ \textbf{years}.
My \textbf{friend} she ’s married and she tells me how lonely she feels, because it ’s \textbf{only} her and her husband.
She \textbf{loves} him and thats her \textbf{best} \textbf{friend} but there ’s still a lack of community for her.
It‘s not an economic \textbf{issue} because there are millionaires I know who feel desperately alone and those living close to near homelessness whom feel alone.
I ’m not here with answers really, I am \textbf{more} genuinely curious with how you all \textbf{cope} with this day-to-day phenomenon.
It feels like I go out of my \textbf{way} to practice integration and community based values everyday, \textbf{understand} compromise.
Focusing my energy on being less \textbf{self} obsessed or hyper individualistic.
I don't feel like it ’s because people are really that bad socially, or people are losers and not working \textbf{hard} enough.
In my opinion, the reality of \textbf{human} connection is : it \textbf{takes} two to tango.
You have to \textbf{give} up a level of uncertainty and control to be apart of any \textbf{relationship} or community.
It ’s a risk, but it feels like we ’ve become like the corporations.
It ’s not worth a risk investment in humanity if it doesn't benefit.
Protecting our inner worlds from any person who may threaten our sense of \textbf{self} and worldview.
When there is one red flag, people jump ship.
I ’m not condoning allowing toxic behavior, but there has to be some leeway for \textbf{humans} to \textbf{make} a mistake or \textbf{take} a risk.
I‘m even a prisoner to this, cutting people off who don't serve me.
Maybe, if I \textbf{gave} it \textbf{more} \textbf{time} the kinks could be rolled out, or we \textbf{find} common ground.
I guess for me it feels like I ’m disposable.
Even when I ’ve \textbf{spent} \textbf{time} to \textbf{make} a career for myself that I ’m proud of.
It feels like a wall or its own separate armor.
They don't \textbf{want} me for me, just what being in proximity to me could \textbf{mean} for them.
I ’m just ranting but hope someone resonates.

% matched lemmas: big, cope, find, friend, give, good, hard, human, issue, love, make, many, mean, more, only, relationship, self, spend, take, time, understand, want, way, woman, year
\end{textsample}
