\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t1761\_gpt.txt}  \label{ex:f2_pos_010}
I ’m 27 and I feel like I ’ve hit a wall in every direction.
My family is tiny and toxic, and I barely speak to them.
I don't have any close \textbf{friends}.
I ’ve basically learned that the \textbf{only} person I can rely on is myself, and even I ’m not doing a \textbf{great} job of holding it together lately.
For \textbf{years}, my two cats were my main \textbf{emotional} \textbf{support}.
They were the \textbf{only} ones who were always there when I came home.
One of them died seven \textbf{months} ago, and I still feel that loss every day.
Now my other cat ’s \textbf{health} is declining, and it feels like the last bit of stability I had is slipping away.
My own \textbf{health} is \textbf{getting} worse too, physically and mentally, but I can't afford proper medical \textbf{care}.
My job pays just enough that I don't qualify for \textbf{help} like food stamps, but not enough to actually live comfortably.
Rent is \textbf{high} even with a roommate, and then there ’s my car payment, insurance, debt, groceries, and vet/medicine bills for my cat.
Every \textbf{month} feels like a balancing act I ’m slowly \textbf{losing}.
On \textbf{top} of that, I ’m \textbf{dealing} with severe OCD, \textbf{depression}, \textbf{anxiety}, and ADHD.
I know I \textbf{need} therapy, meds, maybe even a proper evaluation, but all of that costs money I don't have.
It feels like I ’m \textbf{stuck} in this loop where I can't \textbf{get} \textbf{better} because I ’m poor, and I can't stop being poor because I ’m not well enough to do \textbf{more}.
I don't have a \textbf{support} system.
No family safety net, no partner, no close \textbf{friends}.
I don't have a \textbf{college} degree, and I don't have the money or motivation to go back to \textbf{school}.
I keep \textbf{thinking} about how \textbf{many} people are in \textbf{similar} \textbf{situations}, and how \textbf{much} of life comes down to whether you were born with financial and \textbf{emotional} \textbf{support}.
People don't talk enough about how \textbf{big} a privilege it is to have that from the start.
Some of us are just trying to survive without it, and it ’s exhausting.

% matched lemmas: anxiety, big, care, college, deal, depression, emotional, friend, get, good, great, health, help, high, lose, many, month, more, much, need, only, school, similar, situation, stick, support, think, top, year
\end{textsample}
