\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 22.00 – summary\_guided\_gpt/t1472\_gpt.txt}  \label{ex:f2_pos_020}
I ’m 30, live in rural western PA, financially stable, own my home, and I actually \textbf{love} my job as a field service tech.
On paper, I know I ’m in a \textbf{good} spot.
But I feel incredibly alone.
In 2020 I went through a really traumatic breakup.
My ex cheated on me, \textbf{got} pregnant, and told me I was the father.
I \textbf{believed} her, \textbf{got} attached to the \textbf{idea}, and then a DNA test proved I wasn't.
That \textbf{whole} \textbf{situation} wrecked me.
Since then I ’ve had serious trust \textbf{issues}.
I became bitter, angry, and honestly not a pleasant person to be around.
Because of that, I \textbf{ended} up \textbf{losing} my two \textbf{best} \textbf{friends}.
We had a falling out and they ’ve \textbf{made} it clear they \textbf{want} nothing to do with me anymore.
I ’ve tried to fix it, but they refuse to reconcile.
So now it ’s just…me.
Work and home.
That ’s my \textbf{whole} life. \textbf{Only} in the last \textbf{year} have I started to feel ready to \textbf{date} again.
I ’ve gone on a few \textbf{dates}, but there was no real connection.
I \textbf{struggle} with severe \textbf{social} \textbf{anxiety}, and my job keeps me really busy, so \textbf{meeting} people is \textbf{hard}.
Online \textbf{dating} feels like shouting into the void.
In-person, I freeze up or overthink everything.
I ’m lonely as hell.
I see people my age \textbf{getting} married, having \textbf{kids}, going on trips with \textbf{friends}, and I feel this constant FOMO, like life is passing me by while I ’m \textbf{stuck} on the sidelines.
I just \textbf{want} a \textbf{girlfriend}, someone to \textbf{share} \textbf{things} with, to come home to, to feel like I ’m not doing all of this alone.
I don't really know what I ’m looking for by posting this.
Maybe I just \textbf{needed} to \textbf{get} it off my chest.

% matched lemmas: anxiety, believe, date, end, friend, get, girlfriend, good, hard, idea, issue, kid, lose, love, make, meet, need, only, share, situation, social, stick, struggle, thing, want, whole, year
\end{textsample}
