\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t1709\_gpt.txt}  \label{ex:f2_pos_011}
I ’m 22 and I feel like I ’ve already messed everything up.
I didn't go to \textbf{college}.
I work a low-level customer service job, and every shift just \textbf{makes} me feel like I ’ve already failed at life.
I know I ’m not stupid, but I feel like I have no \textbf{way} to prove I ’m actually smart or capable.
When I look at people my age in university or starting “ real ” careers, I feel like I ’m \textbf{stuck} at the bottom with no ladder.
I \textbf{grew} up mostly with my grandma, and I \textbf{think} that \textbf{kind} of messed with how I connect to people.
I don't really have a solid \textbf{friend} group.
I have people I talk to sometimes, but no one I feel close to.
I overthink every single \textbf{thing} I say.
I replay conversations in my head and cringe at myself.
I feel like I ’m either too quiet or too weird or just … unnecessary.
I \textbf{struggle} a \textbf{lot} with how I see myself.
Some days I feel genuinely pathetic and ugly. \textbf{School} was a nightmare because of ( probably ) undiagnosed ADHD.
I could never focus, I procrastinated everything, I \textbf{avoided} people, and I never \textbf{built} any \textbf{good} habits.
That ’s a \textbf{big} reason I didn't go to \textbf{college}, and part of me is scared that even if I tried now, I ’d just fail again in the \textbf{same} \textbf{ways}. \textbf{Social} stuff drains me.
Going out, going to the gym, just existing around people \textbf{makes} me feel awkward and anxious.
I overthink to the point where I feel “ kinda autistic ” ( not in a joking \textbf{way}, just in how intensely I analyze everything I do or say ).
I feel like everyone can see how uncomfortable I am.
I ’ve been trying to improve.
I ’ve \textbf{lost} some weight, started working out, \textbf{treating} my acne, doing small self-care \textbf{things}.
But it feels like nothing is enough, and that at 22 I ’m already so behind that I ’ll never catch up.
I don't even \textbf{care} that \textbf{much} about being “ successful ” in the traditional sense.
I just \textbf{want} connection.
I \textbf{want} \textbf{friends}.
I \textbf{want} to maybe \textbf{date}.
I \textbf{want} someone I can talk to without feeling like I ’m a burden or some boring, unambitious loser.
I don't really have anyone to talk to about this, which is why I ’m posting.
If anyone has \textbf{advice} on how to \textbf{build} connections from basically zero, or how to \textbf{deal} with feeling this behind and \textbf{broken}, I ’d really appreciate it.

% matched lemmas: advice, avoid, big, break, build, care, college, date, deal, friend, good, grow, kind, lose, lot, make, much, same, school, social, stick, struggle, thing, think, treat, want, way
\end{textsample}
