\begin{textsample}{POS Dim 2 – human – Score 22.00 – human/t2273\_human.txt}  \label{ex:f2_pos_030}
I feel disconnected to my family.
I try to be the loving supportive father and husband.
I \textbf{love} my family but I \textbf{built} a \textbf{lot} of resentment.
Before I \textbf{get} into why I had resentment I should explain a few \textbf{things}.
One my wife and I have been together for 25 \textbf{years} … wow just typing that out feels heavy.
She is chronically ill with \textbf{many} autoimmune \textbf{issues}, including Ehlers danlos syndrome, Reynard syndrome, a spina bifida Oculta, anemia, chronic fatigue syndrome.
IBS.
We have four \textbf{kids} that are living with us 23 15, 13 and eight.
All of them have some form of special \textbf{needs} the older three are \textbf{high} functioning and with Reminders and guidance they can function on their own.
Our \textbf{youngest} is nonverbal autistic level three.
I am a father of four for the last 16 \textbf{years} I have been the sole breadwinner.
For at \textbf{least} the last 5 I have done 90 percent of the cooking and cleaning.
When I ask for \textbf{help} I am asking too \textbf{much}.
If I ask my wife not to sleep till noon and have breakfast or a coffee together I am asking too \textbf{much}.
I feel my purpose is to \textbf{take} \textbf{care} of everything and don't disagree with my wife and don't ask my \textbf{kids} to do anything.
How the \textbf{fuck} did my life \textbf{get} like this?
Work is my vacation.
I feel liked and respected hell my opinions matter at work.
But at home I feel like a glorified servant.
This is not a poor me but a reflection of my thought process.
To feel \textbf{good} mentally I work out 2-3 \textbf{times} a week for \textbf{mental} and \textbf{emotional} \textbf{health}.
So I am not angry or depressed when I \textbf{get} off work I sneak away a quick joint.
I \textbf{want} to be \textbf{happy} without having to relay on weed.
I am not depressed or having suicidal thoughts.
I see no reason for \textbf{self} harm or \textbf{hurting} others.
But I am tired of doing it all.
I am tired of feeling silenced.
Forgive the rant.

% matched lemmas: build, care, emotional, fuck, get, good, happy, health, help, high, hurt, issue, kid, least, lot, love, many, mental, much, need, self, take, thing, time, want, year, young
\end{textsample}
