\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t2089\_gpt.txt}  \label{ex:f2_pos_015}
I ’m 21 and I feel like I ’ve basically lived my \textbf{whole} life on the outside looking in.
I ’ve never had close \textbf{friends}, never had a \textbf{girlfriend}, and most days it feels like I ’m just drifting through life completely invisible.
Lately I ’ve been trying to improve myself physically – working out, \textbf{taking} \textbf{care} of my appearance, that \textbf{kind} of \textbf{thing} – and there ’s been some progress there.
But mentally I ’m a mess.
I have no one I can really talk to about what ’s going on in my head.
The \textbf{only} person I even \textbf{kind} of open up to is my \textbf{mom}, and her \textbf{advice} is always just “ cheer up ” or “ don't \textbf{think} like that. ” I know she \textbf{means} well, but it feels so shallow and doesn't actually \textbf{help}.
Whenever I \textbf{think} about telling someone how I really feel, I immediately feel like a burden.
I don't \textbf{want} to dump my \textbf{problems} on people or \textbf{make} them feel like they have to “ play therapist ” for me.
So I just keep everything inside and it ’s eating at me.
I keep telling myself I \textbf{need} to fix myself before I can expect to have meaningful \textbf{relationships}, but I don't even know where to start.
For those of you who ’ve also had no \textbf{relationships} and \textbf{spent} \textbf{years} feeling invisible, how did you actually \textbf{make} progress?
How did you go from this to something better?
I ’m honestly scared that if this loneliness keeps \textbf{growing}, I might \textbf{end} up \textbf{hurting} myself.
I don't \textbf{want} that.
I \textbf{want} to learn how to be at \textbf{least} somewhat content on my own, and also how to eventually \textbf{build} real connections.
Any \textbf{advice} or personal \textbf{experiences} would \textbf{mean} a \textbf{lot}.

% matched lemmas: advice, build, care, end, experience, friend, girlfriend, grow, help, hurt, kind, least, lot, make, mean, mom, need, only, problem, relationship, spend, take, thing, think, want, whole, year
\end{textsample}
