\begin{textsample}{POS Dim 2 – generic\_gpt – Score 12.00 – generic\_gpt/t2659\_gpt.txt}  \label{ex:f2_pos_032}
I don't really know how to explain this without sounding dramatic, but I feel like I ’m slowly disappearing from everyone ’s life while still being physically present.
On paper I ’m not “ alone. ” I have a job, coworkers who are polite, a couple of old \textbf{friends} I text every now and then, family members who send the occasional “ how are you ” message.
But none of it feels like it actually touches me.
It ’s like I ’m behind glass, watching my own life from the outside.
I go through the motions : wake up, commute, work, scroll on my phone, pretend to laugh at \textbf{things}, come home, eat something random, and then just sit there.
I keep the TV or YouTube on just for background noise so the silence doesn't feel so heavy.
I keep checking my phone hoping someone will message me first, and most of the \textbf{time} it ’s just notifications from apps I don't \textbf{care} about.
When I do talk to people, it feels like I ’m playing a character who ’s \textbf{more} socially acceptable than the real me.
I \textbf{make} small talk, I say “ I ’m fine, ” I ask questions back so they won't notice I ’m not actually \textbf{sharing} anything.
I can't remember the last \textbf{time} I was fully honest with someone about how lonely I feel without worrying they ’d see me as needy or pathetic.
What really messes with my head is that I used to have real connections.
In \textbf{school} and a bit in \textbf{college}, there were people who actually knew me.
Over \textbf{time} everyone drifted away, \textbf{got} partners, moved, \textbf{got} busy.
I know that ’s normal, but it feels like I \textbf{got} \textbf{left} at the train station while everyone else ’s life \textbf{took} off.
I ’m \textbf{stuck} replaying old memories because I don't have \textbf{many} \textbf{new} ones that involve actual closeness.
I ’ve tried to “ fix ” this the \textbf{way} people suggest—joining groups, trying hobbies, being \textbf{more} “ open”—but I always \textbf{end} up feeling like an extra in everyone else ’s story.
People are friendly enough, but it doesn't go deeper.
I \textbf{leave}, go home, and the emptiness hits even \textbf{harder}, like proof that there ’s something about me that just doesn't \textbf{stick} with anyone.
I don't even know what I ’m asking for.
I just \textbf{needed} to put this somewhere, because keeping it in my head all the \textbf{time} is starting to feel like it ’s swallowing me.

% matched lemmas: care, college, end, friend, get, hard, leave, make, many, more, need, new, school, share, stick, take, thing, time, way
\end{textsample}
