\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t1224\_gpt.txt}  \label{ex:f2_pos_014}
I ’m 24 and right now life feels like it ’s caving in from a bunch of directions at once.
I ’ve been \textbf{dealing} with cyclical \textbf{depression}, ADHD, and chronic \textbf{anxiety} for \textbf{years}, but \textbf{things} \textbf{got} worse recently to the point that I had to stop working. \textbf{Losing} that stability has been really scary, and it ’s \textbf{left} me feeling pretty \textbf{lost} and useless.
The \textbf{only} real comfort I have day to day is my two cats.
They ’re my little family and honestly the reason I keep \textbf{pushing} through.
One of them, Azraël, suddenly \textbf{needed} unexpected surgery, and of course it happened right when my \textbf{mental} \textbf{health} and finances were already hanging by a thread.
I don't regret \textbf{getting} him the \textbf{care} he \textbf{needed} for a second, but the bills have hit me \textbf{hard} and I ’m really \textbf{struggling} to keep up.
I feel really uncomfortable and vulnerable even writing this, but I set up a GoFundMe to try to stay afloat.
If anyone is \textbf{able} and willing to \textbf{help}, even a tiny amount, it would \textbf{mean} \textbf{more} than I can put into words.
I completely \textbf{understand} that most people are \textbf{struggling} right now, so please don't feel any pressure or obligation.
If you can't donate, just sending some \textbf{kind} thoughts or \textbf{sharing} a \textbf{kind} word would still \textbf{mean} a \textbf{lot}.
Thank you for reading this and for any \textbf{support} at all, even if it ’s just \textbf{taking} a moment to \textbf{care}.

% matched lemmas: able, anxiety, care, deal, depression, get, hard, health, help, kind, leave, lose, lot, mean, mental, more, need, only, push, share, struggle, support, take, thing, understand, year
\end{textsample}
