\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t1466\_gpt.txt}  \label{ex:f2_pos_013}
I ’m 34 and honestly can't remember the last \textbf{time} I was genuinely \textbf{happy}.
My dad died when I was 17, and from that moment it felt like my own life stopped.
I stepped into the “ \textbf{man} of the \textbf{house} ” role without really \textbf{thinking} about it.
I worked, handed over money, put my own \textbf{interests} and plans on hold so my \textbf{mom} and \textbf{younger} sister would be okay.
For \textbf{years}, that was just my identity : the provider.
Looking back, it feels like that ’s all I ever was to anyone.
Romantic partners, \textbf{friends}, even my own family … it always seemed like they were \textbf{more} interested in what I could do for them than in who I actually am.
I don't remember \textbf{many} moments where I felt seen as a person rather than a resource.
A few \textbf{years} ago I hit some financial hardship and was briefly unemployed.
After everything I had done, my \textbf{mom} and sister basically \textbf{treated} me like I was useless, like I ’d \textbf{lost} my \textbf{only} value.
It was like I became disposable overnight.
That broke something in me.
Now I live alone.
I haven't seen my family in about four \textbf{years}.
We barely speak, and when we do, it ’s shallow and infrequent.
My views on \textbf{love} and marriage are pretty \textbf{much} wrecked.
It ’s \textbf{hard} to \textbf{believe} in those \textbf{things} when your main \textbf{experience} of “ \textbf{love} ” is being \textbf{needed} \textbf{only} as long as you ’re useful.
I ’m \textbf{sharing} this here because I don't really have anyone in my life who \textbf{wants} to \textbf{spend} \textbf{time} with me just to be with me.
I feel like I ’ve \textbf{spent} my \textbf{whole} adult life \textbf{taking} \textbf{care} of others, and somehow \textbf{ended} up completely alone.

% matched lemmas: believe, care, end, experience, friend, happy, hard, house, interest, lose, love, man, many, mom, more, much, need, only, share, spend, take, thing, think, time, treat, want, whole, year, young
\end{textsample}
