\begin{textsample}{POS Dim 2 – human – Score 23.00 – human/t468\_human.txt}  \label{ex:f2_pos_026}
Hi.
First of all, Merry Christmas to you all!
My name 's Hugo, I 'm from Spain, and almost 23 \textbf{years} old.
I don't \textbf{want} to sound thirsty or desperated.
I know that 's such a turn-off.
I just \textbf{want} to \textbf{get} this out my chest.
I \textbf{lost} my job due to \textbf{depression} almost a \textbf{month} ago and started \textbf{taking} meds for it after 15 \textbf{years} of just bearing with everything on my own.
Not very wise of me not asking for \textbf{help} earlier, but who can trust public healthcare nowadays?
Anyways...
I don't feel comfortable \textbf{giving} \textbf{many} details about my life publicly because I \textbf{hate} feeling myself exposed.
I just wanna say I feel completely drained off.
I 've been locked up home for the last three weeks just playing videogames and sleeping.
Not even eating nor \textbf{crying} because I have no energy for it.
I 've never felt myself so alone in my entire life.
I tried everything you can imagine ( and I \textbf{mean} it ) to \textbf{get} to know \textbf{new} people, even if it 's online, but \textbf{meeting} \textbf{new} people is almost \textbf{impossible} nowadays, even \textbf{more} if you 're introverted like me.
It 's not my first period of solitude, but it 's being the worst.
I 've always been such an expressive \textbf{guy} with \textbf{friends}, but \textbf{things} always happen in all groups and they always \textbf{end} up tearing apart.
I had traumatic \textbf{experiences} with old"\textbf{friends}"of mine that led me to adopt a \textbf{more} solitary and sedentary lifestyle five \textbf{years} ago.
I have \textbf{good} \textbf{friends} nowadays, yeah, but we 're all adults and they all have their own \textbf{relationships} and works to \textbf{take} \textbf{care} of.
I 'm just that one \textbf{friend} whose life 's not going as well as theirs.
So...
That 's it.
I don't \textbf{mean} to \textbf{make} anyone feel bad about me or talk to me out of pityness at all.
I just \textbf{wanted} to open up, since I feel myself drowned in my own constant rumination and loneliness.
If anybody feels like talking, I 'd be \textbf{happy} and grateful for having someone to speak with. <3 Thank you for reading this. \textbf{Best} regards, - Hugo {\EmojiFont 💜}

% matched lemmas: care, cry, depression, end, experience, friend, get, give, good, guy, happy, hate, help, impossible, lose, make, many, mean, meet, month, more, new, relationship, take, thing, want, year
\end{textsample}
