\begin{textsample}{POS Dim 2 – generic\_gpt – Score 12.00 – generic\_gpt/t1404\_gpt.txt}  \label{ex:f2_pos_031}
I don't really know how to talk about this in real life, so I ’m dumping it here.
Lately I ’ve been feeling like I ’m living next to other people ’s lives instead of in my own.
I go through the motions : work, commute, groceries, scrolling on my phone until I ’m tired enough to sleep.
I talk to coworkers about tasks and deadlines, but as soon as it veers into anything personal, I panic a bit inside and steer it back to “ safe ” topics.
Then I go home and feel weirdly \textbf{hurt} that no one really knows me.
There are people around me, technically.
I ’m not completely isolated.
I have acquaintances, a group chat that ’s mostly memes, some old \textbf{friends} I occasionally text.
But everything feels thin, like a bad phone signal.
I keep craving those deep, comfortable connections where you can just exist around someone without feeling like you ’re performing.
Instead, I ’m always hyper-aware of how I ’m coming across, like I ’m auditioning for the role of a normal \textbf{human}.
What ’s confusing is that I ’m not even sure who the “ real me ” is anymore.
When I ’m alone too long, I feel hollow and disconnected from myself.
When I ’m with people, I feel like I ’m wearing a costume.
I \textbf{leave} \textbf{social} \textbf{situations} exhausted, replaying every small \textbf{thing} I said, convinced I sounded weird or boring or too \textbf{much}.
Weekends are the worst.
I wake up with this heavy feeling in my chest, knowing I have two days to fill and no one who ’s really expecting me.
Sometimes I ’ll try to reach out and suggest something, and if people are busy or just don't respond, it hits \textbf{way} harder than it should.
Then I feel pathetic for \textbf{caring} so \textbf{much}.
I ’ve tried the usual \textbf{advice} : hobbies, online communities, being the one to initiate.
It \textbf{helps} a bit, but it still feels like I ’m standing outside a \textbf{house}, looking through the window at other people laughing together.
I can see them clearly, but there ’s this invisible barrier between us that I can't figure out how to cross.
I don't even know what I ’m asking for.
I guess I just \textbf{wanted} to say this somewhere.

% matched lemmas: advice, care, friend, help, house, human, hurt, leave, much, situation, social, thing, want, way
\end{textsample}
