\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t197\_gpt.txt}  \label{ex:f2_pos_009}
Last \textbf{year} feels like it happened to a \textbf{different} person.
I was on track for a promotion, had a solid \textbf{friend} group, and there was this \textbf{girl} I really liked.
For the first \textbf{time} in a long \textbf{time}, I actually felt like \textbf{things} were moving in the right direction.
I started to picture a \textbf{future} where I wasn't constantly lonely or doubting myself.
Then everything just fell apart.
The promotion fell through.
I started \textbf{school} on \textbf{top} of working, and that completely wrecked my \textbf{social} life.
I stopped seeing my \textbf{friends} as \textbf{much}, and they slowly drifted away.
The \textbf{girl} I liked told me she \textbf{only} \textbf{wanted} something casual and that she doesn't catch feelings.
I really \textbf{loved} her, and hearing that just crushed me.
I \textbf{ended} up quitting my job, which \textbf{meant} I \textbf{lost} my work \textbf{friends} too.
I \textbf{got} depressed, stopped working out, and isolated myself.
It felt like I went from having momentum to just … nothing.
No progress, no people, no purpose.
Now I ’m trying to rebuild, but it doesn't feel hopeful the \textbf{way} it did before.
I have a \textbf{new} job, but I don't really like the people there.
I started working out again, but I feel weak and everything \textbf{hurts}.
I ’m planning to go back to \textbf{school} in the summer and \textbf{give} it another shot.
The \textbf{thing} is, I don't really have \textbf{many} real \textbf{friends} anymore.
My \textbf{relationship} with my family isn't \textbf{great}.
And a romantic \textbf{relationship} honestly feels unrealistic at this point.
I ’m trying to “ improve myself ” like everyone always says, but underneath it all I still feel this deep \textbf{pain}.
I feel worthless a \textbf{lot} of the \textbf{time}, like I ’ll never be seen as worth anyone ’s \textbf{time}.
Like I ’m never going to be \textbf{good} enough at anything — not as a partner, not as a \textbf{friend}, not in my career.
It ’s \textbf{hard} to keep going and keep trying when it feels like everything I do just proves that belief right.

% matched lemmas: different, end, friend, future, get, girl, give, good, great, hard, hurt, lose, lot, love, many, mean, much, new, only, pain, relationship, school, social, thing, time, top, want, way, year
\end{textsample}
