\begin{textsample}{POS Dim 2 – generic\_gpt – Score 10.00 – generic\_gpt/t580\_gpt.txt}  \label{ex:f2_pos_040}
I don't really know how to talk about this in real life, so I ’m dumping it here.
I ’m at this weird point where my life looks “ fine ” from the outside, but I feel like a ghost moving through it.
I have coworkers I chat with, a family I text sometimes, a couple of old \textbf{friends} I send memes to.
But none of it feels like connection.
It ’s like I ’m constantly in “ small talk mode, ” even with people I ’ve known for \textbf{years}.
I can't remember the last \textbf{time} I felt genuinely \textbf{understood} by someone.
Not “ they listened to me talk, ” but that feeling of, “ oh, they actually \textbf{get} what I \textbf{mean}. ” I always \textbf{end} up editing myself mid-sentence, \textbf{making} my thoughts shorter, lighter, less intense, so I don't come off as “ too \textbf{much}. ” And then I go home feeling like I \textbf{spent} the \textbf{whole} day pretending to be a watered-down version of myself.
I try to reach out sometimes, but it always feels like I ’m intruding.
I ’ll type a message, stare at it, then delete it because I convince myself the other person is just being polite when they say we should talk \textbf{more}.
When I do send it, I overanalyze every minute they don't respond, then feel stupid for \textbf{caring} so \textbf{much}.
The worst part is the evenings.
That moment when the distractions run out and it ’s just me, the quiet, and this heavy sense that if I disappeared from everyone ’s life, their routines wouldn't really change.
Maybe they ’d be sad for a bit, but nothing would actually be \textbf{different} for them in the long run.
For me, it would be everything.
For them, it would be … a passing \textbf{thought}.
I don't even know what I ’m hoping for by posting this.
I guess I just \textbf{wanted} to put into words that specific \textbf{kind} of loneliness where you ’re not technically alone, but you still feel completely unreachable.

% matched lemmas: care, different, end, friend, get, kind, make, mean, more, much, spend, think, time, understand, want, whole, year
\end{textsample}
