\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t006\_gpt.txt}  \label{ex:f2_pos_012}
I \textbf{grew} up constantly moving – \textbf{different} cities, \textbf{different} countries, \textbf{different} \textbf{schools} and universities.
I was “ the \textbf{new} \textbf{kid} ” so \textbf{many} \textbf{times} I \textbf{lost} count.
I ’d \textbf{make} \textbf{friends}, sometimes even \textbf{good} ones, and then we ’d move again.
At first we ’d stay in touch, but over \textbf{time} it always faded.
It ’s just so \textbf{much} easier to keep a friendship going when you see each other regularly than when it ’s all effort and planning and messages across distance.
It slowly turned into this “ out of sight, out of mind ” pattern for me.
Now I ’ve actually been in the \textbf{same} place for about five \textbf{years}, which is the longest I ’ve ever stayed anywhere.
But my friendships still feel temporary.
I \textbf{make} acquaintances, have friendly conversations, sometimes hang out a few \textbf{times}, but it rarely goes deeper.
I \textbf{struggle} to \textbf{find} the \textbf{emotional} energy or even the desire to really invest in people or to start \textbf{new} connections from scratch.
I ’m starting to wonder if I ’ve internalized the \textbf{idea} that everyone is transient, that no one \textbf{sticks} around.
Maybe I ’m subconsciously protecting myself from the \textbf{hurt} of \textbf{losing} people by never letting them \textbf{get} too close in the first place.
On the surface I \textbf{want} deep, stable connections, but when opportunities appear, I almost … pull back.
Or I just don't follow through.
The result is that I feel really unmoored and lonely, like I ’m floating through places and people without ever really belonging anywhere.
I \textbf{want} to change this, but I don't quite know how to override whatever ’s going on underneath.
Has anyone else had a \textbf{similar} \textbf{experience}, especially people who moved around a \textbf{lot} \textbf{growing} up?
Did you notice the \textbf{same} “ everyone is temporary ” mindset?
If so, how did you manage it or start to change it?
What \textbf{helped} you actually \textbf{build} and maintain deeper friendships instead of just letting everything stay on the surface and fade away?

% matched lemmas: build, different, emotional, experience, find, friend, get, good, grow, help, hurt, idea, kid, lose, lot, make, many, much, new, same, school, similar, stick, struggle, time, want, year
\end{textsample}
