\begin{textsample}{POS Dim 2 – human – Score 22.00 – human/t1839\_human.txt}  \label{ex:f2_pos_028}
Hello.
I really don't know what exactly I 'm on here for.
I go expelled from my"regular"brick \textbf{school} when I was in sixth grade.
I 've been doing online \textbf{school} since then.
I have pretty intense \textbf{social} \textbf{anxiety} and \textbf{only} two"\textbf{friends}".
I haven't seen them in person in \textbf{years}.
They don't live super far away.
They are never really interested in talking to me and they 've done some pretty iffy \textbf{things} before.
I 'm gay btw, which is relevant.
One \textbf{friend} \textbf{dated} this \textbf{guy} who would call me the f slur and tell me to KMS on numerous occasions and she was there for each of them.
She \textbf{dated} him for like two \textbf{years}, there \textbf{break} up was unrelated.
Another instance we were talking to a \textbf{guy} in our grade who repeatedly called me \textbf{similar} stuff and threatened to set me on fire.
She \textbf{only}"denounced"him when he \textbf{left}.
Like a week later she posted the two of them and another \textbf{girl} huddled together smiling as \textbf{friends}.
The other \textbf{friend} once laughed when some \textbf{kind} of \textbf{friend} of hers was being very actively homophobic and some other minor"micro aggressions".
I am really lonely, I 've had off and on \textbf{depression} and \textbf{anxiety} for like three \textbf{years}, had to repeat my junior \textbf{year} because I wasn't doing my \textbf{school} work during my \textbf{depression}.
Again I just came on here to vent on a whim.
I am scared I 'll never \textbf{meet} a \textbf{guy} or have any real \textbf{social} life.
I usually \textbf{only} \textbf{leave} my \textbf{house} like once a \textbf{month}, with my \textbf{parents}.
I don't have a driver 's license.
When I 'm around people ik ( my \textbf{parents} and siblings ) I 'm usually a confident person and when I 'm alone I like \textbf{think} of myself as awesome and confident, \textbf{able} to stand up for myself, but when I 'm on a walk by myself ( which my therapist told me I should do ) I \textbf{get} really nervous about running into someone, especially \textbf{men}, my head is always on a swivel and I turn around if I see someone coming my \textbf{way}, I 've walked two blocks out of my \textbf{way} just to \textbf{avoid} a couple walking their dog two last week.
I don't really know what you \textbf{guys} could say but here goes.

% matched lemmas: able, anxiety, avoid, break, date, depression, friend, get, girl, guy, house, kind, leave, man, meet, month, only, parent, school, similar, social, thing, think, way, year
\end{textsample}
