\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 22.00 – summary\_guided\_gpt/t1239\_gpt.txt}  \label{ex:f2_pos_019}
I ’m over 30 and started transitioning in 2023, and in a \textbf{lot} of \textbf{ways} it was the \textbf{best} \textbf{thing} I ’ve ever done for myself.
It ’s like so \textbf{much} of the self-hate and \textbf{mental} \textbf{health} chaos I ’d been dragging around for \textbf{years} finally \textbf{made} sense and started to ease.
For the first \textbf{time}, I actually feel like I ’m living as myself.
But at the \textbf{same} \textbf{time}, I feel absolutely terrified and alone.
The global anti-trans climate has me constantly on edge.
It feels like there ’s this huge, \textbf{growing} wave of hatred aimed at people like me, and I ’m just standing there in the open with no shelter.
That fear mixes with another, \textbf{more} personal one : the fear that I ’m going to be alone forever.
I ’ve been single since 2017.
Nine \textbf{years}.
I ’ve done everything people say you ’re “ supposed ” to do : I go to therapy, I work on myself, I go to the gym, I have hobbies, I join clubs and groups, I \textbf{meet} \textbf{new} people, I ’ve \textbf{pushed} myself to be \textbf{more} \textbf{social} even though I ’m autistic and introverted.
I ’ve tried to pursue romantic \textbf{interests} instead of just waiting for something to happen.
I ’ve \textbf{made} \textbf{friends}.
I ’ve really, genuinely tried.
And yet nothing changes.
Everyone around me seems to be in long-term \textbf{relationships}, \textbf{building} lives with someone, while I just … don't.
I ’m \textbf{happy} for them, but it also \textbf{hurts} so \textbf{much}.
It \textbf{makes} me feel like there ’s something fundamentally wrong with me, like \textbf{love} is some door that just won't open no matter how \textbf{many} \textbf{times} I knock.
My \textbf{friends} are busy and not available often.
I feel like a side character in everyone else ’s life.
The loneliness is so heavy that it ’s starting to turn into suicidal thoughts.
I told my therapist and asked for a referral to a psychiatrist, because I know I ’m depressed.
But even if meds \textbf{help}, and even if friendships \textbf{get} a bit better, it still feels like there ’s this huge missing piece.
I don't \textbf{understand} why \textbf{love} seems to be denied to me, and I ’m really starting to feel like I can't live like this \textbf{much} longer.

% matched lemmas: build, friend, get, good, grow, happy, health, help, hurt, interest, lot, love, make, many, meet, mental, more, much, new, push, relationship, same, social, thing, time, understand, way, year
\end{textsample}
