\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 25.00 – summary\_guided\_gpt/t1108\_gpt.txt}  \label{ex:f2_pos_004}
I keep seeing \textbf{more} and \textbf{more} \textbf{guys} – \textbf{young} and not-so-young – who are basically decent, functional people but can't seem to \textbf{find} a partner.
Not abusive, not addicts, not completely socially inept.
Just … ordinary \textbf{men} who, for whatever reason, never \textbf{get} picked.
And the usual self‑help \textbf{advice} from male and female influencers doesn't seem to move the needle \textbf{much}.
What \textbf{makes} it harder is that a \textbf{lot} of “ what \textbf{women} \textbf{want} ” is either very vague, contradictory, or framed in a \textbf{way} that ’s almost \textbf{impossible} to translate into concrete steps.
Be confident but not arrogant, vulnerable but not needy, ambitious but not work-obsessed, etc.
You can try to improve, but there ’s no clear point where you can say, “ I ’ve done the \textbf{things}, now I ’m allowed to have a \textbf{relationship}. ” I ’m starting to \textbf{think} we ’re heading toward a \textbf{future} where a \textbf{lot} \textbf{more} people – especially \textbf{men} – will be long‑term single, not because there ’s something fundamentally wrong with them, but because of a mix of \textbf{social} and technological changes that nobody really planned for.
Most discussions I see focus on : - \textbf{Men} ’s grief and frustration - Women ’s disappointment and exhaustion - How to “ \textbf{cope} ” with loneliness At the \textbf{same} \textbf{time}, there are tons of channels and communities aimed at \textbf{women} that say, “ Okay, you ’re single, now here ’s how to thrive. ” They encourage travel, hobbies, mutual \textbf{support} groups, empowerment spaces, etc.
There ’s a \textbf{whole} positive narrative available.
What ’s the equivalent for \textbf{men} who realistically have no \textbf{dating} prospects?
Not just “ work out, \textbf{get} a hobby, grind your career, ” but actual positive paths, activities, and networks that \textbf{help} \textbf{men} \textbf{build} meaningful, connected, fulfilling lives while single.
I don't like the phrase “ male crisis. ” It sounds like the \textbf{problem} is \textbf{men} themselves, when in reality it feels \textbf{more} like \textbf{men} are \textbf{stuck} in the middle of rapid changes ( \textbf{dating} apps, shifting norms, economic pressures ) that they didn't create and can't control.
This is \textbf{kind} of uncharted territory.
So I ’m genuinely curious – from both \textbf{men} and \textbf{women} : What does a \textbf{good}, rich, emotionally \textbf{supported} life look like for a \textbf{man} who might stay single long‑term?
What \textbf{kinds} of communities, routines, or structures could \textbf{help} \textbf{men} not \textbf{only} survive this, but actually thrive?

% matched lemmas: advice, build, cope, date, find, future, get, good, guy, help, impossible, kind, lot, make, man, more, much, only, problem, relationship, same, social, stick, support, thing, think, time, want, way, whole, woman, young
\end{textsample}
