\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 22.00 – summary\_guided\_gpt/t749\_gpt.txt}  \label{ex:f2_pos_016}
I ’m 31 now and it feels like my \textbf{whole} adult life has just been one long lesson in being used and then discarded.
I \textbf{met} my ex-husband when I was 21.
We \textbf{got} married, had a child, and for six \textbf{years} I stayed even though he cheated on me over and over.
I kept trying to \textbf{make} it work for our son, kept hoping he ’d change, but in the \textbf{end} he \textbf{left} us.
He \textbf{wants} nothing to do with our child now.
Watching my son \textbf{grow} up without a dad who even \textbf{cares} to know him is its own \textbf{kind} of heartbreak.
After a \textbf{year} on my own, I \textbf{thought} maybe I was ready to try again.
I started \textbf{dating} someone long-distance.
Eventually I moved to be with him, about two hours away from my family.
It felt like a \textbf{big} risk, but I really \textbf{believed} in us.
We were together for 3.5 \textbf{years}.
Between my son and his two \textbf{kids}, we had three children in the \textbf{house} most of the \textbf{time}.
I was the one mostly \textbf{supporting} us.
When he was unemployed and depressed, I \textbf{spent} hours \textbf{helping} him apply for jobs, redoing his resume, \textbf{pushing} him to not \textbf{give} up.
He finally \textbf{got} a job he liked, then a promotion to manager, and even a company truck.
I was genuinely \textbf{happy} for him.
And then he \textbf{broke} up with me.
It ’s \textbf{hard} not to see a pattern : both \textbf{men} \textbf{left} right after they “ \textbf{got} everything ” they seemed to want—stability, \textbf{support}, someone to carry them through the \textbf{hard} parts.
Once life started looking up for them, I was suddenly no longer needed.
Now I ’m here, two hours from my family, feeling like most of my light is just…gone.
I feel empty and stupid for trusting again.
I feel like I poured myself into other people until there was nothing \textbf{left} for me, and now I ’m alone with a child to raise and no one to lean on.
I don't even know what I ’m looking for by posting this.
I just feel so used and so alone.

% matched lemmas: believe, big, break, care, date, end, get, give, grow, happy, hard, help, house, kid, kind, leave, make, man, meet, push, spend, support, think, time, want, whole, year
\end{textsample}
