\begin{textsample}{POS Dim 2 – human – Score 23.00 – human/t1371\_human.txt}  \label{ex:f2_pos_027}
The first \textbf{time} I ever felt in \textbf{love}, it was someone I \textbf{met} when I was 12.
Even now 20 \textbf{years} later, I \textbf{think} about him and how \textbf{much} influence that one \textbf{year} had on me. \textbf{Love} is one of the most fulfilling emotions in my life.
When I look at the life that I ’ve \textbf{built} for myself, I ’m proud of how \textbf{much} I ’ve pulled through.
My life has everything I could possibly ask for, it ’s damn near perfect.
I was \textbf{able} to buy myself a \textbf{house} even though I just \textbf{make} a couple dollars above minimum wage, I ’m still \textbf{friends} with people from childhood and all of them are genuinely \textbf{good} people, I have a stable career field that is in line with my values and \textbf{needs}.
I have a \textbf{lot} of \textbf{health} \textbf{problems}, but I have the will to improve my \textbf{health} as \textbf{much} as I can.
Also, if it wasn't for my \textbf{health} \textbf{problems}, I would be in \textbf{top} shape with the amount of effort I put in.
The \textbf{only} \textbf{thing} I don't have is a romantic partner.
It \textbf{makes} me severely depressed.
I feel like nothing \textbf{helps}.
I ’ve done intensive outpatient for \textbf{depression}.
I will \textbf{make} \textbf{time} to do activities that I \textbf{enjoy}, prioritize spending \textbf{time} with \textbf{friends}.
Practice DBT skills.
Even after a \textbf{lot} of therapy sessions, my therapist \textbf{kind} of came down to the conclusion that it doesn't appear that I ’m imbalanced in some other area of my life causing me to be this sad about not having romantic partner.
But my instinctual \textbf{emotional} \textbf{need} for romantic companionship is just really strong.
I \textbf{hate} it.
I \textbf{want} it to \textbf{end}.
I \textbf{want} it to stop.
I can't stand it.
I literally keep trying to lean into other \textbf{things} to \textbf{make} up for how \textbf{much} this \textbf{hurts} me, but it doesn't work.
I don't know what to do with myself.
I don't know if anybody has some crazy \textbf{ideas} that I haven't considered.

% matched lemmas: able, build, depression, emotional, end, enjoy, friend, good, hate, health, help, house, hurt, idea, kind, lot, love, make, meet, much, need, only, problem, thing, think, time, top, want, year
\end{textsample}
