\begin{textsample}{POS Dim 2 – generic\_gpt – Score 11.00 – generic\_gpt/t2608\_gpt.txt}  \label{ex:f2_pos_034}
I don't really know how to explain this without sounding dramatic, but lately it feels like I ’m living in spectator mode instead of actually participating in my own life.
On paper, I ’m “ fine. ” I have a job, a place to live, I ’m not in immediate crisis.
But I come home every day to an empty apartment, sit on the \textbf{same} spot on the couch, and scroll until my eyes \textbf{hurt}.
Hours go by and I realize I haven't said a single word out loud.
Sometimes the \textbf{only} \textbf{time} I hear my own voice is when I ’m talking to myself or ordering coffee.
I have acquaintances.
People I can talk to at work, send memes to, maybe see once every \textbf{month} or two.
But I don't have that person I can text when something small but important happens.
I don't have anyone who ’ll notice if I go quiet for a few days.
When I do \textbf{meet} people, the connection never seems to move past surface-level.
It ’s like there ’s a glass wall between me and everyone else.
What \textbf{hurts} the most is that I used to have close \textbf{friends}.
Group chats that were constantly active, late-night calls, inside jokes.
Over \textbf{time} people moved, \textbf{got} partners, \textbf{got} busy, and I somehow became the person you “ \textbf{mean} to catch up with sometime. ” I scroll through \textbf{social} media and see everyone \textbf{getting} married, having \textbf{kids}, going on trips with “ their people, ” and I ’m just … not in anyone ’s picture.
I keep asking myself if this is my fault.
Maybe I ’m too quiet, too awkward, too boring.
Maybe I missed the window where people \textbf{build} their core group and now I ’m just orbiting on the outside.
I try to put myself out there occasionally, but it feels forced and exhausting, and I come home feeling \textbf{more} alone than before.
The \textbf{hardest} part is waking up and realizing there is no one who truly knows what ’s going on with me.
If I disappeared from the internet and stopped showing up to work, I honestly don't know how long it would \textbf{take} for anyone to really notice that something was wrong.

% matched lemmas: build, friend, get, hard, hurt, kid, mean, meet, month, more, only, same, social, take, time
\end{textsample}
