\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 26.00 – summary\_guided\_gpt/t1026\_gpt.txt}  \label{ex:f2_pos_001}
Throwaway for obvious reasons.
I ’m 28, and the \textbf{more} I look around, the \textbf{more} I feel like the \textbf{future} for \textbf{guys} like me is just … bleak.
I don't \textbf{hate} \textbf{women}, I ’m not anti-feminist – \textbf{women} ’s \textbf{struggles} and feminism are real and important, and I genuinely \textbf{believe} that.
But at the \textbf{same} \textbf{time}, it feels like \textbf{men} are being vilified \textbf{more} and \textbf{more}, like just existing as a \textbf{man} \textbf{makes} you suspect or unwanted.
It seems like there are simply \textbf{more} \textbf{men} than \textbf{women}, and that math alone \textbf{means} a \textbf{lot} of us are going to \textbf{end} up alone no matter what we do.
On \textbf{top} of that, it feels like \textbf{men} generally crave intimacy \textbf{more}, while a \textbf{lot} of \textbf{women} I know seem genuinely content being single, focusing on themselves, their \textbf{friends}, their careers.
I ’m \textbf{happy} for them, but it just reinforces this feeling that there ’s no place for someone like me.
I ’ve \textbf{spent} about a decade trying. \textbf{Shared} \textbf{interest} groups, hobbies, meetups, \textbf{dating} apps – you name it.
Not a single \textbf{date}, not a single kiss, no \textbf{girlfriend}, no sexual \textbf{experience}.
Nothing.
It ’s like I ’m invisible, or worse, like I ’m not even allowed to \textbf{want} anything without being labeled creepy or entitled.
Economic stuff doesn't \textbf{help} either.
Money is tight, everything is expensive, and even hobbies cost \textbf{more} than I can really afford.
It ’s \textbf{hard} to “ \textbf{enjoy} life ” when you ’re broke and alone.
The gym is literally the \textbf{only} \textbf{thing} keeping me going at this point.
Some days it feels like \textbf{young} \textbf{men} like me are just \textbf{meant} to work \textbf{hard}, shut up, and die alone.
I don't know what I ’m looking for posting this, I just \textbf{needed} to say it somewhere.

% matched lemmas: believe, date, end, enjoy, experience, friend, future, girlfriend, guy, happy, hard, hate, help, interest, lot, make, man, mean, more, need, only, same, share, spend, struggle, thing, time, top, want, woman, young
\end{textsample}
