\begin{textsample}{POS Dim 2 – generic\_gpt – Score 12.00 – generic\_gpt/t735\_gpt.txt}  \label{ex:f2_pos_033}
I don't really know how to say this in a \textbf{way} that doesn't sound dramatic, but lately it feels like my life is happening behind glass.
On paper I ’m not “ alone. ” I have coworkers, a couple of old \textbf{friends} I text sometimes, family chats that light up with memes and logistics.
But I feel like I ’m always slightly out of phase with everyone else, like I ’m there physically but not really *with* them.
I go days without using my voice for anything besides “ thank you ” at a checkout or “ have a \textbf{good} one ” at work.
I ’ll rehearse conversations in my head—what I ’d say if someone actually asked how I ’m doing, what I ’d tell a \textbf{friend} if I felt safe enough to be honest—and then the moment passes and I just default to “ I ’m fine, you? ” because I don't \textbf{want} to \textbf{make} \textbf{things} weird.
The weird part is I ’m not even sure what I ’m missing anymore.
I don't know if it ’s a romantic partner, deeper friendships, or just one person who genuinely \textbf{wants} to know what my day looked like.
I scroll through \textbf{social} media and see people posting group photos, trips, little inside jokes in the comments, and I feel like I ’m watching a life I somehow didn't qualify for.
I try to reach out sometimes.
I ’ll send a message, suggest a plan, and then \textbf{spend} the \textbf{whole} \textbf{time} terrified I ’m being annoying or clingy.
If they \textbf{take} a while to answer, I immediately assume I ’ve overstepped.
If they say they ’re busy, I tell myself they ’re just being polite and don't really \textbf{want} to see me.
It ’s like my brain is determined to interpret everything in the most self-rejecting \textbf{way} possible.
I ’ve also noticed how loneliness \textbf{makes} me smaller.
I \textbf{share} less.
I \textbf{take} up less space.
I censor my \textbf{interests} because I don't \textbf{want} to be “ too \textbf{much}. ” Then I feel invisible and resentful, but it ’s a \textbf{situation} I \textbf{helped} create by not showing up as myself.
Nights are the worst.
There ’s this heavy silence that feels almost physical.
I ’ll lie there \textbf{thinking} about how, if I disappeared, it would \textbf{take} a while for anyone to notice in a concrete \textbf{way}.
People would be “ shocked ” in the abstract, but day-to-day, not \textbf{much} would change.
I don't really know what I \textbf{want} from posting this.
Maybe I just \textbf{needed} to put it somewhere outside my own head for once.

% matched lemmas: friend, good, help, interest, make, much, need, share, situation, social, spend, take, thing, think, time, want, way, whole
\end{textsample}
