\begin{textsample}{POS Dim 2 – generic\_gpt – Score 11.00 – generic\_gpt/t1852\_gpt.txt}  \label{ex:f2_pos_035}
I ’ve been feeling this really specific \textbf{kind} of loneliness lately that doesn't quite fit into the usual “ no \textbf{friends} / no \textbf{relationship} ” boxes, even though those are part of it too.
On paper, I ’m not completely alone.
I have coworkers I \textbf{get} along with, a few old \textbf{friends} I text every now and then, family I can visit on holidays.
But the weird \textbf{thing} is that I feel the most alone when I ’m actually around people.
It ’s like there ’s a glass wall between me and everyone else.
I can see them, hear them, laugh at their jokes, but it doesn't feel like I ’m really *with* them.
I notice it most in group conversations.
People talk about their weekends, their partners, their \textbf{kids}, their trips, their plans.
I chime in with something surface-level, they respond politely, and then the conversation moves on.
No one is being \textbf{mean}.
It ’s just like I ’m a background character in a movie, there to fill space so the main characters don't look like they ’re talking to themselves.
I ’m also realizing how \textbf{much} of my “ connection ” with people is logistical or functional. “ What \textbf{time} is the meeting? ” “ Can you send that file? ” “ Are you free Saturday? ” When I try to go deeper—say something honest like “ I ’ve been feeling pretty off lately”—it usually \textbf{gets} brushed past, or people say “ \textbf{same} ” and then switch topics.
I \textbf{get} it ; everyone has their own stuff.
But it reinforces this \textbf{idea} that my inner world isn't really something anyone \textbf{wants} to linger on.
What \textbf{makes} it worse is that I don't even know how to fix it.
I ’ve tried being \textbf{more} open, I ’ve tried initiating plans, I ’ve tried being the “ funny one ” or the “ \textbf{good} listener. ” I can play those roles, but none of them feel like me.
And when I ’m finally alone again, I feel this heavy emptiness, like I \textbf{spent} all this energy performing and still came back with nothing.
I keep thinking there must be some missing piece—some \textbf{way} other people naturally connect that I never learned.
But I ’m starting to worry that this might just be how my life feels : surrounded, but separate.

% matched lemmas: friend, get, good, idea, kid, kind, make, mean, more, much, relationship, same, spend, thing, time, want, way
\end{textsample}
