\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 23.00 – summary\_guided\_gpt/t1793\_gpt.txt}  \label{ex:f2_pos_008}
I ’m so tired.
Not just physically, but in a \textbf{way} that feels like something inside me has burned out.
I keep saying to myself that my “ soul is dead, ” and that ’s honestly the closest \textbf{thing} I have to describing it.
I don't even \textbf{understand} my own feelings anymore.
I ’m sad, but also \textbf{kind} of numb, like everything is happening behind a thick piece of glass.
I \textbf{avoid} talking to my family as \textbf{much} as I can.
I don't know what to say to them, and I don't \textbf{want} to pretend I ’m okay when I ’m not.
I don't really have close \textbf{friends} either, just coworkers I talk to at work.
I don't trust people.
I used to hang out \textbf{more}, but I stopped because it never actually \textbf{made} me \textbf{happy}.
It just felt like going through the motions. \textbf{Dating} feels pointless.
Every \textbf{time} I start to \textbf{care} about someone, it \textbf{ends} up feeling worthless, like it was a waste of \textbf{time} to open up in the first place.
I feel \textbf{stuck} with no real goals, no clear \textbf{future}, just existing.
On \textbf{top} of that, I ’m \textbf{dealing} with financial \textbf{problems}, constant overthinking, trust \textbf{issues}, \textbf{depression}, and \textbf{anxiety}.
It all just piles up.
I ’ve tried so \textbf{many} \textbf{things} to \textbf{cope}.
I ’ve tried leaning on religious faith, and I ’ve tried other “ \textbf{good} ” and “ bad ” \textbf{ways} of \textbf{coping}.
Nothing seems to actually \textbf{help}.
I ’ve even gone to therapy, but it hasn't felt useful because I can't explain what exactly \textbf{makes} me so sad.
I just am.
I feel completely \textbf{lost} about what to do with my life, like I ’m wandering without a map and every direction looks wrong.

% matched lemmas: anxiety, avoid, care, cope, date, deal, depression, end, friend, future, good, happy, help, issue, kind, lose, make, many, more, much, problem, stick, thing, time, top, understand, want, way
\end{textsample}
