\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 24.00 – summary\_guided\_gpt/t810\_gpt.txt}  \label{ex:f2_pos_006}
I turned 20 today and it honestly just feels like any other lonely day, maybe a bit worse.
So far \textbf{only} one person has said \textbf{happy} birthday to me.
My own family hasn't said anything.
I ’ve also had the flu for the last four days, so I ’m \textbf{stuck} in bed feeling physically awful on \textbf{top} of everything else.
I ’m \textbf{kind} of used to being alone, so I didn't expect \textbf{much}, but it still stings \textbf{more} than I \textbf{want} to admit.
I \textbf{grew} up in a family where we don't talk about feelings at all.
No “ I \textbf{love} you, ” no real conversations about what ’s going on inside.
Because of that, opening up to people and being \textbf{social} feels almost \textbf{impossible} sometimes.
It ’s like I never learned how.
About three \textbf{years} ago I \textbf{met} a \textbf{girl} on Discord.
We were \textbf{friends} for a \textbf{year}, then we became long-distance partners.
That \textbf{year} we were together was honestly the \textbf{best} I ’ve ever felt.
We had this really beautiful connection.
I could tell her about my day, my dreams, my fears.
We \textbf{made} plans together and had \textbf{shared} goals.
For once, I felt like I wasn't just drifting through life.
I had direction, and a \textbf{future} that actually seemed worth moving toward.
She \textbf{ended} \textbf{things} around our one-year anniversary because of external reasons.
I still \textbf{loved} her, but it didn't matter.
It ’s been about ten \textbf{months} since then.
I don't miss her specifically as intensely anymore, but I really miss what we had.
That feeling of being \textbf{understood}, of having someone I could be completely honest with.
Someone who \textbf{cared} about my day and my \textbf{future}, and whose \textbf{future} I \textbf{cared} about too.
Now I just feel \textbf{lost} again.
I miss having that deep \textbf{emotional} connection \textbf{more} than anything.
I don't even know how to \textbf{find} something like that again, especially when I \textbf{struggle} so \textbf{much} with opening up in the first place.
I guess I just \textbf{needed} to put this somewhere, because I don't really have anyone in my life I can say it to.

% matched lemmas: care, emotional, end, find, friend, future, girl, good, grow, happy, impossible, kind, lose, love, make, meet, month, more, much, need, only, share, social, stick, struggle, thing, top, understand, want, year
\end{textsample}
