\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 26.00 – summary\_guided\_gpt/t468\_gpt.txt}  \label{ex:f2_pos_002}
I ’m Hugo, almost 23, from Spain.
About a \textbf{month} ago I \textbf{lost} my job because of my \textbf{depression}, and \textbf{only} recently did I finally start medication after \textbf{years} of trying to \textbf{cope} on my own.
The last three weeks I ’ve basically been at home the \textbf{whole} \textbf{time}, just playing video games and sleeping.
I barely have energy to do anything else, sometimes not even to eat or \textbf{cry}.
It feels like I ’m just existing rather than living.
I feel \textbf{more} alone than I ever have.
I ’ve tried a \textbf{lot} of \textbf{different} \textbf{ways} to \textbf{meet} \textbf{new} people over the \textbf{years}, but it always \textbf{ends} up feeling almost \textbf{impossible}, especially being an introvert.
I don't naturally put myself out there, and when I do, it usually feels awkward or forced.
After some really bad \textbf{experiences} with \textbf{friends} about five \textbf{years} ago, I \textbf{kind} of retreated into myself and chose a \textbf{more} solitary lifestyle, \textbf{thinking} it would protect me.
Now it just feels like I \textbf{built} my own prison.
I do still have some \textbf{good} \textbf{friends}, but they ’re busy with their own adult lives : work, \textbf{relationships}, responsibilities.
I ’m \textbf{happy} for them, but at the \textbf{same} \textbf{time} I feel like I ’m the one whose life isn't going anywhere.
I ’m the \textbf{friend} who ’s \textbf{stuck}, the one whose life isn't going well, and it \textbf{makes} it even harder to reach out to them.
I don't \textbf{want} to be the constant “ \textbf{problem} ” \textbf{friend}.
I ’m not posting this because I \textbf{want} pity.
I just \textbf{needed} to open up somewhere, to say out loud that I feel incredibly lonely and \textbf{lost} right now.
If anyone relates to this or just feels like talking, I ’d honestly be really grateful to have someone to chat with.
Even just a simple conversation would \textbf{mean} a \textbf{lot}.

% matched lemmas: build, cope, cry, depression, different, end, experience, friend, good, happy, impossible, kind, lose, lot, make, mean, meet, month, more, need, new, only, problem, relationship, same, stick, think, time, want, way, whole, year
\end{textsample}
