\begin{textsample}{POS Dim 2 – human – Score 25.00 – human/t1265\_human.txt}  \label{ex:f2_pos_022}
\textbf{Parents} \textbf{hate} me.
Pretty sure my sister \textbf{finds} me as a horrible weird person.
Antisocial.
Don't talk to anybody.
I have the urge to \textbf{cry} all the \textbf{time} but I just hold it in.
I feel I ’ve forgotten to \textbf{cry}.
Just wanna let it out but at the \textbf{same} \textbf{time} not \textbf{want} to.
I have most of the \textbf{things} I ’ve ever \textbf{wanted} but past that I ’m just a failure.
I ’m a burden and shame to the people I try to surround myself with.
I promised my \textbf{self} that I would just \textbf{give} up this \textbf{time} around but I keep \textbf{giving} in to false hope and it just \textbf{hurts} even \textbf{more}.
My entire life I have this one picture engrained in my mind, and it ’s that \textbf{same} look of disappointment people have of me, their anger, their sadness caused by me, their negative \textbf{experiences}, all because of me.
I ’ve said some pretty horrible \textbf{things} to defend myself in heated \textbf{situations}.
Some of which I do \textbf{mean} because of repeated trauma but deep down I know they ’re right.
There ’s this side of me that envisions wild success in the \textbf{future} but with that also comes the person that \textbf{made} it happen.
I ’ve contemplated \textbf{many} \textbf{times}.
Some \textbf{times} after \textbf{big} \textbf{things}, sometimes casually, sometimes in my dreams.
I know that I ’ll never be \textbf{able} to be normal.
I ’ve just \textbf{accepted} it.
I will always be the miserable person I am, no matter how \textbf{good} or how bad \textbf{things} \textbf{get}.
I \textbf{grew} up with the sole mindset that I am the burden, I am the discrepancy, I am trash that \textbf{needs} to be thrown away.
No one will ever \textbf{love} me, \textbf{understand} me.
It ’s a dog eat dog world.
I just \textbf{wish} i was normal.
So enough of the rant.
Been \textbf{thinking} about it. \textbf{Thought} of all the possible \textbf{ways} but not sure which one would be the easiest and \textbf{least} painful.
Also don't know how to \textbf{make} it so that it will happen so casually that nobody will notice.
Feel like my existence has no significance.
I \textbf{only} consume and not \textbf{give} anything in return.
Just \textbf{wished} that somebody \textbf{loved} and \textbf{understood} me.
Not just for a moment but they really \textbf{understand} me.

% matched lemmas: able, accept, big, cry, experience, find, future, get, give, good, grow, hate, hurt, least, love, make, many, mean, more, need, only, parent, same, self, situation, thing, think, time, understand, want, way, wish
\end{textsample}
