\begin{textsample}{POS Dim 2 – summary\_guided\_gpt – Score 26.00 – summary\_guided\_gpt/t2451\_gpt.txt}  \label{ex:f2_pos_003}
I \textbf{broke} up with my first lover recently.
We \textbf{met} online 5 \textbf{years} ago, basically \textbf{grew} up together from our teens into \textbf{young} adulthood.
When it finally \textbf{ended}, I didn't \textbf{cry}, but there was this weird, heavy \textbf{pain} in my chest that I still don't fully \textbf{understand}.
It ’s like grief without tears.
Because of my past – sexual trauma and watching my \textbf{parents} \textbf{stuck} in a bad marriage – I honestly didn't \textbf{believe} \textbf{love} was real for a long \textbf{time}.
This \textbf{relationship} was the first \textbf{thing} that \textbf{made} me \textbf{think}, “ Maybe it is. ” I ’d been half-expecting the breakup for a while, but I \textbf{thought} I had \textbf{more} \textbf{time}.
And then suddenly there was just … silence.
No messages, no calls.
The quiet \textbf{made} me realize how empty and lonely my life feels right now.
It ’s not the first \textbf{time} I ’ve felt like this.
In 11th grade I \textbf{lost} my \textbf{best} \textbf{friends} of 6 \textbf{years} and felt completely alone.
Back then, my family – my \textbf{mom} and my two brothers – stepped in.
We went on trips, watched movies together, and it actually \textbf{helped}.
I felt held, in a \textbf{way}.
Now that closeness is gone, and I don't even know when or why it changed.
We still see each other, but it feels formal, like we ’re just going through the motions.
My therapist keeps suggesting I \textbf{spend} \textbf{more} \textbf{time} with my family, but I feel like whatever we had before is gone for \textbf{good}, and that \textbf{hurts} in its own \textbf{way}.
I ’m \textbf{stuck} between \textbf{wanting} connection and being terrified of it.
I \textbf{want} to \textbf{meet} \textbf{new} people, hear \textbf{different} perspectives, feel alive again.
But I ’m scared.
Every \textbf{relationship} \textbf{ends} somehow, and I don't know if I can handle this \textbf{kind} of \textbf{pain} over and over.
My loneliness feels like both a wound and a blanket – it \textbf{hurts}, but it also feels safer than risking another ending.

% matched lemmas: believe, break, cry, different, end, friend, good, grow, help, hurt, kind, lose, love, make, meet, mom, more, new, pain, parent, relationship, spend, stick, thing, think, time, understand, want, way, year, young
\end{textsample}
