\begin{textsample}{POS Dim 1 – human – Score 42.00 – human/t2029\_human.txt}  \label{ex:f1_pos_039}
I ’m a 20-year-old college sophomore and I ’ve never really dealt with my mental health the \textbf{way} I should.
I \textbf{get} depressed sometimes, stuck in my \textbf{own} \textbf{head}.
But the one \textbf{thing} that always \textbf{pulls} me out is my \textbf{friend} \textbf{group}.
There ’s six of us who all live together in a \textbf{small} 1000 square foot apartment and it \textbf{feels} \textbf{like} some movie-type friendship I never \textbf{thought} I ’d have Whenever I \textbf{get} in a hole mentally, I come \textbf{home} to \textbf{laughing}, music, \textbf{random} \textbf{conversations}, \textbf{someone} cooking, \textbf{someone} knocking on my \textbf{door} and it takes me out of it.
I don't \textbf{think} I ’ve ever stayed truly depressed for \textbf{more} than a \textbf{day} because the house is so alive all the \textbf{time}.
I \textbf{know} how rare that is. \textbf{Sure}, a lot of \textbf{people} I \textbf{know} live with their \textbf{friends}, but I \textbf{noticed} they all have separate “ \textbf{circles} ” of \textbf{friends} \textbf{outside} of their house and do a lot of \textbf{stuff} without each \textbf{other}. \textbf{None} of their \textbf{groups} are even \textbf{close} to how tight we are.
It ’s almost always all of us together, and somehow there ’s never any issues.
No sub-groups, no \textbf{people} being left out.
It just \textbf{works} and \textbf{everyone} is happy.
Some of us do have our separate ( not as \textbf{close} ) \textbf{friends} but we mainly just have each \textbf{other}.
And recently I \textbf{started} \textbf{thinking} about studying abroad because I love adventure and \textbf{trying} new \textbf{things} … but the thought of losing 6 months of the little \textbf{time} I have left with them \textbf{hit} me \textbf{way} harder than I \textbf{expected}.
It didn't just \textbf{make} me \textbf{think} about being \textbf{gone} but it \textbf{made} me \textbf{realize} all this friendship is temporary.
In two years we are all \textbf{going} to \textbf{move} out, graduate, spread across the country, and I ’m \textbf{going} to have to live alone.
And that terrifies me.
I don't \textbf{know} if I ’ll ever find another \textbf{group} of \textbf{friends} \textbf{like} this again.
And \textbf{thinking} about how eventually I ’ll be coming \textbf{home} to an empty house \textbf{makes} me \textbf{scared} that I ’ll spiral or \textbf{feel} unbearably lonely.
It ’s \textbf{like} studying abroad \textbf{opened} this \textbf{door} in my mind where I suddenly \textbf{see} how fragile and temporary this all is.
I just \textbf{feel} really lucky but also really \textbf{scared} for when it \textbf{ends}.

% matched lemmas: circle, close, conversation, day, door, end, everyone, expect, feel, friend, get, go, group, head, hit, home, know, laugh, like, make, more, move, none, notice, open, other, outside, own, people, pull, random, realize, scare, see, small, someone, start, stuff, sure, thing, think, time, try, way, work
\end{textsample}
