\begin{textsample}{POS Dim 1 – generic\_gpt – Score 79.00 – generic\_gpt/t2287\_gpt.txt}  \label{ex:f1_pos_015}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} my \textbf{life} is just … \textbf{background} \textbf{noise}.
I ’m not completely \textbf{isolated}.
I have \textbf{coworkers} I \textbf{chat} with, a \textbf{couple} of \textbf{old} \textbf{friends} I \textbf{send} memes to, \textbf{family} \textbf{group} \textbf{chats} that \textbf{light} up on holidays.
So on \textbf{paper} I ’m “ not alone. ” But it \textbf{feels} \textbf{like} I ’m just \textbf{orbiting} \textbf{everyone} else ’s \textbf{lives} instead of actually being in them.
I \textbf{notice} it \textbf{most} in the \textbf{quiet} \textbf{parts} of the \textbf{day}.
I ’ll have \textbf{something} happen—good or bad—and \textbf{realize} there ’s no one I instinctively \textbf{want} to \textbf{tell}.
Or I ’ll \textbf{scroll} through my \textbf{contacts} and \textbf{realize} that every \textbf{name} comes with a hesitation : “ We haven't \textbf{talked} in a \textbf{while}, this will be \textbf{weird} ” or “ They ’re probably \textbf{busy}, I don't \textbf{want} to \textbf{bother} them. ” So I don't \textbf{message} \textbf{anyone}.
Then I \textbf{feel} even \textbf{more} distant, which \textbf{makes} it harder the next \textbf{time}.
It ’s \textbf{like} a slow erosion. \textbf{Social} \textbf{media} \textbf{makes} it \textbf{worse}.
I \textbf{see} \textbf{people} posting \textbf{group} \textbf{photos}, \textbf{inside} \textbf{jokes} in the comments, tagging each \textbf{other} in \textbf{everything}.
I ’m there too, technically, but \textbf{more} \textbf{like} a ghost \textbf{watching} from the sidelines.
Sometimes I ’ll leave a comment and it just \textbf{gets} buried under \textbf{everyone} else ’s, and I \textbf{feel} \textbf{stupid} for even \textbf{trying} to wedge myself into a \textbf{space} that clearly isn't mine.
I ’m also \textbf{tired} of being the one who \textbf{reaches} out \textbf{first}.
I ’ve \textbf{noticed} that if I \textbf{stop} \textbf{initiating}, \textbf{things} just … \textbf{stop}.
No one \textbf{checks} in, no one \textbf{says} “ hey, haven't heard from you in a \textbf{while}. ” \textbf{Days} \textbf{turn} into \textbf{weeks}, and the \textbf{silence} \textbf{kind} of confirms this fear that maybe I was never that important to \textbf{anyone} in the \textbf{first} \textbf{place}.
Just convenient when I \textbf{happened} to be around.
The \textbf{worst} \textbf{part} is how it ’s \textbf{changing} me.
I can \textbf{feel} myself becoming \textbf{more} \textbf{awkward}, \textbf{more} withdrawn.
When I ’m actually around \textbf{people}, I second-guess \textbf{everything} I \textbf{say}.
I \textbf{replay} \textbf{conversations} later and cringe at myself, \textbf{convinced} I came off as \textbf{weird} or \textbf{boring}.
It ’s exhausting.
I don't even \textbf{know} what I ’m hoping for by writing this.
Maybe I just \textbf{needed} to \textbf{say} out \textbf{loud} that I \textbf{feel} \textbf{invisible} \textbf{most} of the \textbf{time}, even when I ’m technically “ with ” \textbf{people}.
It ’s a \textbf{strange} \textbf{kind} of loneliness : not the absence of \textbf{others}, but the absence of \textbf{feeling} \textbf{like} I matter to \textbf{anyone} in a \textbf{real} \textbf{way}.

% matched lemmas: anyone, awkward, background, bad, boring, bother, busy, change, chat, check, contact, conversation, convince, couple, coworker, day, dramatic, everyone, everything, explain, family, feel, first, friend, get, group, happen, initiate, inside, invisible, isolate, joke, kind, know, life, light, like, loud, make, medium, message, more, most, name, need, noise, notice, old, orbit, other, paper, part, people, photo, place, quiet, reach, real, realize, replay, say, scroll, see, send, silence, social, something, sound, space, stop, strange, stupid, talk, tell, thing, time, tire, try, turn, want, watch, way, week, weird, while
\end{textsample}
