\begin{textsample}{POS Dim 1 – generic\_gpt – Score 91.00 – generic\_gpt/t1839\_gpt.txt}  \label{ex:f1_pos_001}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} I ’m slowly \textbf{disappearing} from my \textbf{own} \textbf{life}.
I ’m in this \textbf{weird} \textbf{place} where, on \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, I pay my bills, I \textbf{answer} emails, I \textbf{say} “ not \textbf{much}, you? ” when \textbf{people} \textbf{ask} how I ’m doing.
I \textbf{show} up, I \textbf{smile}, I \textbf{make} \textbf{small} \textbf{talk}.
But underneath that, it ’s \textbf{like} there ’s this \textbf{constant}, low-level \textbf{ache} of being alone that never really \textbf{goes} away.
What ’s \textbf{messing} with me is that I ’m not completely \textbf{isolated}.
I have \textbf{acquaintances}. \textbf{People} at \textbf{work} \textbf{know} my \textbf{name}.
Sometimes I even \textbf{get} \textbf{invited} to \textbf{group} \textbf{things}, \textbf{like} birthday drinks or office lunches.
But I always \textbf{feel} \textbf{like} an \textbf{extra}. \textbf{Like} if I \textbf{stopped} \textbf{showing} up, the dynamic wouldn't \textbf{change}.
They might \textbf{notice} once, \textbf{say} “ oh, where ’s [ me ]? ” and then just \textbf{move} on.
I \textbf{miss} \textbf{feeling} \textbf{known}.
I \textbf{miss} when \textbf{people} \textbf{used} to \textbf{text} me just to \textbf{send} a dumb meme or \textbf{ask} how my \textbf{day} was, not because they \textbf{needed} \textbf{something} or it was \textbf{part} of a \textbf{group} \textbf{chat}.
I \textbf{scroll} through my \textbf{messages} and it ’s basically a graveyard of \textbf{old} \textbf{conversations} that just … faded.
No fights, no drama, just slowly shorter \textbf{replies} until \textbf{nothing}.
I ’ve \textbf{tried} to “ \textbf{fix} ” it.
I ’ve \textbf{joined} clubs, \textbf{gone} to meetups, \textbf{tried} to be \textbf{more} \textbf{open} and vulnerable in \textbf{conversations}.
But there ’s this \textbf{wall} I can't \textbf{seem} to \textbf{get} past.
I can \textbf{talk} about \textbf{surface} \textbf{stuff}, even share a few personal \textbf{things}, but I never \textbf{feel} that click where you \textbf{realize}, “ Oh, this \textbf{person} actually \textbf{sees} me. ” I always \textbf{feel} \textbf{like} I ’m performing a \textbf{version} of myself that ’s \textbf{easier} to \textbf{like}. \textbf{Nights} are the \textbf{worst}.
I come \textbf{home}, eat alone, \textbf{sit} on my \textbf{phone}, \textbf{watch} \textbf{other} \textbf{people} ’s \textbf{lives} \textbf{happening} in \textbf{real} \textbf{time}. \textbf{Group} \textbf{photos}, \textbf{inside} \textbf{jokes}, “ had the best \textbf{night} with my favorite \textbf{people}. ” I ’m happy for them in theory, but it also \textbf{feels} \textbf{like} I ’m standing \textbf{outside} a house in winter, \textbf{looking} through the \textbf{window} at \textbf{everyone} else \textbf{sitting} by the fire.
I don't even \textbf{know} what I ’m \textbf{expecting} from posting this.
I \textbf{guess} I just \textbf{wanted} to \textbf{put} it somewhere instead of letting it bounce around in my \textbf{head}.
It ’s \textbf{tiring}, \textbf{feeling} this \textbf{invisible} all the \textbf{time}.

% matched lemmas: ache, acquaintance, answer, ask, bad, change, chat, constant, conversation, day, disappear, dramatic, easy, everyone, expect, explain, extra, feel, fine, fix, get, go, group, guess, happen, head, home, inside, invisible, invite, isolate, job, join, joke, know, life, like, look, make, mess, message, miss, more, move, much, name, need, night, nothing, notice, old, open, other, outside, own, paper, part, people, person, phone, photo, place, put, real, realize, reply, say, scroll, see, seem, send, show, sit, small, smile, something, sound, stop, stuff, surface, talk, text, thing, time, tire, try, use, version, wall, want, watch, weird, window, work
\end{textsample}
