\begin{textsample}{POS Dim 1 – generic\_gpt – Score 79.00 – generic\_gpt/t967\_gpt.txt}  \label{ex:f1_pos_017}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} I ’m living behind \textbf{glass}.
My \textbf{days} are technically “ \textbf{full} ” — \textbf{work}, \textbf{errands}, \textbf{random} \textbf{conversations} with \textbf{coworkers} about TV \textbf{shows} or \textbf{weekend} \textbf{plans} I won't be \textbf{part} of — but underneath all of that I \textbf{feel} completely disconnected.
I ’m around \textbf{people} all the \textbf{time} and still \textbf{feel} \textbf{like} I ’m on mute. \textbf{Everyone} else \textbf{seems} to have these \textbf{invisible} threads tying them to \textbf{others} : \textbf{group} \textbf{chats}, \textbf{inside} \textbf{jokes}, \textbf{someone} to \textbf{text} when \textbf{something} \textbf{small} or \textbf{stupid} \textbf{happens}.
I don't have that.
If \textbf{something} funny or upsetting \textbf{happens}, it just sort of dies in my \textbf{head} because there ’s no one I \textbf{feel} \textbf{close} enough to share it with.
What really \textbf{gets} to me is how optional I \textbf{seem} to be in \textbf{other} \textbf{people} ’s \textbf{lives}.
If I don't \textbf{reach} out, \textbf{nothing} \textbf{happens}.
No one \textbf{checks} in.
No one \textbf{notices} if I \textbf{go} \textbf{quiet}.
I can \textbf{disappear} from \textbf{social} \textbf{media} for \textbf{days} and it doesn't \textbf{change} \textbf{anything}.
I \textbf{keep} \textbf{thinking} : if I just \textbf{stopped} \textbf{trying}, how long would it take before \textbf{anyone} \textbf{realized}?
And I hate that my brain even \textbf{goes} there, but it does.
I also \textbf{feel} stuck in this loop where loneliness \textbf{makes} me \textbf{weird} and \textbf{awkward}, and then being \textbf{weird} and \textbf{awkward} \textbf{makes} me \textbf{more} \textbf{isolated}.
I overthink every \textbf{interaction} : “ Did I \textbf{talk} too \textbf{much}?
Not enough?
Did I \textbf{sound} desperate? ” Then I \textbf{replay} it later and cringe at myself, which \textbf{makes} me \textbf{want} to avoid \textbf{people} even \textbf{more}.
It ’s exhausting. \textbf{Nights} are the \textbf{worst}.
There ’s \textbf{something} about \textbf{turning} off the \textbf{lights} and \textbf{knowing} no one is \textbf{going} to \textbf{call} or \textbf{text}, that no one is wondering how my \textbf{day} \textbf{went}.
I \textbf{lie} there \textbf{scrolling} and \textbf{see} \textbf{people} posting pictures with \textbf{friends}, partners, \textbf{families}, and it just reinforces this \textbf{feeling} that I ’m some \textbf{kind} of \textbf{extra} in \textbf{everyone} else ’s \textbf{story}.
I ’m not even \textbf{sure} what I ’m hoping for by writing this.
I \textbf{guess} I just \textbf{wanted} to \textbf{put} it somewhere \textbf{outside} my \textbf{own} \textbf{head} for once.

% matched lemmas: anyone, anything, awkward, bad, call, change, chat, check, close, conversation, coworker, day, disappear, dramatic, errand, everyone, explain, extra, family, feel, feeling, friend, full, get, glass, go, group, guess, happen, head, inside, interaction, invisible, isolate, joke, keep, kind, know, lie, life, light, like, make, medium, more, much, night, nothing, notice, other, outside, own, part, people, plan, put, quiet, random, reach, realize, replay, scroll, see, seem, show, small, social, someone, something, sound, stop, story, stupid, sure, talk, text, think, time, try, turn, want, weekend, weird, work
\end{textsample}
