\begin{textsample}{POS Dim 1 – human – Score 50.00 – human/t1264\_human.txt}  \label{ex:f1_pos_033}
I ’m lonely in a very literal \textbf{sense}.
I live alone, and I \textbf{go} \textbf{days} without \textbf{talking} to \textbf{anyone}.
No \textbf{messages}, no \textbf{calls}.
Just long stretches of \textbf{silence} in my apartment.
After a \textbf{while} it \textbf{starts} to \textbf{feel} unreal, \textbf{like} I ’m \textbf{watching} my \textbf{life} instead of living it.
Around my \textbf{family}, I mask it well.
Too well.
I \textbf{show} up calm, functional, \textbf{normal} enough that it ’s \textbf{easier} for everyone—including me—to \textbf{pretend} I ’m \textbf{okay}.
I \textbf{think} the topic of my loneliness is uncomfortable for them, so it never really comes up.
It ’s \textbf{easier} to \textbf{assume} I ’m \textbf{fine} than to \textbf{open} \textbf{something} \textbf{none} of us \textbf{know} how to handle.
Because of that, I \textbf{feel} \textbf{like} I ’m on my \textbf{own} with this.
Not abandoned—just unsupported in a \textbf{way} that ’s \textbf{quiet} and unspoken.
What \textbf{makes} it \textbf{worse} is that I technically have freedom.
I ’m an adult.
No one is \textbf{stopping} me from \textbf{changing} my \textbf{life}.
I \textbf{know} what I \textbf{want} to do.
I \textbf{know} the steps.
And still, I don't have the courage to do them.
That freedom—having \textbf{full} responsibility for my choices—feels \textbf{like} a prison.
There ’s no obvious obstacle I can point to, so the blame \textbf{turns} inward.
I \textbf{feel} \textbf{like} I ’m wasting \textbf{time}. \textbf{Like} I ’ve failed at \textbf{something} basic \textbf{everyone} else \textbf{seems} to manage.
Each \textbf{day} I stay stuck, that \textbf{feeling} \textbf{gets} \textbf{heavier}.
I wish I had \textbf{someone} to lean on \textbf{while} I figured this out. \textbf{Someone} who could just \textbf{sit} in it with me so it didn't all \textbf{feel} \textbf{like} it rested on my shoulders alone.
But it doesn't \textbf{feel} \textbf{like} that ’s an option.
It \textbf{feels} \textbf{like} it ’s up to me—and I don't trust myself enough \textbf{right} now to carry it well.
I still function.
I \textbf{work}.
I eat.
I \textbf{get} through the \textbf{day}.
But underneath all of that is this \textbf{constant} \textbf{sense} of being trapped by my \textbf{own} \textbf{life}, frozen by choice, and quietly disappointed in myself for not \textbf{moving}.
I ’m not posting this for advice or reassurance.
I just \textbf{needed} to \textbf{say} it somewhere \textbf{honest}, because holding it in \textbf{makes} it \textbf{feel} unbearable.
If this resonates with you, you ’re not alone in it.

% matched lemmas: anyone, assume, bad, call, change, constant, day, easy, everyone, family, feel, feeling, fine, full, get, go, heavy, honest, know, life, like, make, message, move, need, none, normal, okay, open, own, pretend, quiet, right, say, seem, sense, show, silence, sit, someone, something, start, stop, talk, think, time, turn, want, watch, way, while, work
\end{textsample}
