\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 53.00 – summary\_guided\_gpt/t1837\_gpt.txt}  \label{ex:f1_pos_025}
Lately I ’ve been stuck on this thought that I ’m no one ’s “ favorite \textbf{person}. ” \textbf{Like}, if I \textbf{disappeared} tomorrow, it would probably take \textbf{weeks} before \textbf{anyone} \textbf{realized} \textbf{something} was wrong.
I don't \textbf{feel} \textbf{like} I truly matter to \textbf{anyone}.
I ’ve \textbf{noticed} that communication with pretty \textbf{much} \textbf{everyone} in my \textbf{life} only \textbf{happens} if I ’m the one who \textbf{starts} it.
If I don't \textbf{text} \textbf{first}, \textbf{days} or \textbf{weeks} \textbf{go} by in \textbf{silence}.
Nobody \textbf{seems} excited to \textbf{reach} out to me, to share their good news, to \textbf{say} “ hey, I \textbf{thought} of you. ” What really hurts is my \textbf{family}.
I recently found out my mom has been taking my younger siblings on vacations and cruises without ever \textbf{inviting} me.
There are \textbf{family} \textbf{group} \textbf{chats} and \textbf{plans} for trips and holidays that I just … don't \textbf{exist} in.
I ’ll hear about these \textbf{things} after the fact, \textbf{like} an outsider \textbf{getting} the recap of \textbf{someone} else ’s \textbf{life}.
I can understand that my \textbf{friends} have \textbf{other} \textbf{close} \textbf{friends}, and I don't \textbf{expect} to be \textbf{anyone} ’s number one.
But being \textbf{shut} out by my \textbf{own} \textbf{family} \textbf{feels} \textbf{like} a different \textbf{kind} of rejection.
It \textbf{makes} me \textbf{feel} pathetic that I ’m always the one who \textbf{calls}, \textbf{checks} in, and \textbf{asks} to \textbf{hang} out, \textbf{while} \textbf{everyone} else already \textbf{seems} to have “ their ” \textbf{people}. \textbf{Part} of me \textbf{wants} to just \textbf{stop} \textbf{trying}, \textbf{stop} \textbf{reaching} out, and \textbf{see} who actually \textbf{notices}.
But I ’m \textbf{scared} that if I do that, I ’ll just \textbf{end} up even \textbf{more} alone than I already \textbf{feel}.
I don't \textbf{know} how to \textbf{fix} any of this, or if it ’s even fixable.
I just \textbf{feel} stuck in this \textbf{place} where I ’m present in \textbf{other} \textbf{people} ’s \textbf{lives}, but never essential.

% matched lemmas: anyone, ask, call, chat, check, close, day, disappear, end, everyone, exist, expect, family, feel, first, fix, friend, get, go, group, hang, happen, invite, kind, know, life, like, make, more, much, notice, other, own, part, people, person, place, plan, reach, realize, say, scare, see, seem, shut, silence, someone, something, start, stop, text, thing, think, try, want, week, while
\end{textsample}
