\begin{textsample}{POS Dim 1 – generic\_gpt – Score 79.00 – generic\_gpt/t402\_gpt.txt}  \label{ex:f1_pos_019}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} my \textbf{life} is \textbf{happening} behind a \textbf{glass} \textbf{wall}.
On \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, I \textbf{respond} to \textbf{messages}, I \textbf{show} up when I ’m \textbf{supposed} to.
I \textbf{make} \textbf{small} \textbf{talk} about \textbf{work}, \textbf{weather}, TV \textbf{shows}. \textbf{People} \textbf{laugh} at my \textbf{jokes} sometimes.
From the \textbf{outside} I probably \textbf{look} \textbf{normal}, maybe even “ \textbf{social}. ” But it all \textbf{feels} \textbf{like} acting.
I can \textbf{play} the role, but once I ’m back \textbf{home} and the \textbf{door} \textbf{shuts}, it ’s just this \textbf{heavy} \textbf{silence} that \textbf{feels} louder than \textbf{anything}.
What \textbf{gets} to me is the lack of \textbf{anyone} who really \textbf{knows} me.
I don't mean \textbf{knowing} my favorite movie or my coffee order.
I mean the \textbf{kind} of \textbf{knowing} where you can \textbf{send} a half-finished \textbf{text} and they already understand, or where you can \textbf{sit} together in \textbf{silence} and it doesn't \textbf{feel} \textbf{awkward}.
I don't have that with \textbf{anyone}.
I have “ we should \textbf{catch} up sometime ” \textbf{people}, not “ I ’m \textbf{outside}, \textbf{open} the \textbf{door} ” \textbf{people}.
I \textbf{try} to \textbf{reach} out, but it always \textbf{feels} one-sided.
I ’m the one \textbf{asking} how they ’re doing, suggesting \textbf{plans}, \textbf{trying} to \textbf{keep} the \textbf{conversation} alive.
When I \textbf{stop} \textbf{initiating}, \textbf{everything} just…stops.
It ’s \textbf{like} I \textbf{disappear} from their world unless I ’m actively reminding them I \textbf{exist}.
And then I \textbf{start} wondering if I ’m just \textbf{annoying} them, if they ’re only \textbf{responding} out of politeness.
I ’ve also \textbf{noticed} I ’m \textbf{starting} to hold back \textbf{more}.
I censor myself because I don't \textbf{want} to come across as \textbf{needy} or depressing.
So I \textbf{end} up \textbf{talking} about \textbf{nothing}, and then I \textbf{feel} even \textbf{more} disconnected because I ’m not actually sharing \textbf{anything} \textbf{real}.
It ’s \textbf{like} I ’m protecting \textbf{people} from the \textbf{parts} of me that are actually lonely, which just \textbf{makes} me lonelier. \textbf{Nights} are the \textbf{worst}.
That ’s when it \textbf{hits} me that no one is \textbf{thinking} about me, no one is wondering how my \textbf{day} \textbf{went}, no one is \textbf{waiting} for my \textbf{message}.
I \textbf{scroll}, I lurk, I \textbf{watch} \textbf{other} \textbf{people} ’s \textbf{lives} through screens, and it just reinforces this \textbf{feeling} that I ’m on the \textbf{outside} of \textbf{everything}, \textbf{watching} \textbf{everyone} else \textbf{belong} to \textbf{something} I can't \textbf{seem} to \textbf{reach}.

% matched lemmas: annoy, anyone, anything, ask, awkward, bad, belong, catch, conversation, day, disappear, door, dramatic, end, everyone, everything, exist, explain, feel, feeling, fine, get, glass, go, happen, heavy, hit, home, initiate, job, joke, keep, kind, know, laugh, life, like, look, make, message, more, needy, night, normal, nothing, notice, open, other, outside, paper, part, people, plan, play, reach, real, respond, scroll, seem, send, show, shut, silence, sit, small, social, something, sound, start, stop, suppose, talk, text, think, try, wait, wall, want, watch, weather, work
\end{textsample}
