\begin{textsample}{POS Dim 1 – generic\_gpt – Score 79.00 – generic\_gpt/t735\_gpt.txt}  \label{ex:f1_pos_016}
I don't really \textbf{know} how to \textbf{say} this in a \textbf{way} that doesn't \textbf{sound} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} my \textbf{life} is \textbf{happening} behind \textbf{glass}.
On \textbf{paper} I ’m not “ alone. ” I have \textbf{coworkers}, a \textbf{couple} of \textbf{old} \textbf{friends} I \textbf{text} sometimes, \textbf{family} \textbf{chats} that \textbf{light} up with memes and logistics.
But I \textbf{feel} \textbf{like} I ’m always slightly out of phase with \textbf{everyone} else, \textbf{like} I ’m there physically but not really *with* them.
I \textbf{go} \textbf{days} without \textbf{using} my voice for \textbf{anything} besides “ thank you ” at a checkout or “ have a good one ” at \textbf{work}.
I ’ll rehearse \textbf{conversations} in my head—what I ’d \textbf{say} if \textbf{someone} actually \textbf{asked} how I ’m doing, what I ’d \textbf{tell} a \textbf{friend} if I \textbf{felt} safe enough to be honest—and then the \textbf{moment} passes and I just default to “ I ’m \textbf{fine}, you? ” because I don't \textbf{want} to \textbf{make} \textbf{things} \textbf{weird}.
The \textbf{weird} \textbf{part} is I ’m not even \textbf{sure} what I ’m \textbf{missing} anymore.
I don't \textbf{know} if it ’s a romantic partner, deeper friendships, or just one \textbf{person} who genuinely \textbf{wants} to \textbf{know} what my \textbf{day} \textbf{looked} \textbf{like}.
I \textbf{scroll} through \textbf{social} \textbf{media} and \textbf{see} \textbf{people} posting \textbf{group} \textbf{photos}, trips, little \textbf{inside} \textbf{jokes} in the comments, and I \textbf{feel} \textbf{like} I ’m \textbf{watching} a \textbf{life} I somehow didn't qualify for.
I \textbf{try} to \textbf{reach} out sometimes.
I ’ll \textbf{send} a \textbf{message}, suggest a \textbf{plan}, and then spend the whole \textbf{time} terrified I ’m being \textbf{annoying} or clingy.
If they take a \textbf{while} to \textbf{answer}, I immediately \textbf{assume} I ’ve overstepped.
If they \textbf{say} they ’re \textbf{busy}, I \textbf{tell} myself they ’re just being \textbf{polite} and don't really \textbf{want} to \textbf{see} me.
It ’s \textbf{like} my brain is determined to interpret \textbf{everything} in the \textbf{most} self-rejecting \textbf{way} possible.
I ’ve also \textbf{noticed} how loneliness \textbf{makes} me \textbf{smaller}.
I share less.
I take up less \textbf{space}.
I censor my interests because I don't \textbf{want} to be “ too \textbf{much}. ” Then I \textbf{feel} \textbf{invisible} and resentful, but it ’s a situation I helped create by not \textbf{showing} up as myself. \textbf{Nights} are the \textbf{worst}.
There ’s this \textbf{heavy} \textbf{silence} that \textbf{feels} almost physical.
I ’ll \textbf{lie} there \textbf{thinking} about how, if I \textbf{disappeared}, it would take a \textbf{while} for \textbf{anyone} to \textbf{notice} in a concrete \textbf{way}. \textbf{People} would be “ shocked ” in the abstract, but day-to-day, not \textbf{much} would \textbf{change}.
I don't really \textbf{know} what I \textbf{want} from posting this.
Maybe I just \textbf{needed} to \textbf{put} it somewhere \textbf{outside} my \textbf{own} \textbf{head} for once.

% matched lemmas: annoy, answer, anyone, anything, ask, assume, bad, busy, change, chat, conversation, couple, coworker, day, disappear, dramatic, everyone, everything, family, feel, fine, friend, glass, go, group, happen, head, heavy, inside, invisible, joke, know, lie, life, light, like, look, make, medium, message, miss, moment, most, much, need, night, notice, old, outside, own, paper, part, people, person, photo, plan, polite, put, reach, say, scroll, see, send, show, silence, small, social, someone, sound, space, sure, tell, text, thing, think, time, try, use, want, watch, way, weird, while, work
\end{textsample}
