\begin{textsample}{POS Dim 1 – generic\_gpt – Score 81.00 – generic\_gpt/t2407\_gpt.txt}  \label{ex:f1_pos_009}
I ’ve been struggling with a very specific \textbf{kind} of loneliness lately, and I don't really \textbf{know} what to do with it anymore.
On \textbf{paper}, I ’m not “ alone. ” I have \textbf{coworkers} I \textbf{get} along with, a \textbf{couple} of \textbf{friends} I \textbf{see} once in a \textbf{while}, \textbf{family} I \textbf{text} with.
But I \textbf{feel} \textbf{like} I ’m living behind a pane of \textbf{glass}.
I ’m there, visible, technically \textbf{part} of \textbf{things}, but it all \textbf{feels} \textbf{like} I ’m \textbf{watching} \textbf{someone} else ’s \textbf{life} from the \textbf{outside}.
I \textbf{keep} \textbf{noticing} how surface-level \textbf{most} of my \textbf{interactions} are.
At \textbf{work} we \textbf{talk} about projects, TV \textbf{shows}, the \textbf{weather}, the \textbf{usual} “ How was your \textbf{weekend}? ” \textbf{stuff}.
With \textbf{friends} it ’s memes, \textbf{group} \textbf{chats}, and meeting up for drinks every few \textbf{weeks}.
It all \textbf{looks} \textbf{normal}, but I never \textbf{feel} \textbf{like} I ’m actually \textbf{known}.
If I \textbf{disappeared}, I ’m not \textbf{sure} \textbf{anyone} would really \textbf{notice} for a \textbf{while}, just that the \textbf{group} \textbf{chat} \textbf{got} a bit \textbf{quieter}.
I \textbf{think} what I ’m \textbf{missing} is that \textbf{feeling} of being \textbf{someone} ’s “ \textbf{person}. ” Not in a romantic-only \textbf{sense}, just … \textbf{someone} who \textbf{thinks} of you \textbf{first}, who \textbf{wants} to \textbf{tell} you news as it \textbf{happens}, who \textbf{checks} in without it \textbf{feeling} \textbf{like} a chore.
I don't have that.
I ’m always the one \textbf{reaching} out, organizing, \textbf{asking} how \textbf{people} are.
When I \textbf{stop}, \textbf{everything} just \textbf{goes} \textbf{silent}.
It ’s \textbf{messing} with my \textbf{sense} of self-worth \textbf{more} than I \textbf{want} to admit.
I \textbf{start} \textbf{assuming} I ’m boring or draining or just not that important.
I \textbf{replay} \textbf{conversations} later and pick apart every \textbf{awkward} pause, every \textbf{time} I maybe overshared or \textbf{made} a \textbf{joke} that didn't land.
Then I \textbf{pull} back, which just \textbf{makes} the distance worse. \textbf{Nights} are the hardest.
I ’ll be \textbf{lying} in \textbf{bed}, \textbf{scrolling}, \textbf{seeing} \textbf{everyone} ’s \textbf{photos} with \textbf{friends}, partners, \textbf{families}, and I \textbf{feel} this \textbf{heavy}, physical \textbf{ache} in my chest.
I \textbf{want} to \textbf{send} a “ hey, are you awake? ” \textbf{message} to \textbf{someone}, but there isn't \textbf{anyone} I \textbf{feel} \textbf{close} enough to for that to not be \textbf{weird}.
So I just \textbf{put} my \textbf{phone} down and stare at the ceiling.
I don't even \textbf{know} if I ’m \textbf{looking} for advice.
I just \textbf{needed} to \textbf{say} this somewhere.
It ’s exhausting to \textbf{keep} \textbf{pretending} I ’m \textbf{fine} when I \textbf{feel} this empty and disconnected \textbf{most} of the \textbf{time}.

% matched lemmas: ache, anyone, ask, assume, awkward, bed, chat, check, close, conversation, couple, coworker, disappear, everyone, everything, family, feel, fine, first, friend, get, glass, go, group, happen, heavy, interaction, joke, keep, kind, know, lie, life, like, look, make, mess, message, miss, more, most, need, night, normal, notice, outside, paper, part, people, person, phone, photo, pretend, pull, put, quiet, reach, replay, say, scroll, see, send, sense, show, silent, someone, start, stop, stuff, sure, talk, tell, text, thing, think, time, usual, want, watch, weather, week, weekend, weird, while, work
\end{textsample}
