\begin{textsample}{POS Dim 1 – human – Score 53.00 – human/t2136\_human.txt}  \label{ex:f1_pos_031}
I lost my last grandma two months before this new year, and it ’s been \textbf{sitting} \textbf{heavy} on me in this \textbf{strange}, \textbf{quiet} \textbf{way}.
We weren't super \textbf{close}, and she wasn't the “ favourite ” grandma \textbf{people} always \textbf{talk} about.
But grief doesn't care about that.
It just \textbf{shows} up, uninvited, and takes \textbf{space} you didn't even \textbf{know} you had.
Not only this but hearing uni classmates of mine mentioning that thue haven't been \textbf{home} in a \textbf{while} and how they \textbf{miss} their parents and grandparents since they 're not from Bucharest but \textbf{other} zones of Romania..makes me \textbf{feel} even emptier as \textbf{time} \textbf{goes} on, \textbf{while} I 'm \textbf{trying} to handle grief in my \textbf{own} way.{\EmojiFont 😔} What ’s been \textbf{hitting} me hardest is how it creeps into the \textbf{small} \textbf{moments} : when I ’m \textbf{walking} \textbf{home}, when I ’m washing dishes, when I ’m \textbf{trying} to fall asleep.
It ’s not the \textbf{dramatic} \textbf{kind} of sadness \textbf{people} \textbf{expect}.
It ’s \textbf{more} \textbf{like} this dull \textbf{ache} that \textbf{keeps} reminding me she ’s not here anymore.
She was just … always there.
A steady \textbf{background} presence I never \textbf{questioned}.
And now there ’s this \textbf{weird} \textbf{silence} where she \textbf{used} to be, \textbf{like} a \textbf{room} in my mind that suddenly \textbf{went} dark.
I didn't \textbf{realize} how \textbf{much} those \textbf{quiet}, familiar presences matter until they ’re \textbf{gone}.
I didn't \textbf{expect} to \textbf{miss} her voice, or the \textbf{way} she repeated the \textbf{same} \textbf{stories}, or even the \textbf{way} she ’d forget \textbf{things} mid‑sentence.
But I do.
And it ’s confusing, because we weren't incredibly \textbf{close}, yet somehow her absence \textbf{feels} \textbf{like} a piece of my \textbf{life} \textbf{got} \textbf{pulled} out without warning.
It ’s \textbf{like} \textbf{something} shifted \textbf{inside} me, and I can't shift it back.
Losing her broke \textbf{something} in me I didn't \textbf{expect}.
I didn't \textbf{need} her to be my favourite for her absence to \textbf{feel} unbearable.
I don't really \textbf{know} how to \textbf{talk} about this in \textbf{real} \textbf{life}. \textbf{Everyone} around me \textbf{seems} to have \textbf{moved} on, or they \textbf{assume} I ’m \textbf{fine} because “ we weren't that \textbf{close}. ” But I ’m not \textbf{fine}.
Not really.
So I ’m \textbf{putting} it here, hoping \textbf{someone} out there understands what it ’s \textbf{like} to \textbf{miss} \textbf{someone} you weren't even \textbf{sure} you ’d \textbf{miss} this \textbf{much}.

% matched lemmas: ache, assume, background, close, dramatic, everyone, expect, feel, fine, get, go, heavy, hit, home, inside, keep, kind, know, life, like, miss, moment, more, move, much, need, other, own, people, pull, put, question, quiet, real, realize, room, same, seem, show, silence, sit, small, someone, something, space, story, strange, sure, talk, thing, time, try, use, walk, way, weird, while
\end{textsample}
