\begin{textsample}{POS Dim 1 – generic\_gpt – Score 83.00 – generic\_gpt/t2316\_gpt.txt}  \label{ex:f1_pos_005}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but I \textbf{feel} \textbf{like} I ’m living next to my \textbf{own} \textbf{life} instead of \textbf{inside} it.
On \textbf{paper}, I ’m not “ alone. ” I have \textbf{coworkers}, \textbf{acquaintances}, a \textbf{couple} of \textbf{people} I could technically \textbf{text} if I really \textbf{needed} \textbf{something}.
I \textbf{show} up to \textbf{work}, \textbf{make} \textbf{small} \textbf{talk} about TV \textbf{shows}, complain about the \textbf{weather}, \textbf{laugh} at the \textbf{right} \textbf{moments}. \textbf{People} would probably describe me as “ nice ” or “ \textbf{quiet} but friendly. ” But once I \textbf{get} \textbf{home} and \textbf{close} the \textbf{door}, it ’s \textbf{like} the world just forgets I \textbf{exist}, and honestly, I \textbf{kind} of forget too.
What \textbf{messes} with my \textbf{head} is that I don't even \textbf{know} how to bridge the gap between “ friendly ” and “ actually \textbf{close}. ” I \textbf{watch} \textbf{other} \textbf{people} slip into friendships so easily—inside \textbf{jokes}, \textbf{group} \textbf{chats} buzzing all \textbf{day}, \textbf{weekend} \textbf{plans} that just \textbf{seem} to form out of nowhere.
Meanwhile, I ’m \textbf{sitting} there overthinking whether \textbf{sending} a meme to \textbf{someone} is “ too \textbf{much} ” or if I ’ll come across as \textbf{annoying}.
I ’m \textbf{tired} of being the \textbf{person} who only \textbf{gets} \textbf{invited} as an afterthought, or not at all.
I ’m \textbf{tired} of \textbf{realizing} that if I \textbf{stopped} \textbf{initiating} with the few \textbf{people} I do \textbf{talk} to, the \textbf{conversations} would just die.
It \textbf{makes} me \textbf{feel} \textbf{like} a placeholder in \textbf{other} \textbf{people} ’s \textbf{lives}, \textbf{someone} they don't dislike but don't really \textbf{think} about either.
It ’s not \textbf{like} I haven't \textbf{tried}.
I ’ve \textbf{joined} clubs, \textbf{gone} to meetups, \textbf{forced} myself into situations that are uncomfortable for me as an introvert.
I \textbf{show} up, I \textbf{smile}, I \textbf{try} to be interested in \textbf{others}.
But the connections never \textbf{seem} to stick. \textbf{People} are \textbf{polite}, then they drift back into their established \textbf{circles}, and I ’m left \textbf{orbiting} on the \textbf{outside} again.
The \textbf{worst} \textbf{part} is the \textbf{way} loneliness seeps into \textbf{everything}.
It ’s not just about not having \textbf{plans} on a Friday \textbf{night}.
It ’s eating dinner at my table and \textbf{realizing} I haven't heard my \textbf{own} voice out \textbf{loud} all \textbf{day}.
It ’s having \textbf{something} funny or upsetting \textbf{happen} and instinctively \textbf{reaching} for my \textbf{phone}, then \textbf{remembering} there ’s no one I \textbf{feel} \textbf{close} enough to share it with.
It ’s \textbf{scrolling} through my \textbf{contacts} and \textbf{realizing} there isn't a single \textbf{person} I ’d \textbf{feel} comfortable \textbf{calling} just to \textbf{talk}.
I don't even \textbf{know} what I ’m \textbf{expecting} by posting this.
I \textbf{guess} I just \textbf{wanted} to \textbf{put} it into \textbf{words} somewhere, because \textbf{keeping} it all in my \textbf{head} \textbf{makes} it \textbf{feel} even \textbf{heavier}.

% matched lemmas: acquaintance, annoy, bad, call, chat, circle, close, contact, conversation, couple, coworker, day, door, dramatic, everything, exist, expect, explain, feel, force, get, go, group, guess, happen, head, heavy, home, initiate, inside, invite, join, joke, keep, kind, know, laugh, life, like, loud, make, mess, moment, much, need, night, orbit, other, outside, own, paper, part, people, person, phone, plan, polite, put, quiet, reach, realize, remember, right, scroll, seem, send, show, sit, small, smile, someone, something, sound, stop, talk, text, think, tire, try, want, watch, way, weather, weekend, word, work
\end{textsample}
