\begin{textsample}{POS Dim 1 – generic\_gpt – Score 85.00 – generic\_gpt/t2641\_gpt.txt}  \label{ex:f1_pos_002}
I don't really \textbf{know} how to \textbf{talk} about this in \textbf{real} \textbf{life}, so I ’m \textbf{dumping} it here instead.
Lately I ’ve been \textbf{feeling} this \textbf{weird} combination of being “ connected ” and completely alone at the \textbf{same} \textbf{time}.
I have \textbf{people} I \textbf{message}, \textbf{group} \textbf{chats} that ping all \textbf{day}, \textbf{social} \textbf{media} feeds that never \textbf{end}, but when I \textbf{close} my \textbf{phone}, the \textbf{silence} in my \textbf{room} \textbf{feels} almost physical.
It ’s \textbf{like} all those little \textbf{interactions} are just \textbf{background} \textbf{noise}, and underneath it there ’s this \textbf{heavy}, empty \textbf{space}.
I ’m not totally \textbf{isolated}.
I have \textbf{coworkers}, some \textbf{acquaintances}, \textbf{people} I can be “ friendly ” with.
But I don't \textbf{feel} \textbf{known} by \textbf{anyone}. \textbf{Conversations} stay on the \textbf{surface} : \textbf{work}, memes, \textbf{weekend} \textbf{plans}.
I can be standing in a \textbf{room} \textbf{full} of \textbf{people} and \textbf{feel} \textbf{like} I ’m behind \textbf{glass}.
They \textbf{see} a \textbf{version} of me, but it ’s \textbf{like} I ’m not really there.
I ’ve \textbf{tried} to “ \textbf{fix} ” it in the \textbf{ways} you ’re \textbf{supposed} to.
I \textbf{joined} a hobby \textbf{group}.
I \textbf{go} to \textbf{social} events sometimes, even when I don't \textbf{feel} \textbf{like} it.
I \textbf{make} \textbf{small} \textbf{talk}, \textbf{ask} \textbf{questions}, \textbf{try} to be interested.
Then I come \textbf{home} and \textbf{feel} \textbf{more} drained and alone than I did before, because it just reminds me that I don't really \textbf{belong} anywhere.
I ’m always the \textbf{extra} \textbf{person}, the one who ’s there but not essential, the one \textbf{people} are \textbf{fine} with but wouldn't really \textbf{miss}.
What \textbf{bothers} me \textbf{most} is how it ’s \textbf{changing} me.
I can \textbf{feel} myself \textbf{getting} \textbf{quieter}, \textbf{more} withdrawn.
I \textbf{start} second-guessing \textbf{everything} I \textbf{say}, \textbf{assuming} \textbf{people} are just being \textbf{polite}.
I \textbf{replay} \textbf{interactions} in my \textbf{head} and pick apart every \textbf{awkward} pause.
Sometimes I cancel \textbf{plans} last minute because the idea of \textbf{sitting} in a \textbf{group} and still \textbf{feeling} lonely is somehow \textbf{worse} than just staying \textbf{home}. \textbf{Nights} are the hardest.
That ’s when it \textbf{hits} me that no one is \textbf{going} to \textbf{text} to \textbf{check} in, no one is wondering how my \textbf{day} \textbf{went}, no one is saving \textbf{stories} to \textbf{tell} me later.
I \textbf{scroll}, I \textbf{watch} \textbf{random} videos, I listen to podcasts just to have some \textbf{kind} of human voice in the \textbf{background}.
Then I wake up and do it all again.
I don't really \textbf{know} what I ’m \textbf{expecting} by posting this.
I just \textbf{needed} to \textbf{put} it somewhere \textbf{outside} my \textbf{own} \textbf{head} for a \textbf{while}.

% matched lemmas: acquaintance, anyone, ask, assume, awkward, background, bad, belong, bother, change, chat, check, close, conversation, coworker, day, dump, end, everything, expect, extra, feel, fine, fix, full, get, glass, go, group, head, heavy, hit, home, interaction, isolate, join, kind, know, life, like, make, medium, message, miss, more, most, need, night, noise, outside, own, people, person, phone, plan, polite, put, question, quiet, random, real, replay, room, same, say, scroll, see, silence, sit, small, social, space, start, story, suppose, surface, talk, tell, text, time, try, version, watch, way, weekend, weird, while, work
\end{textsample}
