\begin{textsample}{POS Dim 1 – generic\_gpt – Score 81.00 – generic\_gpt/t1709\_gpt.txt}  \label{ex:f1_pos_007}
I ’ve been \textbf{feeling} this \textbf{weird}, \textbf{heavy} \textbf{kind} of loneliness lately that doesn't really fit into any of the \textbf{usual} categories \textbf{people} \textbf{talk} about.
I ’m not totally \textbf{isolated}.
I \textbf{work}, I \textbf{talk} to \textbf{coworkers}, I \textbf{answer} \textbf{messages} in \textbf{group} \textbf{chats}.
On \textbf{paper} I ’m “ \textbf{connected}. ” But it all \textbf{feels} \textbf{like} I ’m \textbf{playing} a role in \textbf{other} \textbf{people} ’s \textbf{lives} instead of actually being in them. \textbf{Most} of my \textbf{interactions} \textbf{feel} \textbf{like} \textbf{background} \textbf{noise}. \textbf{Small} \textbf{talk}, memes, work-related \textbf{stuff}, surface-level updates.
I can \textbf{go} \textbf{days} without \textbf{anyone} \textbf{asking} me how I ’m really doing in a \textbf{way} that suggests they actually \textbf{want} to \textbf{know}.
When I \textbf{try} to \textbf{open} up a bit, the \textbf{conversation} either \textbf{gets} redirected or brushed off with a \textbf{joke}.
I \textbf{end} up \textbf{feeling} \textbf{like} I overshared, even if I only \textbf{said} one \textbf{honest} sentence.
What \textbf{makes} it \textbf{worse} is that I \textbf{used} to have \textbf{people} I \textbf{felt} \textbf{close} to.
Not many, but enough that I \textbf{felt} \textbf{like} I had a “ \textbf{home} base ” in the world.
Over \textbf{time}, \textbf{life} just \textbf{pulled} us in different directions. \textbf{People} \textbf{moved}, \textbf{got} into serious relationships, became \textbf{busy} with kids or careers.
We still “ \textbf{keep} in \textbf{touch} ” in the vaguest \textbf{sense}, but it ’s \textbf{more} \textbf{like} we ’re \textbf{watching} each \textbf{other} ’s \textbf{lives} from the \textbf{outside} rather than living \textbf{anything} together.
I ’ve \textbf{tried} to meet new \textbf{people}, but I ’m at this age where \textbf{everyone} already \textbf{seems} to have their established \textbf{circle}.
I always \textbf{feel} \textbf{like} the \textbf{extra} \textbf{person} tagging along, the one who can be there or not and it wouldn't really \textbf{change} \textbf{anything}.
I ’m present, but not essential. \textbf{Replaceable}.
The \textbf{part} that really \textbf{messes} with me is how \textbf{invisible} this \textbf{feels}.
From the \textbf{outside}, I probably \textbf{look} \textbf{fine}.
I \textbf{show} up, I \textbf{smile}, I contribute to \textbf{conversations}.
Nobody \textbf{sees} that I \textbf{go} \textbf{home} and just \textbf{sit} in the \textbf{quiet}, \textbf{scrolling} on my \textbf{phone} because I don't \textbf{know} what else to do with myself.
I \textbf{keep} \textbf{wanting} to \textbf{send} a \textbf{message} that just \textbf{says}, “ I \textbf{feel} really alone \textbf{right} now, ” but I don't \textbf{know} who I ’d \textbf{send} it to, or what I ’d even \textbf{want} them to \textbf{say} back.
There ’s this \textbf{constant} \textbf{ache} of \textbf{wanting} to be \textbf{known}, really \textbf{known}, and at the \textbf{same} \textbf{time} \textbf{feeling} \textbf{like} I ’ve forgotten how to let \textbf{anyone} that \textbf{close}.
I ’m not \textbf{sure} if I ’ve built \textbf{walls} or if \textbf{people} just \textbf{stopped} \textbf{trying} to \textbf{look} over them.
Maybe both.
All I \textbf{know} is that I ’m \textbf{tired} of \textbf{feeling} \textbf{like} a side \textbf{character} in my \textbf{own} \textbf{life}.

% matched lemmas: ache, answer, anyone, anything, ask, background, bad, busy, change, character, chat, circle, close, connect, constant, conversation, coworker, day, end, everyone, extra, feel, fine, get, go, group, heavy, home, honest, interaction, invisible, isolate, joke, keep, kind, know, life, like, look, make, mess, message, more, most, move, noise, open, other, outside, own, paper, part, people, person, phone, play, pull, quiet, replaceable, right, same, say, scroll, see, seem, send, sense, show, sit, small, smile, stop, stuff, sure, talk, time, tire, touch, try, use, usual, wall, want, watch, way, weird, work
\end{textsample}
