\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 55.00 – summary\_guided\_gpt/t1201\_gpt.txt}  \label{ex:f1_pos_022}
I \textbf{remember} one \textbf{night} \textbf{looking} at my \textbf{phone} and \textbf{realizing} I hadn't \textbf{gotten} a meaningful \textbf{message} in … I don't even \textbf{know} how long.
Just \textbf{random} memes, \textbf{work} \textbf{stuff}, and the occasional “ how are you? ” that never \textbf{went} beyond \textbf{small} \textbf{talk}.
It \textbf{hit} me that I hadn't had a \textbf{real} \textbf{conversation} in \textbf{weeks}.
My \textbf{days} had all blurred into the \textbf{same} pattern : wake up, \textbf{go} to \textbf{work}, exchange a few surface-level comments with \textbf{coworkers}, come \textbf{home}, \textbf{scroll} on my \textbf{phone}, \textbf{sleep}.
Repeat.
I \textbf{told} myself I was “ too tired ” or “ too \textbf{busy} ” to do \textbf{anything} else, but really I was just stuck.
My \textbf{old} \textbf{friends} are far away now, and we only \textbf{talk} every once in a \textbf{while}.
I \textbf{kept} \textbf{waiting} for \textbf{something} to \textbf{change} on its \textbf{own}, \textbf{like} one \textbf{day} I ’d just magically \textbf{feel} less alone.
Instead, \textbf{everything} just \textbf{felt} empty and stale.
I ’d \textbf{catch} myself doomscrolling, not because I cared about what I was \textbf{looking} at, but because there was \textbf{nothing} else \textbf{going} on.
It \textbf{scared} me how \textbf{normal} that \textbf{started} to \textbf{feel}.
At some point I \textbf{realized} that if I didn't do \textbf{anything}, this would just \textbf{keep} being my \textbf{life}.
So I \textbf{made} a decision : \textbf{stop} \textbf{waiting} for destiny to hand me a \textbf{social} \textbf{life} and \textbf{start} \textbf{putting} myself in situations where one could actually \textbf{exist}.
I didn't \textbf{force} \textbf{conversations} or chase \textbf{people}, but I did \textbf{show} up \textbf{more}.
I gave myself chances to meet \textbf{others} instead of hiding behind the \textbf{same} routines.
It wasn't instant, but slowly my \textbf{phone} \textbf{stopped} being just a black hole of \textbf{scrolling}.
It \textbf{started} to be \textbf{something} that buzzed with actual connection.
If loneliness is \textbf{bothering} you, don't let isolation become your comfort zone. \textbf{Nothing} \textbf{changes} if \textbf{nothing} \textbf{changes}.
Even \textbf{small} steps to \textbf{put} yourself out there can \textbf{open} the \textbf{door} to \textbf{something} better.

% matched lemmas: anything, bother, busy, catch, change, conversation, coworker, day, door, everything, exist, feel, force, friend, get, go, hit, home, keep, know, life, like, look, make, message, more, night, normal, nothing, old, open, other, own, people, phone, put, random, real, realize, remember, same, scare, scroll, show, sleep, small, social, something, start, stop, stuff, talk, tell, wait, week, while, work
\end{textsample}
