\begin{textsample}{POS Dim 1 – generic\_gpt – Score 80.00 – generic\_gpt/t1229\_gpt.txt}  \label{ex:f1_pos_013}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} I ’m living behind \textbf{glass}.
On \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, I pay my bills, I occasionally \textbf{go} out with \textbf{coworkers}, my \textbf{family} \textbf{texts} me memes.
There ’s \textbf{nothing} obviously wrong.
But I \textbf{feel} \textbf{like} I ’m just … not actually there. \textbf{Like} I ’m role‑playing a \textbf{normal} \textbf{person} \textbf{while} the \textbf{real} me is somewhere far away, \textbf{watching}.
The loneliness isn't \textbf{loud}.
It ’s this low, \textbf{constant} hum.
I can be in a \textbf{room} \textbf{full} of \textbf{people} and still \textbf{feel} \textbf{like} I ’m on mute. \textbf{Everyone} else \textbf{seems} to have this \textbf{invisible} thread \textbf{connecting} them to \textbf{someone} : \textbf{group} \textbf{chats} that are actually active, \textbf{people} who \textbf{call} “ just to \textbf{talk}, ” \textbf{someone} who would \textbf{notice} if they \textbf{disappeared} for a \textbf{day}.
I don't \textbf{feel} \textbf{like} I have that.
If I \textbf{went} \textbf{quiet}, I \textbf{think} \textbf{people} would just \textbf{assume} I was \textbf{busy} and \textbf{move} on.
I ’ve \textbf{tried} to be \textbf{more} \textbf{social}.
I \textbf{say} yes to \textbf{invites} when they come ( they don't come often ), I \textbf{try} to \textbf{start} \textbf{conversations}, I \textbf{ask} \textbf{people} \textbf{questions}.
But I always \textbf{feel} \textbf{like} the \textbf{extra} \textbf{person}.
The one you ’re \textbf{polite} to, but don't really \textbf{think} about later.
There ’s this \textbf{awkward} \textbf{moment} when \textbf{everyone} else is \textbf{talking} to “ their \textbf{person} ” and I ’m just standing there, \textbf{pretending} to \textbf{check} my \textbf{phone} \textbf{like} it ’s urgent.
What really \textbf{gets} to me is not having \textbf{anyone} I can be unfiltered with.
I have “ \textbf{people} to \textbf{talk} to, ” in the shallow \textbf{sense}, but not \textbf{anyone} I can \textbf{text} at 2am and \textbf{say}, “ I \textbf{feel} \textbf{like} I ’m falling apart, ” without worrying I ’m being too \textbf{much}, too \textbf{needy}, too \textbf{heavy}.
So I \textbf{keep} \textbf{everything} on the \textbf{surface}.
I \textbf{talk} about \textbf{shows}, \textbf{work}, \textbf{random} news.
Meanwhile there ’s this whole storm \textbf{going} on \textbf{inside} that never really comes out.
Sometimes I \textbf{catch} myself rehearsing \textbf{conversations} in my \textbf{head} that will never \textbf{happen}.
Imagining what it would be \textbf{like} to have \textbf{someone} actually \textbf{see} me, \textbf{remember} little details about me, \textbf{ask} how I really am and mean it.
It \textbf{feels} pathetic to admit that, but it ’s true.
I don't even \textbf{know} what I ’m \textbf{looking} for posting this.
I \textbf{guess} I just \textbf{wanted} to \textbf{put} it somewhere \textbf{outside} my \textbf{own} \textbf{head} for once.

% matched lemmas: anyone, ask, assume, awkward, busy, call, catch, chat, check, connect, constant, conversation, coworker, day, disappear, dramatic, everyone, everything, explain, extra, family, feel, fine, full, get, glass, go, group, guess, happen, head, heavy, inside, invisible, invite, job, keep, know, like, look, loud, moment, more, move, much, needy, normal, nothing, notice, outside, own, paper, people, person, phone, polite, pretend, put, question, quiet, random, real, remember, room, say, see, seem, sense, show, social, someone, sound, start, surface, talk, text, think, try, want, watch, while, work
\end{textsample}
