\begin{textsample}{POS Dim 1 – generic\_gpt – Score 39.00 – generic\_gpt/t1054\_gpt.txt}  \label{ex:f1_pos_011}
I don't really know how to explain this without sounding dramatic, but lately it feels like my \textbf{life} is just … \textbf{background} noise.
I go through the \textbf{motions} every \textbf{day} – \textbf{work}, commute, \textbf{phone}, sleep – and there ’s no one who would really notice if I swapped any of it out for \textbf{nothing}.
I have “ \textbf{people} ” in my \textbf{life}, technically. \textbf{Coworkers} I can \textbf{joke} with, a \textbf{family} \textbf{group} \textbf{chat} that wakes up on holidays, a \textbf{couple} of old \textbf{friends} I exchange memes with every few \textbf{weeks}.
But it never goes deeper.
The second the \textbf{conversation} might turn into \textbf{something} real, my brain just shuts down and I default to “ yeah, I ’m \textbf{fine}, all good. ” I don't know if it ’s fear of being a burden or just not trusting that \textbf{anyone} actually wants to know.
The weird \textbf{part} is I crave \textbf{connection} so badly that it ’s almost physical.
I ’ll be on the bus and see two \textbf{friends} laughing together, or a \textbf{couple} half-arguing, half-teasing, and it hits me how far away that \textbf{kind} of closeness feels.
It ’s like watching a movie through thick \textbf{glass}.
I can see it, but there ’s no \textbf{way} to touch it.
I ’ve tried apps, tried making small \textbf{talk} at events, tried “ putting myself out there, ” whatever that means.
I always \textbf{end} up feeling like an extra in other \textbf{people} ’s \textbf{stories}.
I ’m there to fill a \textbf{silence}, to react, to listen, but not to actually matter. \textbf{People} forget to \textbf{text} back, \textbf{plans} get cancelled, and I ’m left staring at my own reflection in my \textbf{phone} screen, wondering what ’s so fundamentally off about me.
What messes with my \textbf{head} is that on \textbf{paper}, \textbf{nothing} is horribly wrong.
I ’m not in crisis.
I function.
I pay bills.
I \textbf{show} up.
And yet there ’s this constant, low-level \textbf{ache}, like homesickness for a \textbf{place} I ’ve never actually been – a \textbf{version} of my \textbf{life} where I ’m not always on the \textbf{outside}, watching \textbf{everyone} else belong to each other.

% matched lemmas: ache, anyone, background, chat, connection, conversation, couple, coworker, day, end, everyone, family, fine, friend, glass, group, head, joke, kind, life, motion, nothing, outside, paper, part, people, phone, place, plan, show, silence, something, story, talk, text, version, way, week, work
\end{textsample}
