\begin{textsample}{POS Dim 1 – generic\_gpt – Score 82.00 – generic\_gpt/t555\_gpt.txt}  \label{ex:f1_pos_006}
I ’ve been \textbf{feeling} this \textbf{strange} mix of \textbf{invisible} and “ too \textbf{much} ” at the \textbf{same} \textbf{time}, and I don't really \textbf{know} where else to \textbf{put} it, so I ’m \textbf{dumping} it here.
I ’m at that point in \textbf{life} where \textbf{everyone} \textbf{seems} to have \textbf{moved} into their \textbf{own} \textbf{orbit} — partners, kids, stable \textbf{friend} \textbf{groups}, \textbf{group} \textbf{chats} that actually stay active — and I ’m just \textbf{kind} of … \textbf{orbiting} \textbf{nothing}.
I \textbf{talk} to \textbf{people} every \textbf{day} at \textbf{work}, I \textbf{make} \textbf{small} \textbf{jokes}, I ’m “ \textbf{easy} to \textbf{talk} to, ” but when I come \textbf{home}, it ’s \textbf{like} I just vanish.
My \textbf{phone} \textbf{goes} \textbf{silent}.
No one is \textbf{waiting} for me to \textbf{show} up online, no one is wondering how my \textbf{day} \textbf{went}.
If I didn't \textbf{message} \textbf{first}, I don't \textbf{think} I ’d hear from \textbf{anyone} for \textbf{weeks}.
What \textbf{messes} with my \textbf{head} is how performative \textbf{everything} \textbf{feels}.
I ’ve become really good at \textbf{playing} the role of the “ chill, \textbf{okay} \textbf{person} ” because it ’s \textbf{easier} than \textbf{trying} to \textbf{explain} that I ’m lonely in a \textbf{way} that doesn't \textbf{make} \textbf{sense} from the \textbf{outside}. \textbf{People} \textbf{see} that I have \textbf{coworkers}, \textbf{acquaintances}, a \textbf{family} that ’s technically there, and they \textbf{assume} that adds up to “ not alone. ” But \textbf{none} of those connections \textbf{feel} \textbf{like} \textbf{places} I can land.
It ’s all surface-level, \textbf{like} I ’m permanently stuck in the small-talk stage of every relationship.
I \textbf{notice} I ’ve \textbf{started} editing myself down when I do \textbf{talk} to \textbf{people}.
I don't \textbf{say} the \textbf{weird} \textbf{things} I ’m actually \textbf{thinking}, I don't share \textbf{stuff} that matters to me unless I ’m almost \textbf{sure} it ’ll be received well.
I \textbf{guess} I ’m \textbf{scared} that if I \textbf{show} the \textbf{full} \textbf{version} of myself, it ’ll just confirm this \textbf{feeling} that I ’m fundamentally not \textbf{someone} \textbf{people} choose.
So I \textbf{end} up being this watered-down \textbf{version} of myself that even I don't particularly \textbf{like}, and then I \textbf{feel} even \textbf{more} disconnected. \textbf{Nights} are the \textbf{worst}.
That ’s when it \textbf{hits} me that there ’s no one I can \textbf{text} \textbf{something} mundane to, \textbf{like} “ I \textbf{saw} this and \textbf{thought} of you, ” because there isn't really a “ you ” in my \textbf{life} that fits that.
I \textbf{scroll}, I lurk, I \textbf{watch} \textbf{other} \textbf{people} ’s \textbf{conversations} \textbf{happen} in \textbf{real} \textbf{time}, and it ’s \textbf{like} pressing my face against a \textbf{window} from the \textbf{outside}.
I don't really \textbf{know} what I ’m \textbf{looking} for by writing this.
I just \textbf{wanted} to \textbf{put} into \textbf{words} that I \textbf{exist}, that I ’m here, and that it \textbf{feels} \textbf{like} no one in my \textbf{real} \textbf{life} has \textbf{noticed} in a very long \textbf{time}.

% matched lemmas: acquaintance, anyone, assume, bad, chat, conversation, coworker, day, dump, easy, end, everyone, everything, exist, explain, family, feel, feeling, first, friend, full, go, group, guess, happen, head, hit, home, invisible, joke, kind, know, life, like, look, make, mess, message, more, move, much, night, none, nothing, notice, okay, orbit, other, outside, own, people, person, phone, place, play, put, real, same, say, scare, scroll, see, seem, sense, show, silent, small, someone, something, start, strange, stuff, sure, talk, text, thing, think, time, try, version, wait, want, watch, way, week, weird, window, word, work
\end{textsample}
