\begin{textsample}{POS Dim 1 – generic\_gpt – Score 84.00 – generic\_gpt/t2659\_gpt.txt}  \label{ex:f1_pos_003}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but I \textbf{feel} \textbf{like} I ’m slowly \textbf{disappearing} from \textbf{everyone} ’s \textbf{life} \textbf{while} still being physically present.
On \textbf{paper} I ’m not “ alone. ” I have a \textbf{job}, \textbf{coworkers} who are \textbf{polite}, a \textbf{couple} of \textbf{old} \textbf{friends} I \textbf{text} every now and then, \textbf{family} members who \textbf{send} the occasional “ how are you ” \textbf{message}.
But \textbf{none} of it \textbf{feels} \textbf{like} it actually \textbf{touches} me.
It ’s \textbf{like} I ’m behind \textbf{glass}, \textbf{watching} my \textbf{own} \textbf{life} from the \textbf{outside}.
I \textbf{go} through the \textbf{motions} : wake up, commute, \textbf{work}, \textbf{scroll} on my \textbf{phone}, \textbf{pretend} to \textbf{laugh} at \textbf{things}, come \textbf{home}, eat \textbf{something} \textbf{random}, and then just \textbf{sit} there.
I \textbf{keep} the TV or YouTube on just for \textbf{background} \textbf{noise} so the \textbf{silence} doesn't \textbf{feel} so \textbf{heavy}.
I \textbf{keep} \textbf{checking} my \textbf{phone} hoping \textbf{someone} will \textbf{message} me \textbf{first}, and \textbf{most} of the \textbf{time} it ’s just \textbf{notifications} from apps I don't care about.
When I do \textbf{talk} to \textbf{people}, it \textbf{feels} \textbf{like} I ’m \textbf{playing} a \textbf{character} who ’s \textbf{more} socially acceptable than the \textbf{real} me.
I \textbf{make} \textbf{small} \textbf{talk}, I \textbf{say} “ I ’m \textbf{fine}, ” I \textbf{ask} \textbf{questions} back so they won't \textbf{notice} I ’m not actually sharing \textbf{anything}.
I can't \textbf{remember} the last \textbf{time} I was fully \textbf{honest} with \textbf{someone} about how lonely I \textbf{feel} without worrying they ’d \textbf{see} me as \textbf{needy} or pathetic.
What really \textbf{messes} with my \textbf{head} is that I \textbf{used} to have \textbf{real} connections.
In school and a bit in college, there were \textbf{people} who actually \textbf{knew} me.
Over \textbf{time} \textbf{everyone} drifted away, \textbf{got} partners, \textbf{moved}, \textbf{got} \textbf{busy}.
I \textbf{know} that ’s \textbf{normal}, but it \textbf{feels} \textbf{like} I \textbf{got} left at the train station \textbf{while} \textbf{everyone} else ’s \textbf{life} took off.
I ’m stuck \textbf{replaying} \textbf{old} memories because I don't have many new ones that involve actual closeness.
I ’ve \textbf{tried} to “ \textbf{fix} ” this the \textbf{way} \textbf{people} suggest—joining \textbf{groups}, \textbf{trying} hobbies, being \textbf{more} “ open”—but I always \textbf{end} up \textbf{feeling} \textbf{like} an \textbf{extra} in \textbf{everyone} else ’s \textbf{story}. \textbf{People} are friendly enough, but it doesn't \textbf{go} deeper.
I leave, \textbf{go} \textbf{home}, and the emptiness \textbf{hits} even harder, \textbf{like} proof that there ’s \textbf{something} about me that just doesn't stick with \textbf{anyone}.
I don't even \textbf{know} what I ’m \textbf{asking} for.
I just \textbf{needed} to \textbf{put} this somewhere, because \textbf{keeping} it in my \textbf{head} all the \textbf{time} is \textbf{starting} to \textbf{feel} \textbf{like} it ’s swallowing me.

% matched lemmas: anyone, anything, ask, background, busy, character, check, couple, coworker, disappear, dramatic, end, everyone, explain, extra, family, feel, fine, first, fix, friend, get, glass, go, group, head, heavy, hit, home, honest, job, keep, know, laugh, life, like, make, mess, message, more, most, motion, move, need, needy, noise, none, normal, notice, notification, old, outside, own, paper, people, phone, play, polite, pretend, put, question, random, real, remember, replay, say, scroll, see, send, silence, sit, small, someone, something, sound, start, story, talk, text, thing, time, touch, try, use, watch, way, while, work
\end{textsample}
