\begin{textsample}{POS Dim 1 – human – Score 20.00 – human/t1856\_human.txt}  \label{ex:f1_pos_040}
I ’ve been sitting with this \textbf{feeling} for a \textbf{while}, so I figured I ’d put it somewhere \textbf{people} might understand.
Especially because I feel like this \textbf{feeling} is only getting worse.
I often feel much older in my soul than I actually am, and it makes it hard to connect with \textbf{people} my age.
My passions lean toward \textbf{things} like aviation, history, and maritime topics, every \textbf{couple} \textbf{weeks} or so, there 's \textbf{something} specific I hyperfixate on when it comes to learning about it and it 's all I focus on. my current hyperfixation is Sutra Baths.
Very niche, I understand.
These are very specific worlds that most of my peers just aren't into.
I get that these interests aren't exactly mainstream, and I don't expect \textbf{everyone} around me to share them.
But sometimes that disconnect spills into simpler \textbf{things} too.
I ’ll want to spend an entire \textbf{day} just walking along the ocean, listening to the waves, watching the horizon, thinking about ships, \textbf{time}, and \textbf{everything} in between.
I crave slow, reflective \textbf{moments} like that, and it often feels like I ’m the only one in my \textbf{circle} who does.
I ’ve tried to build \textbf{connections} online with \textbf{people} who share these interests, but those relationships rarely feel mutual.
I ’m usually the one reaching out, initiating, and keeping \textbf{things} going, and eventually I just \textbf{end} up feeling more alone than before.
I always tell \textbf{people} I do much better in \textbf{person}.
I hate falling into the pattern of connecting briefly, \textbf{talking} for a few \textbf{weeks} and then the falling out.
I just want to feel understood, or at least less out of \textbf{place} in my own age \textbf{group}.
I ’m trying to accept that I ’m wired differently, but some \textbf{days} the \textbf{loneliness} still hits hard.

% matched lemmas: circle, connection, couple, day, end, everyone, everything, feeling, group, loneliness, moment, people, person, place, something, talk, thing, time, week, while
\end{textsample}
