\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 52.00 – summary\_guided\_gpt/t552\_gpt.txt}  \label{ex:f1_pos_027}
I ’m 29, originally from Iran, and I ’ve been in the US for about four years now for my master ’s.
I just \textbf{moved} to Texas by myself because of immigration \textbf{stuff}, and it ’s really \textbf{hitting} me how \textbf{much} “ being alone ” has become the default setting of my \textbf{life}.
It ’s not \textbf{like} this \textbf{started} with \textbf{moving} here.
Even back in college, at \textbf{work}, traveling, doing hobbies … I ’ve always been the one who has to \textbf{initiate} \textbf{everything}.
If I don't \textbf{text} \textbf{first}, if I don't suggest \textbf{plans}, \textbf{nothing} \textbf{happens}.
I ’ve \textbf{gotten} \textbf{used} to doing \textbf{most} \textbf{things} alone : \textbf{going} to museums, \textbf{watching} movies in the theater, \textbf{trying} out new \textbf{places}.
I ’m genuinely comfortable with that \textbf{part} ; I don't \textbf{feel} ashamed \textbf{sitting} alone at a café or \textbf{going} to a movie by myself.
But there ’s this painful side to it.
When I ’m out, I \textbf{see} \textbf{groups} of \textbf{friends} \textbf{laughing}, \textbf{couples} sharing \textbf{inside} \textbf{jokes}, \textbf{people} taking \textbf{photos} together.
It ’s \textbf{like} there ’s this \textbf{invisible} \textbf{wall} between my world and theirs.
I can do the \textbf{same} activities, but the “ together ” \textbf{part} \textbf{feels} \textbf{like} \textbf{something} I just don't have access to.
It ’s not even that I ’m desperate to be surrounded by \textbf{people} all the \textbf{time} ; it ’s \textbf{more} this \textbf{constant} reminder that I ’m on the \textbf{outside} of \textbf{something} \textbf{everyone} else \textbf{seems} to have.
Remote \textbf{work} has \textbf{made} all of this \textbf{worse}.
At least with in-person \textbf{work} or school there was some built-in \textbf{contact}, even if it was shallow.
Now my \textbf{days} are mostly just me, my laptop, my apartment.
On the rare occasions I do spend \textbf{time} with \textbf{people}, I almost \textbf{feel} disoriented, \textbf{like} I ’ve forgotten how to be around \textbf{others}.
And then, inevitably, I \textbf{go} back to being alone again, \textbf{like} that ’s the “ \textbf{real} ” state and \textbf{everything} else was a temporary glitch.
I ’ve basically paused dating.
I value my alone \textbf{time} a lot, and the \textbf{constant} \textbf{messaging}, check-ins, and \textbf{small} obligations of a relationship \textbf{feel} draining compared to the few shared \textbf{moments} they bring.
It doesn't \textbf{feel} \textbf{like} a good trade-off.
So I \textbf{end} up choosing solitude, even though that \textbf{same} solitude hurts in its \textbf{own} \textbf{way}.

% matched lemmas: bad, constant, contact, couple, day, end, everyone, everything, feel, first, friend, get, go, group, happen, hit, initiate, inside, invisible, joke, laugh, life, like, make, message, moment, more, most, move, much, nothing, other, outside, own, part, people, photo, place, plan, real, same, see, seem, sit, small, something, start, stuff, text, thing, time, try, use, wall, watch, way, work
\end{textsample}
