\begin{textsample}{POS Dim 1 – human – Score 21.00 – human/t1709\_human.txt}  \label{ex:f1_pos_038}
Lately I ’ve been dealing with a lot, but honestly the worst \textbf{part} isn't even the \textbf{outside} \textbf{stuff}.
It ’s the \textbf{loneliness}.
That constant \textbf{feeling} of being on the \textbf{outside} of \textbf{everything}.
I didn't go to college.
I just started \textbf{working} shitty customer service, \textbf{nothing} special.
I always thought I ’d be more by now.
I put so much pressure on myself to impress \textbf{people}, be \textbf{someone}, prove I ’m smart.
Now having a normal low-level \textbf{job} makes me feel like I already failed at \textbf{life}.
I grew up mostly with my grandma, and I think that messed with me more than I realized.
I don't really know how to build close \textbf{connections}.
I don't have a solid \textbf{friend} \textbf{group}.
I overthink \textbf{everything} I say.
I don't even know how \textbf{people} see me.
Some \textbf{days} I feel okay about myself, other \textbf{days} I feel so pathetic and ugly.
Adhd didn't help either.
I wasn't diagnosed when I was younger so school was a total mess.
Couldn't focus for my \textbf{life}, procrastinated \textbf{everything}, avoided \textbf{friends}, stayed \textbf{home} because of insecurities about how I look.
I never built any good habits, so I know I ’d probably struggle even if I went to uni now.
My brain just never learned how to handle long projects, deadlines, sitting through boring lectures, and nobody ever taught me.
Even now going out, gym ( started recently ), social \textbf{stuff} drains me fast.
I feel awkward and anxious most of the \textbf{time}, kinda autistic in how I overthink \textbf{everything}.
I ’ve been trying to change though.
Lost a lot of weight, started \textbf{working} out, taking care of my skin ( meds for acne ), small upgrades here and there.
On the \textbf{outside} it kinda looks like progress.
But realizing I ’m 22 and I should be \textbf{way} ahead drains me of any positive thoughts.
I don't need a perfect \textbf{life}.
I just want \textbf{connection}. \textbf{Someone} to \textbf{talk} to.
Maybe date.
Maybe just not feel like I ’m doing \textbf{everything} alone.
I ’m scared of being a burden.
I ’m afraid \textbf{people} see me as unambitious or boring even though I know I ’m not boring or unfunny.
And I hate that my own brain makes \textbf{everything} harder than it probably is.
So yeah, I guess I ’m just writing this here because I don't really have \textbf{anyone} to say it to.
Any advice would be super appreciated 🖤

% matched lemmas: anyone, connection, day, everything, feeling, friend, group, home, job, life, loneliness, nothing, outside, part, people, someone, stuff, talk, time, way, work
\end{textsample}
