\begin{textsample}{POS Dim 1 – generic\_gpt – Score 79.00 – generic\_gpt/t1406\_gpt.txt}  \label{ex:f1_pos_018}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but I \textbf{feel} \textbf{like} I ’m slowly \textbf{disappearing} from my \textbf{own} \textbf{life}.
On \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, a \textbf{place} to live, no huge crisis \textbf{going} on.
I \textbf{talk} to \textbf{people} every \textbf{day} : \textbf{coworkers}, the barista, neighbors in the hallway.
But it all \textbf{feels} \textbf{like} \textbf{background} \textbf{noise}. \textbf{Nothing} sticks.
No one actually \textbf{knows} me, and I ’m \textbf{starting} to \textbf{feel} \textbf{like} maybe there ’s \textbf{nothing} worth \textbf{knowing}.
I \textbf{scroll} through my \textbf{phone} and \textbf{realize} I don't have \textbf{anyone} I can \textbf{text} without overthinking it.
Even with the few \textbf{people} I might \textbf{reach} out to, I rehearse what to \textbf{say}, \textbf{delete} it, rewrite it, then \textbf{end} up \textbf{sending} \textbf{nothing} because I \textbf{convince} myself I ’m being \textbf{annoying}.
I \textbf{watch} the “ typing … ” bubble when they do \textbf{respond} and \textbf{feel} guilty for taking up their \textbf{time}.
It ’s exhausting. \textbf{Weekends} are the \textbf{worst}.
I wake up, \textbf{check} my \textbf{notifications}, \textbf{see} \textbf{nothing}, and then just \textbf{kind} of … drift.
Sometimes I ’ll \textbf{pretend} I ’m \textbf{busy} if \textbf{anyone} \textbf{asks} what I did, but honestly it ’s usually just me \textbf{sitting} in my \textbf{room}, \textbf{scrolling}, listening to the \textbf{same} songs, staring at the \textbf{same} \textbf{walls}.
I ’ll hear \textbf{people} \textbf{outside} \textbf{laughing} or \textbf{heading} somewhere together and it \textbf{feels} \textbf{like} there ’s this \textbf{invisible} \textbf{glass} between me and the rest of the world.
I ’ve \textbf{tried} to “ \textbf{put} myself out there ” \textbf{like} \textbf{everyone} suggests. \textbf{Joined} a \textbf{couple} of \textbf{group} \textbf{things}, \textbf{tried} \textbf{talking} \textbf{more} at \textbf{work}, even \textbf{forced} myself to \textbf{go} to a \textbf{social} event alone.
I \textbf{end} up standing there, \textbf{feeling} \textbf{like} an intruder in \textbf{other} \textbf{people} ’s \textbf{conversations}, \textbf{nodding} and \textbf{smiling} until I can leave without it being too obvious. \textbf{People} are \textbf{polite}, but it never \textbf{goes} beyond that.
I \textbf{walk} \textbf{home} \textbf{feeling} \textbf{more} alone than before.
The \textbf{thing} that \textbf{scares} me is how \textbf{normal} this is \textbf{starting} to \textbf{feel}.
I ’m \textbf{getting} \textbf{used} to not \textbf{expecting} \textbf{messages}, to eating alone, to having entire \textbf{days} where the only voice I hear is my \textbf{own}.
And when I do finally \textbf{talk} to \textbf{someone}, I \textbf{feel} rusty, \textbf{like} I ’ve forgotten how to be a \textbf{person} around \textbf{other} \textbf{people}.
I don't \textbf{know} what I ’m hoping for by posting this.
I \textbf{guess} I just \textbf{wanted} to \textbf{say} it somewhere, because \textbf{keeping} it all in my \textbf{head} is \textbf{starting} to \textbf{feel} \textbf{heavier} than the loneliness itself.

% matched lemmas: annoy, anyone, ask, background, bad, busy, check, conversation, convince, couple, coworker, day, delete, disappear, dramatic, end, everyone, expect, explain, feel, fine, force, get, glass, go, group, guess, head, heavy, home, invisible, job, join, keep, kind, know, laugh, life, like, message, more, nod, noise, normal, nothing, notification, other, outside, own, paper, people, person, phone, place, polite, pretend, put, reach, realize, respond, room, same, say, scare, scroll, see, send, sit, smile, social, someone, sound, start, talk, text, thing, time, try, use, walk, wall, want, watch, weekend, work
\end{textsample}
