\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 53.00 – summary\_guided\_gpt/t639\_gpt.txt}  \label{ex:f1_pos_026}
I haven't properly \textbf{spoken} to my best \textbf{friend} in over two months now.
The last \textbf{real} \textbf{conversation} we had \textbf{ended} in a fight.
After that, it was just a \textbf{couple} of “ happy festival ” \textbf{messages} back and forth, and then … \textbf{nothing}.
Complete \textbf{silence}.
They were always the “ \textbf{busy} ” one, the \textbf{kind} of \textbf{person} who \textbf{replied} late but eventually did.
Now it ’s different.
Sometimes they \textbf{respond} after \textbf{days}, sometimes not at all.
They don't \textbf{call}, they don't \textbf{text} \textbf{first}, and I can't \textbf{tell} if I ’m being ignored or if they just don't even \textbf{bother} \textbf{opening} WhatsApp anymore.
I \textbf{keep} wondering if they ’re just quietly done with me and don't have the courage to \textbf{say} it.
On the \textbf{outside}, I ’m acting \textbf{like} \textbf{everything} is \textbf{fine}.
I \textbf{laugh}, I \textbf{talk} to \textbf{other} \textbf{people}, I \textbf{go} through my routine \textbf{like} I ’m \textbf{okay}.
But I ’m not.
It \textbf{feels} \textbf{like} there ’s this \textbf{constant} weight in my chest.
Every \textbf{time} I \textbf{open} WhatsApp, I \textbf{end} up clicking on our \textbf{chat}.
I \textbf{start} typing \textbf{something} – “ Hey, how are you? ” or “ Can we \textbf{talk}? ” – and then I \textbf{scroll} up, reread our last \textbf{conversation}, \textbf{remember} how it \textbf{ended}, and just \textbf{delete} \textbf{everything}.
Then I \textbf{close} the app and \textbf{pretend} I never \textbf{tried}.
I don't \textbf{know} if I ’m overthinking, or if this is just what it \textbf{looks} \textbf{like} when \textbf{someone} slowly lets you \textbf{go}.
It hurts that \textbf{someone} who once \textbf{knew} almost \textbf{everything} about me can now \textbf{go} \textbf{days}, \textbf{weeks}, months without \textbf{wanting} to \textbf{talk}.
I \textbf{keep} \textbf{asking} myself if I should \textbf{reach} out one \textbf{more} \textbf{time} or just accept that maybe they don't \textbf{want} me in their \textbf{life} anymore.
I \textbf{feel} really alone in this.
I ’m surrounded by \textbf{people}, but the one \textbf{person} I \textbf{want} to \textbf{talk} to the \textbf{most} \textbf{feels} out of \textbf{reach}, \textbf{like} they ’re already \textbf{gone}, and I ’m the only one who hasn't \textbf{caught} up to that reality yet.

% matched lemmas: ask, bother, busy, call, catch, chat, close, constant, conversation, couple, day, delete, end, everything, feel, fine, first, friend, go, keep, kind, know, laugh, life, like, look, message, more, most, nothing, okay, open, other, outside, people, person, pretend, reach, real, remember, reply, respond, say, scroll, silence, someone, something, speak, start, talk, tell, text, time, try, want, week
\end{textsample}
