\begin{textsample}{POS Dim 1 – generic\_gpt – Score 81.00 – generic\_gpt/t020\_gpt.txt}  \label{ex:f1_pos_010}
I don't really \textbf{know} how to \textbf{say} this in a \textbf{way} that doesn't \textbf{sound} \textbf{dramatic}, but I \textbf{feel} \textbf{like} I ’m living my \textbf{life} behind \textbf{glass}.
On \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, I \textbf{respond} to \textbf{messages}, I \textbf{show} up when I ’m \textbf{supposed} to. \textbf{People} would probably describe me as \textbf{quiet} but “ nice. ” I \textbf{make} \textbf{small} \textbf{talk} about \textbf{work}, the \textbf{weather}, whatever \textbf{show} is popular.
I \textbf{smile}, I \textbf{nod}, I \textbf{laugh} at the \textbf{right} \textbf{times}.
Then I \textbf{go} \textbf{home} and it ’s \textbf{like} I evaporate.
No one \textbf{notices} that \textbf{part}.
What ’s \textbf{getting} to me lately is this \textbf{sense} that I ’m “ around \textbf{people} ” all the \textbf{time} but not actually *with* \textbf{anyone}.
At \textbf{work}, \textbf{everyone} has their little \textbf{groups}.
They \textbf{talk} about \textbf{weekend} trips, brunches, game \textbf{nights}.
I ’m always just \textbf{close} enough to overhear \textbf{plans}, never \textbf{close} enough to be included.
I stand there \textbf{pretending} to be \textbf{busy} on my \textbf{phone} so it doesn't \textbf{look} as \textbf{awkward} as it \textbf{feels}.
I ’ve \textbf{tried} to \textbf{put} myself out there.
I ’ve \textbf{gone} to meetups, \textbf{joined} \textbf{group} \textbf{chats}, even \textbf{forced} myself to \textbf{start} \textbf{conversations}.
It always \textbf{ends} the \textbf{same} \textbf{way} : a few surface-level \textbf{interactions} that slowly fade out, \textbf{like} I ’m forgettable \textbf{background} \textbf{noise}.
I don't \textbf{think} \textbf{people} dislike me ; it ’s \textbf{more} \textbf{like} I ’m just … not \textbf{anyone} ’s \textbf{first} choice.
Or \textbf{second}.
Or third.
The \textbf{worst} \textbf{part} is how it \textbf{messes} with my \textbf{sense} of reality.
I \textbf{start} wondering if maybe I ’m actually really \textbf{boring}, or off-putting in \textbf{ways} I can't \textbf{see}.
I \textbf{replay} every \textbf{conversation}, every \textbf{silence}, every \textbf{time} \textbf{someone} ’s eyes drift past me to \textbf{someone} \textbf{more} interesting.
It ’s exhausting to constantly \textbf{feel} \textbf{like} you ’re auditioning for a role in \textbf{other} \textbf{people} ’s \textbf{lives} and never \textbf{getting} the \textbf{part}. \textbf{Nights} are the hardest.
I come \textbf{home}, \textbf{put} my \textbf{stuff} down, and the \textbf{silence} just \textbf{hits} me.
No one \textbf{asking} how my \textbf{day} was, no one to vent to, no one to \textbf{sit} next to on the couch doing \textbf{nothing}.
I \textbf{scroll} through \textbf{social} \textbf{media} and it \textbf{feels} \textbf{like} \textbf{watching} a world I ’m not \textbf{part} of. \textbf{Everyone} \textbf{seems} to have “ their \textbf{people}. ” I have … me.
I don't even \textbf{know} what I ’m hoping for by posting this.
Maybe I just \textbf{wanted} to \textbf{put} it somewhere \textbf{other} than my \textbf{own} \textbf{head} for once.

% matched lemmas: anyone, ask, awkward, background, bad, boring, busy, chat, close, conversation, day, dramatic, end, everyone, feel, fine, first, force, get, glass, go, group, head, hit, home, interaction, job, join, know, laugh, life, like, look, make, medium, mess, message, more, night, nod, noise, nothing, notice, other, own, paper, part, people, phone, plan, pretend, put, quiet, replay, respond, right, same, say, scroll, second, see, seem, sense, show, silence, sit, small, smile, social, someone, sound, start, stuff, suppose, talk, think, time, try, want, watch, way, weather, weekend, work
\end{textsample}
