\begin{textsample}{POS Dim 1 – human – Score 46.00 – human/t320\_human.txt}  \label{ex:f1_pos_034}
Just \textbf{turned} 23 Last year on December.
I don't really \textbf{know} why I ’m writing this.
Maybe because tonight it \textbf{hit} me again.
I ’m \textbf{sitting} in my \textbf{room} again, \textbf{lights} off, \textbf{door} \textbf{closed}, just me and the \textbf{silence}.
I graduated three years ago, but I don't have a \textbf{job} yet.
I ’m living at \textbf{home}, spending my father ’s money, doing \textbf{nothing} useful,and every \textbf{day} I hear it the reminders, the criticism, the frustration dripping from every \textbf{word} my parents throw at me.
I hear them complain about me \textbf{sitting} here, doing \textbf{nothing}, wasting my \textbf{life}.
Every \textbf{word} \textbf{feels} \textbf{like} a weight pressing down on my chest.
I eat in my \textbf{room}.
I \textbf{scroll} my \textbf{phone} to \textbf{feel} \textbf{busy}.
I \textbf{watch} YouTube and doing doomscrolling all the \textbf{day} abd \textbf{night} to just to hear human voices, to trick myself into \textbf{thinking} I ’m not entirely \textbf{invisible}.
I \textbf{go} for \textbf{walks} when no one ’s around very rarely.
I \textbf{keep} \textbf{quiet}.
I \textbf{disappear} into corners, into the shadows, because every glance \textbf{feels} \textbf{like} judgment, every \textbf{moment} a reminder that I am not enough.
Some \textbf{nights}, I cry quietly under my blanket.
Not because I ’m weak, not because I \textbf{want} pity but because it physically hurts to \textbf{exist} in a \textbf{space} where i \textbf{feel} unwanted, unneeded, unloved and unseen.
I \textbf{try} to \textbf{pretend} I ’m \textbf{okay}, but \textbf{inside}, it screams. \textbf{Inside}, I \textbf{ache} to be anywhere else, \textbf{anyone} else ’s priority, even for one hour. \textbf{People} \textbf{say} learn to enjoy your \textbf{own} company.
But it ’s not that simple.
Sometimes it ’s just surviving.
Surviving the \textbf{silence}.
Surviving the \textbf{words} that \textbf{make} me \textbf{feel} \textbf{small}.
Surviving the \textbf{way} the world, even at \textbf{home}, \textbf{makes} me \textbf{invisible}.
I just survive in the \textbf{quiet}, counting the hours until the house \textbf{sleeps}, until I can \textbf{close} the \textbf{door} and cry until my chest hurts, until the world can't \textbf{see} the pieces of me I can't hold together.
I dont \textbf{need} advice.
I don't \textbf{need} cheer up or you ’ll be fine.I just \textbf{want} to \textbf{know} if \textbf{anyone} else \textbf{feels} this the weight of loneliness \textbf{while} living at \textbf{home}, the sting of judgment for simply \textbf{existing}, the \textbf{quiet}, endless \textbf{ache} of \textbf{feeling} \textbf{like} you don't matter.
If you relate, even one me too would mean the world tonight for me.

% matched lemmas: ache, anyone, busy, close, day, disappear, door, exist, feel, go, hit, home, inside, invisible, job, keep, know, life, light, like, make, moment, need, night, nothing, okay, own, people, phone, pretend, quiet, room, say, scroll, see, silence, sit, sleep, small, space, think, try, turn, walk, want, watch, way, while, word
\end{textsample}
