\begin{textsample}{POS Dim 1 – human – Score 43.00 – human/t967\_human.txt}  \label{ex:f1_pos_037}
I have this fear that one of the only \textbf{friends} I \textbf{go} out with doesn't \textbf{like} to \textbf{hang} out with me anymore but is too \textbf{polite} to \textbf{say}.
I always \textbf{ask} to \textbf{hang} out, it ’s almost never the \textbf{other} \textbf{way} around.
We only ever \textbf{talk} when we \textbf{see} each \textbf{other} in \textbf{real} \textbf{life}, or when I \textbf{text} \textbf{something}.
So I ’m \textbf{trying} to \textbf{go} out on my \textbf{own} tomorrow.
I \textbf{feel} pretty sad but I ’m \textbf{trying} to \textbf{look} at the positive side that at least I can do that.
But having so \textbf{much} \textbf{silence}. \textbf{Looking} at my \textbf{phone} constantly with no one really who \textbf{wants} to \textbf{ask} me about my \textbf{day} or \textbf{anything} as \textbf{much} as I \textbf{ask} about theirs.
I ’m \textbf{trying} to ignore \textbf{getting} depressed, but being this lonely \textbf{makes} me tired.
Drained.
When I \textbf{go} to \textbf{sleep} I \textbf{try} to be as vivid as possible to imagine I ’m with \textbf{someone}.
I have these two \textbf{people} on YouTube that I “ \textbf{watch} ” movies with because I don't have \textbf{anyone} in \textbf{real} \textbf{life} to do that with.
At \textbf{work}, \textbf{everyone} is \textbf{going} on vacation.
To \textbf{see} their \textbf{friends} and \textbf{families}, with their husbands or wives and kids. \textbf{Everyone} has \textbf{someone} to \textbf{go} \textbf{home} to.
I ’m always the last to leave, I \textbf{walk} alone and I \textbf{wait} alone for the bus.
My dream is to just have \textbf{someone} \textbf{see} me.
And \textbf{want} to \textbf{know} me and \textbf{talk} to me just because they \textbf{feel} \textbf{like} it.
I \textbf{look} in the mirror and wonder if maybe I ’m too fat, or too ugly, or just too \textbf{annoying} with the \textbf{things} that I \textbf{like}.
There ’s a boy that I \textbf{think} about always who never falls short of finding \textbf{someone} else to be in love with.
It \textbf{makes} my heart \textbf{ache}.
I \textbf{keep} \textbf{trying} to \textbf{keep} myself in good spirits \textbf{thinking} that it ’s for a reason.
But even in my thoughts I ’m lonely and have \textbf{nothing} to \textbf{talk} to myself about.
I fill my \textbf{time} consuming information and \textbf{watching} \textbf{shows} hoping that I ’ll \textbf{get} to \textbf{talk} to \textbf{someone} about it for the \textbf{day}.

% matched lemmas: ache, annoy, anyone, anything, ask, day, everyone, family, feel, friend, get, go, hang, home, keep, know, life, like, look, make, much, nothing, other, own, people, phone, polite, real, say, see, show, silence, sleep, someone, something, talk, text, thing, think, time, try, wait, walk, want, watch, way, work
\end{textsample}
