\begin{textsample}{POS Dim 1 – generic\_gpt – Score 80.00 – generic\_gpt/t2402\_gpt.txt}  \label{ex:f1_pos_012}
I ’ve been \textbf{feeling} \textbf{like} a ghost who still has to \textbf{show} up to \textbf{work} every \textbf{day}.
On \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, a \textbf{place} to live, \textbf{people} I interact with.
But \textbf{everything} \textbf{feels} \textbf{like} \textbf{background} \textbf{noise}.
I \textbf{talk} to \textbf{coworkers}, I \textbf{say} “ good \textbf{weekend}? ” on Mondays, I \textbf{laugh} at the \textbf{right} \textbf{times}.
Then I \textbf{go} \textbf{home} and it ’s \textbf{like} the \textbf{sound} just cuts out.
I ’m alone with this \textbf{heavy} \textbf{quiet} that almost \textbf{feels} physical.
What ’s \textbf{messing} with me is that I ’m not completely \textbf{isolated} in the obvious \textbf{ways}.
I have a few \textbf{people} I could \textbf{text}.
Sometimes I do.
The \textbf{conversations} are shallow though—memes, \textbf{random} comments, logistics.
I can't \textbf{remember} the last \textbf{time} I \textbf{felt} \textbf{like} I could \textbf{say}, “ I ’m really not \textbf{okay}, ” and have \textbf{anyone} actually stay in that \textbf{space} with me instead of \textbf{changing} the subject or throwing a quick “ you ’ll be \textbf{fine} ” at it.
I ’ve \textbf{tried} to “ \textbf{fix} ” it the \textbf{usual} ways—joining clubs, \textbf{going} to events, \textbf{trying} to be \textbf{more} \textbf{social}.
I can \textbf{show} up and \textbf{talk} to \textbf{people}, but it \textbf{feels} \textbf{like} I ’m always on the \textbf{outside} of \textbf{something} \textbf{everyone} else \textbf{seems} to naturally understand.
They slip into \textbf{groups} and \textbf{inside} \textbf{jokes} and \textbf{easy} familiarity, and I ’m standing \textbf{right} there but somehow not actually in it. \textbf{Like} I ’m \textbf{watching} them through a \textbf{window}.
Sometimes I \textbf{start} to wonder if there ’s just \textbf{something} fundamentally off about me that \textbf{other} \textbf{people} can \textbf{sense}.
Not in a \textbf{dramatic} “ I ’m the \textbf{worst} \textbf{person} ever ” \textbf{way}, \textbf{more} \textbf{like} a subtle wrong frequency—close enough to pass, but not \textbf{close} enough for \textbf{anyone} to really lock onto.
I \textbf{get} \textbf{home} after \textbf{social} \textbf{stuff} and \textbf{replay} every \textbf{interaction}, picking apart the \textbf{weird} pauses and \textbf{awkward} \textbf{jokes}, and it just confirms the \textbf{feeling} that I don't quite fit anywhere.
What \textbf{scares} me is how \textbf{normal} this has \textbf{started} to \textbf{feel}.
The routines of it : \textbf{work}, \textbf{home}, screen, \textbf{bed}.
The \textbf{constant} low-level \textbf{ache} of \textbf{wanting} \textbf{someone} to really \textbf{know} me and not having the faintest idea how to \textbf{make} that \textbf{happen} without coming across as \textbf{needy} or \textbf{strange}.
It ’s \textbf{like} I ’m drifting further out, and \textbf{everyone} else is on shore, \textbf{busy} with their \textbf{own} \textbf{lives}, not even \textbf{noticing} there was \textbf{someone} standing near them in the \textbf{first} \textbf{place}.

% matched lemmas: ache, anyone, awkward, background, bad, bed, busy, change, close, constant, conversation, coworker, day, dramatic, easy, everyone, everything, feel, feeling, fine, first, fix, get, go, group, happen, heavy, home, inside, interaction, isolate, job, joke, know, laugh, life, like, make, mess, more, needy, noise, normal, notice, okay, other, outside, own, paper, people, person, place, quiet, random, remember, replay, right, say, scare, seem, sense, show, social, someone, something, sound, space, start, strange, stuff, talk, text, time, try, usual, want, watch, way, weekend, weird, window, work
\end{textsample}
