\begin{textsample}{POS Dim 1 – human – Score 50.00 – human/t1709\_human.txt}  \label{ex:f1_pos_032}
Lately I ’ve been dealing with a lot, but honestly the \textbf{worst} \textbf{part} isn't even the \textbf{outside} \textbf{stuff}.
It ’s the loneliness.
That \textbf{constant} \textbf{feeling} of being on the \textbf{outside} of \textbf{everything}.
I didn't \textbf{go} to college.
I just \textbf{started} \textbf{working} shitty customer service, \textbf{nothing} special.
I always \textbf{thought} I ’d be \textbf{more} by now.
I \textbf{put} so \textbf{much} pressure on myself to impress \textbf{people}, be \textbf{someone}, prove I ’m smart.
Now having a \textbf{normal} low-level \textbf{job} \textbf{makes} me \textbf{feel} \textbf{like} I already failed at \textbf{life}.
I grew up mostly with my grandma, and I \textbf{think} that \textbf{messed} with me \textbf{more} than I \textbf{realized}.
I don't really \textbf{know} how to build \textbf{close} connections.
I don't have a solid \textbf{friend} \textbf{group}.
I overthink \textbf{everything} I \textbf{say}.
I don't even \textbf{know} how \textbf{people} \textbf{see} me.
Some \textbf{days} I \textbf{feel} \textbf{okay} about myself, \textbf{other} \textbf{days} I \textbf{feel} so pathetic and ugly.
Adhd didn't help either.
I wasn't diagnosed when I was younger so school was a total \textbf{mess}.
Couldn't focus for my \textbf{life}, procrastinated \textbf{everything}, avoided \textbf{friends}, stayed \textbf{home} because of insecurities about how I \textbf{look}.
I never built any good habits, so I \textbf{know} I ’d probably struggle even if I \textbf{went} to uni now.
My brain just never learned how to handle long projects, deadlines, \textbf{sitting} through \textbf{boring} lectures, and nobody ever taught me.
Even now \textbf{going} out, gym ( \textbf{started} recently ), \textbf{social} \textbf{stuff} drains me fast.
I \textbf{feel} \textbf{awkward} and anxious \textbf{most} of the \textbf{time}, kinda autistic in how I overthink \textbf{everything}.
I ’ve been \textbf{trying} to \textbf{change} though.
Lost a lot of weight, \textbf{started} \textbf{working} out, taking care of my skin ( meds for acne ), \textbf{small} upgrades here and there.
On the \textbf{outside} it kinda \textbf{looks} \textbf{like} progress.
But \textbf{realizing} I ’m 22 and I should be \textbf{way} ahead drains me of any positive thoughts.
I don't \textbf{need} a perfect \textbf{life}.
I just \textbf{want} connection. \textbf{Someone} to \textbf{talk} to.
Maybe date.
Maybe just not \textbf{feel} \textbf{like} I ’m doing \textbf{everything} alone.
I ’m \textbf{scared} of being a burden.
I ’m afraid \textbf{people} \textbf{see} me as unambitious or \textbf{boring} even though I \textbf{know} I ’m not \textbf{boring} or unfunny.
And I hate that my \textbf{own} brain \textbf{makes} \textbf{everything} harder than it probably is.
So yeah, I \textbf{guess} I ’m just writing this here because I don't really have \textbf{anyone} to \textbf{say} it to.
Any advice would be super appreciated {\EmojiFont 🖤}

% matched lemmas: anyone, awkward, bad, boring, change, close, constant, day, everything, feel, feeling, friend, go, group, guess, home, job, know, life, like, look, make, mess, more, most, much, need, normal, nothing, okay, other, outside, own, part, people, put, realize, say, scare, see, sit, small, social, someone, start, stuff, talk, think, time, try, want, way, work
\end{textsample}
