\begin{textsample}{POS Dim 1 – generic\_gpt – Score 80.00 – generic\_gpt/t2079\_gpt.txt}  \label{ex:f1_pos_014}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but I \textbf{feel} \textbf{like} I ’m living next to my \textbf{own} \textbf{life} instead of in it.
On \textbf{paper}, I ’m “ \textbf{fine}. ” I have a \textbf{job}, I pay my bills, I \textbf{talk} to \textbf{people} every \textbf{day}.
I \textbf{answer} emails, I \textbf{join} meetings, I \textbf{nod} along in \textbf{conversations} about \textbf{weekend} \textbf{plans} that never include me.
I ’m surrounded by \textbf{noise} and still \textbf{feel} \textbf{like} I ’m in a soundproof box. \textbf{People} \textbf{see} me, but it doesn't \textbf{feel} \textbf{like} \textbf{anyone} actually \textbf{sees} me.
The \textbf{weird} \textbf{thing} is, I \textbf{used} to have \textbf{friends}.
Not a huge \textbf{group}, but enough that I \textbf{felt} \textbf{like} I \textbf{belonged} somewhere.
Over \textbf{time}, \textbf{everyone} just … drifted. \textbf{People} \textbf{moved}, \textbf{got} partners, had kids, found new \textbf{friend} \textbf{groups}.
I didn't do \textbf{anything} \textbf{dramatic} to push them away ; I just became the \textbf{person} you “ mean to \textbf{catch} up with soon ” and never actually do.
I \textbf{scroll} through \textbf{social} \textbf{media} and \textbf{see} them all together, and it ’s \textbf{like} \textbf{watching} an alternate timeline where I didn't \textbf{get} left behind.
I \textbf{try} to \textbf{reach} out sometimes.
I ’ll type a \textbf{message}, stare at it, rewrite it, then either \textbf{send} it and \textbf{get} a \textbf{polite} but distant \textbf{reply}, or \textbf{delete} it and \textbf{tell} myself it was \textbf{stupid} anyway.
I ’m constantly torn between \textbf{wanting} connection and being terrified of being \textbf{annoying} or unwanted.
I overanalyze every \textbf{silence}, every “ \textbf{seen} ” without a response, every “ we should \textbf{hang} out sometime ” that never \textbf{turns} into a \textbf{plan}.
I ’ve also \textbf{noticed} I ’ve \textbf{started} \textbf{lying} by omission.
When \textbf{people} \textbf{ask} what I did over the \textbf{weekend}, I ’ll \textbf{say}, “ Just relaxed, ” instead of “ I \textbf{sat} alone in my \textbf{room} and \textbf{tried} not to \textbf{think} about how no one texted me. ” It \textbf{feels} shameful to admit how empty my \textbf{life} is \textbf{outside} of \textbf{work} and \textbf{errands}. \textbf{Like} there ’s \textbf{something} fundamentally wrong with me that \textbf{everyone} else can \textbf{sense}. \textbf{Nights} are the \textbf{worst}.
That ’s when \textbf{everything} \textbf{gets} \textbf{loud} in my \textbf{head}.
I \textbf{replay} \textbf{old} \textbf{conversations}, \textbf{think} about \textbf{people} I haven't \textbf{spoken} to in years, wonder if they ever \textbf{think} about me.
I \textbf{keep} my \textbf{phone} nearby even though it almost never \textbf{lights} up with \textbf{anything} personal.
I still \textbf{check} it too often, \textbf{like} I ’m \textbf{waiting} for \textbf{something} that ’s not coming.
I don't even \textbf{know} what I ’m \textbf{looking} for posting this.
I just \textbf{needed} to \textbf{put} it somewhere that isn't just \textbf{inside} my \textbf{own} \textbf{head}.

% matched lemmas: annoy, answer, anyone, anything, ask, bad, belong, catch, check, conversation, day, delete, dramatic, errand, everyone, everything, explain, feel, fine, friend, get, group, hang, head, inside, job, join, keep, know, lie, life, light, like, look, loud, medium, message, move, need, night, nod, noise, notice, old, outside, own, paper, people, person, phone, plan, polite, put, reach, replay, reply, room, say, scroll, see, send, sense, silence, sit, social, something, sound, speak, start, stupid, talk, tell, thing, think, time, try, turn, use, wait, want, watch, weekend, weird, work
\end{textsample}
