\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 55.00 – summary\_guided\_gpt/t2136\_gpt.txt}  \label{ex:f1_pos_021}
I lost my last grandmother about two months before the new year, and the grief has been this \textbf{weird}, \textbf{quiet} \textbf{thing} that just \textbf{sits} with me all the \textbf{time}.
It ’s not \textbf{loud} or \textbf{dramatic}, \textbf{more} \textbf{like} a dull \textbf{ache} that \textbf{keeps} humming in the \textbf{background} of \textbf{everything} I do.
What \textbf{makes} it confusing is that we weren't especially \textbf{close}.
She wasn't my “ favourite ” grandparent, not the one I visited the \textbf{most} or \textbf{told} \textbf{everything} to.
If you \textbf{looked} at it from the \textbf{outside}, you ’d probably \textbf{think} I ’d be \textbf{fine}.
A lot of \textbf{people} around me do \textbf{seem} to \textbf{assume} that.
They ’ll \textbf{say}, “ Oh, you weren't that \textbf{close}, \textbf{right}? ” and then \textbf{move} on, \textbf{like} that \textbf{explains} \textbf{everything} and means I shouldn't be hurting.
But I do hurt.
A lot \textbf{more} than I \textbf{expected}.
It ’s little everyday \textbf{moments} that \textbf{hit} the hardest.
When my classmates \textbf{talk} about \textbf{missing} their \textbf{families} or grandparents, I \textbf{feel} this emptiness \textbf{open} up \textbf{inside} me.
I \textbf{miss} her voice, the \textbf{way} she would repeat the \textbf{same} \textbf{stories}, her forgetfulness that we ’d gently \textbf{laugh} about.
I \textbf{miss} just \textbf{knowing} she was there, \textbf{existing} in the \textbf{background} of my \textbf{life}.
I didn't \textbf{realize} how \textbf{much} comfort that gave me until it was \textbf{gone}.
Now that she isn't here anymore, \textbf{something} in me \textbf{feels} … shifted.
Or broken. \textbf{Like} a \textbf{part} of the foundation under my \textbf{life} has quietly crumbled, even though it wasn't the \textbf{most} visible or important \textbf{part}.
I \textbf{keep} \textbf{thinking}, “ Why is this \textbf{hitting} me so hard when we weren't that \textbf{close}? ” and I don't really have an \textbf{answer}.
I also \textbf{feel} pretty alone with it.
Since \textbf{people} \textbf{think} I ’m \textbf{fine}, there isn't really \textbf{space} to \textbf{talk} about how \textbf{strange} and \textbf{heavy} this \textbf{feels}.
I \textbf{end} up just carrying it around by myself, \textbf{pretending} it ’s not a big deal because that ’s what \textbf{everyone} \textbf{seems} to \textbf{expect}.
I ’m sharing this here because I ’m wondering if \textbf{anyone} else has \textbf{gone} through \textbf{something} similar—missing \textbf{someone} \textbf{way} \textbf{more} than you \textbf{thought} you would, even if the relationship wasn't super \textbf{close} or perfect.
It would help to \textbf{know} I ’m not the only one who \textbf{feels} this \textbf{kind} of \textbf{quiet}, confusing grief.

% matched lemmas: ache, answer, anyone, assume, background, close, dramatic, end, everyone, everything, exist, expect, explain, family, feel, fine, go, heavy, hit, inside, keep, kind, know, laugh, life, like, look, loud, make, miss, moment, more, most, move, much, open, outside, part, people, pretend, quiet, realize, right, same, say, seem, sit, someone, something, space, story, strange, talk, tell, thing, think, time, way, weird
\end{textsample}
