\begin{textsample}{POS Dim 1 – human – Score 45.00 – human/t2079\_human.txt}  \label{ex:f1_pos_035}
I ’m officially giving up.
I have no \textbf{friends}, and I ’ve \textbf{reached} the point where this isn't just"sadness"anymore—it ’s a goddamn complex that ’s eating me alive. \textbf{Everyone} \textbf{keeps} preaching :"Socializing is a skill!
Practice it!"Well, screw you.
My \textbf{social} muscle didn't just atrophy ; it rotted and fell off. \textbf{Trying} to restore this"abandoned building"of a \textbf{life}?
It ’s useless.
It ’s \textbf{like} \textbf{trying} to glue ashes back together.
Recently, I \textbf{tried}.
I \textbf{reached} out to \textbf{someone} I hadn't \textbf{spoken} to in 19 \textbf{days}.
I simply \textbf{asked} if they had any \textbf{friends}.
And what \textbf{happened}?
Total \textbf{silence}. 24 hours of being ignored.
Another"500,000 years of \textbf{silence}."I snapped.
I \textbf{sent} a \textbf{message} \textbf{saying},"Of course, why would you \textbf{need} me when you already have a \textbf{couple} of \textbf{real} \textbf{friends} anyway?"and I blocked them.
Yeah, I struck \textbf{first}.
Yeah, I cut the cord myself.
And I don't \textbf{feel} sorry for that \textbf{person}.
I \textbf{feel} sorry for myself because I ’m back in this pit.
I did it so I wouldn't have to \textbf{sit} there staring at my screen \textbf{like} a beaten dog, \textbf{waiting} for a"charity \textbf{reply}."I took back control the only \textbf{way} I \textbf{know} how—through blocking and aggression.
I don't even have a freaking PC to lose myself in games.
My whole world is this damn \textbf{phone}.
A \textbf{window} into a world that ignores me.
Every attempt to \textbf{start} a \textbf{conversation} \textbf{turns} into torture : a \textbf{couple} of \textbf{stupid}, dry phrases, and then—emptiness.
I don't \textbf{want} to \textbf{talk} to chatbots \textbf{like} they ’re human ; it ’s a pathetic substitute.
I \textbf{need} \textbf{real} warmth, but apparently, I ’m so broken that I just \textbf{make} \textbf{people} \textbf{want} to \textbf{shut} up and \textbf{walk} away.
What ’s the point of even \textbf{trying}?
To prove to myself one \textbf{more} \textbf{time} that I ’m worthless?
To \textbf{feel} that sting again when your \textbf{message} stays"read"and ignored?
I hate this state, I hate my helplessness, and I hate this endless grief that \textbf{hits} the \textbf{second} after I ’ve pushed \textbf{everyone} away.
Are there any \textbf{other}"abandoned buildings"out here? \textbf{Anyone} who has \textbf{stopped} believing in"self-improvement"and just \textbf{wants} this \textbf{social} thirst to finally die so it \textbf{stops} hurting?
The \textbf{text} was written with the help of AI because I couldn't have done it myself.

% matched lemmas: anyone, ask, conversation, couple, day, everyone, feel, first, friend, happen, hit, keep, know, life, like, make, message, more, need, other, people, person, phone, reach, real, reply, say, second, send, shut, silence, sit, social, someone, speak, start, stop, stupid, talk, text, time, try, turn, wait, walk, want, way, window
\end{textsample}
