\begin{textsample}{POS Dim 1 – generic\_gpt – Score 81.00 – generic\_gpt/t1888\_gpt.txt}  \label{ex:f1_pos_008}
I ’ve been \textbf{feeling} this \textbf{weird} combination of \textbf{invisible} and “ too \textbf{much} ” at the \textbf{same} \textbf{time}, and I don't really \textbf{know} where else to \textbf{put} it, so here it \textbf{goes}.
On \textbf{paper}, my \textbf{life} \textbf{looks} \textbf{fine}.
I have a \textbf{job}, a \textbf{place} to live, \textbf{people} I can technically \textbf{contact} if I \textbf{need} \textbf{something}.
But I don't \textbf{feel} actually *known* by \textbf{anyone}. \textbf{Most} of my \textbf{interactions} are surface-level : \textbf{work} \textbf{small} \textbf{talk}, occasional memes in \textbf{group} \textbf{chats}, the “ we should \textbf{catch} up sometime ” \textbf{messages} that never \textbf{turn} into \textbf{anything} \textbf{real}.
I \textbf{keep} \textbf{thinking} I ’m \textbf{part} of \textbf{people} ’s \textbf{lives}, then I \textbf{realize} I ’m \textbf{more} \textbf{like} a \textbf{background} \textbf{character}.
I ’ve \textbf{noticed} that when I ’m around \textbf{people}, I \textbf{feel} lonelier than when I ’m alone.
It ’s \textbf{like} there ’s this \textbf{glass} \textbf{wall} between me and \textbf{everyone} else.
I can \textbf{see} them \textbf{laughing} and \textbf{connecting}, but I can't \textbf{seem} to \textbf{join} in properly.
I either \textbf{talk} too \textbf{much} because I ’m nervous and \textbf{trying} to fill the \textbf{silence}, or I \textbf{shut} down completely and just listen, then \textbf{go} \textbf{home} and overanalyze every \textbf{word} I \textbf{said}.
I also \textbf{feel} \textbf{like} I \textbf{missed} some critical \textbf{social} development stage. \textbf{Other} \textbf{people} \textbf{seem} to just \textbf{know} how to maintain friendships, how often to \textbf{text}, how to \textbf{ask} to \textbf{hang} out without \textbf{sounding} desperate or \textbf{annoying}.
For me, every \textbf{message} \textbf{feels} \textbf{like} I ’m imposing.
I \textbf{wait} for \textbf{people} to \textbf{reach} out \textbf{first}, they don't, and then I \textbf{use} that as proof that I don't matter that \textbf{much} to them. \textbf{Nights} are the \textbf{worst}.
I \textbf{lie} in \textbf{bed} \textbf{scrolling}, \textbf{seeing} \textbf{people} posting \textbf{photos} with their \textbf{friends}, partners, \textbf{families}.
I \textbf{know} \textbf{social} \textbf{media} is curated, but it still stings.
I \textbf{keep} \textbf{thinking}, “ No one is \textbf{thinking} about me \textbf{right} now.
If I \textbf{disappeared}, it would take a \textbf{while} before \textbf{anyone} \textbf{noticed}. ” I ’m not even \textbf{sure} what I ’m hoping for by posting this.
I \textbf{guess} I just \textbf{wanted} to \textbf{put} it somewhere \textbf{outside} my \textbf{own} \textbf{head} for once.

% matched lemmas: annoy, anyone, anything, ask, background, bad, bed, catch, character, chat, connect, contact, disappear, everyone, family, feel, fine, first, friend, glass, go, group, guess, hang, head, home, interaction, invisible, job, join, keep, know, laugh, lie, life, like, look, medium, message, miss, more, most, much, need, night, notice, other, outside, own, paper, part, people, photo, place, put, reach, real, realize, right, same, say, scroll, see, seem, shut, silence, small, social, something, sound, sure, talk, text, think, time, try, turn, use, wait, wall, want, weird, while, word, work
\end{textsample}
