\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 51.00 – summary\_guided\_gpt/t1812\_gpt.txt}  \label{ex:f1_pos_030}
I ’m 19 and I \textbf{feel} \textbf{like} my \textbf{life} is already over before it ’s even \textbf{started}.
I don't have any \textbf{friends}, never had a boyfriend, and I haven't had a \textbf{real} \textbf{social} \textbf{life} in years. \textbf{Most} \textbf{days} I ’m just at \textbf{home}, doing \textbf{nothing}, \textbf{watching} \textbf{everyone} else my age \textbf{move} forward \textbf{while} I ’m stuck.
I \textbf{got} held back in school so I ’m still in high school, and that just \textbf{makes} me \textbf{feel} even \textbf{more} behind and pathetic.
I struggle with depression and anxiety from OCD, and it \textbf{feels} \textbf{like} my brain is constantly \textbf{working} against me.
When I ’m in public I avoid \textbf{talking} to \textbf{people} as \textbf{much} as possible.
I freeze up, overthink every \textbf{word}, and just \textbf{want} to \textbf{disappear}.
Online isn't \textbf{much} better.
I ’m really self‑conscious about how I \textbf{look}, so I hate \textbf{social} apps, and even when I \textbf{want} to \textbf{reach} out I overthink every sentence and \textbf{end} up \textbf{deleting} it.
With my \textbf{close} \textbf{family} I can actually be confident and outspoken.
I can \textbf{joke} around and be myself.
But the \textbf{second} it ’s \textbf{anyone} \textbf{outside} that tiny \textbf{circle}, I \textbf{turn} into this shy, timid, nervous \textbf{person} who can't \textbf{say} or do \textbf{anything} \textbf{right}.
It ’s \textbf{like} there are two \textbf{versions} of me and the one I \textbf{want} to be only \textbf{exists} at \textbf{home}.
Sometimes \textbf{people} online \textbf{say}, “ If you ever \textbf{want} to \textbf{talk}, my DMs are \textbf{open}, ” and instead of \textbf{feeling} happy, I just \textbf{assume} they ’re being \textbf{polite}.
I ’m \textbf{scared} they ’ll \textbf{see} me as a burden or \textbf{get} bored and leave.
I \textbf{keep} \textbf{checking} Reddit for responses, hoping \textbf{someone} will \textbf{say} \textbf{something} that \textbf{makes} me \textbf{feel} less alone, and then hating myself for caring so \textbf{much}.
I ’m \textbf{scared} that when I ’m thirty I ’ll still be living with my parents, barely leaving the house, and still this lonely.
I don't \textbf{know} if I ’ll ever have the happy \textbf{life} I \textbf{want}, and that thought really hurts.

% matched lemmas: anyone, anything, assume, check, circle, close, day, delete, disappear, end, everyone, exist, family, feel, friend, get, home, joke, keep, know, life, like, look, make, more, most, move, much, nothing, open, outside, people, person, polite, reach, real, right, say, scare, second, see, social, someone, something, start, talk, turn, version, want, watch, while, word, work
\end{textsample}
