\begin{textsample}{POS Dim 1 – generic\_gpt – Score 79.00 – generic\_gpt/t2732\_gpt.txt}  \label{ex:f1_pos_020}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} I ’m just drifting through my \textbf{own} \textbf{life} as a \textbf{background} \textbf{character}.
I have \textbf{people} around me, technically. \textbf{Coworkers}, a \textbf{couple} of \textbf{old} \textbf{friends} I \textbf{text} every now and then, \textbf{family} \textbf{chats} that \textbf{light} up my \textbf{phone}.
But I don't \textbf{feel} *connected* to any of it.
It ’s \textbf{like} \textbf{watching} a \textbf{group} \textbf{conversation} through a \textbf{window}.
I can \textbf{see} \textbf{everyone} \textbf{laughing}, reacting, being \textbf{part} of \textbf{something}, and I ’m just … pressing my face against the \textbf{glass}.
What \textbf{messes} with my \textbf{head} is that from the \textbf{outside}, I probably \textbf{look} \textbf{fine}.
I \textbf{go} to \textbf{work}, \textbf{make} \textbf{small} \textbf{talk}, \textbf{send} memes, \textbf{answer} “ how are you? ” with “ I ’m good, you? ” \textbf{like} it ’s automatic.
No one \textbf{sees} that once I \textbf{get} \textbf{home}, it ’s just \textbf{silence}.
I \textbf{put} my bag down, \textbf{sit} on the \textbf{bed}, and there ’s this \textbf{heavy}, hollow \textbf{feeling}. \textbf{Like} I ’m \textbf{missing} \textbf{something} I can't even \textbf{name}.
I don't \textbf{think} I ’ve ever had that “ \textbf{person} ” \textbf{people} \textbf{talk} about.
The one you can \textbf{message} without overthinking, the one who actually \textbf{checks} in because they \textbf{want} to, not because it ’s \textbf{polite}.
I have \textbf{acquaintances} who are nice enough, but I always \textbf{feel} \textbf{like} a temporary guest in their \textbf{lives}, never \textbf{someone} whose absence would really matter.
I overanalyze \textbf{everything} I \textbf{say}.
I \textbf{replay} \textbf{conversations} and \textbf{convince} myself I \textbf{sounded} \textbf{weird} or \textbf{annoying}.
Then I \textbf{pull} back a bit, \textbf{respond} slower, become “ \textbf{busy}, ” and that just reinforces the distance.
I \textbf{know} I ’m \textbf{part} of my \textbf{own} problem, but \textbf{knowing} that doesn't magically \textbf{fix} it.
It just adds guilt on top of the loneliness.
Sometimes I \textbf{scroll} through \textbf{social} \textbf{media} and \textbf{see} \textbf{people} doing the \textbf{most} mundane \textbf{things} together—grocery shopping, \textbf{watching} movies, \textbf{sitting} on the floor eating takeout—and it \textbf{feels} \textbf{like} another universe.
I ’m not even craving big parties or \textbf{constant} attention.
I just \textbf{want} to \textbf{feel} \textbf{like} I \textbf{belong} somewhere specific, with \textbf{someone} specific. \textbf{Most} \textbf{days} I just \textbf{go} through the \textbf{motions}, hoping \textbf{something} will eventually shift, but I honestly don't \textbf{know} what I ’m \textbf{waiting} for or what I ’m \textbf{supposed} to do differently.
It just \textbf{feels} \textbf{like} I ’m slowly fading out around the \textbf{edges} and no one ’s really \textbf{noticing}.

% matched lemmas: acquaintance, annoy, answer, background, bed, belong, busy, character, chat, check, constant, conversation, convince, couple, coworker, day, dramatic, edge, everyone, everything, explain, family, feel, feeling, fine, fix, friend, get, glass, go, group, head, heavy, home, know, laugh, life, light, like, look, make, medium, mess, message, miss, most, motion, name, notice, old, outside, own, part, people, person, phone, polite, pull, put, replay, respond, say, scroll, see, send, silence, sit, small, social, someone, something, sound, suppose, talk, text, thing, think, wait, want, watch, weird, window, work
\end{textsample}
