\begin{textsample}{POS Dim 1 – human – Score 22.00 – human/t810\_human.txt}  \label{ex:f1_pos_036}
( This is translated with GPT because I don't speak English very well ) I ’m ( 20M ) and today I feel lonelier than usual.
Today is my birthday and it feels strange.
Only one \textbf{person} congratulated me, and \textbf{none} of my \textbf{family} has.
On top of that, I ’ve been sick with the flu for 4 \textbf{days}, so I don't even have the energy to do \textbf{anything}.
I ’ve lived a lonely \textbf{life} all these years, and it ’s \textbf{something} I ’ve gotten used to.
About 3 years ago, I met a girl on Discord in a community a \textbf{friend} created.
We were \textbf{friends} for about a year, and then we became long-distance \textbf{partners}.
It was a beautiful relationship that lasted a year.
But the relationship \textbf{ended} on her side, \textbf{while} I still loved her and wanted to continue, since the problem wasn't between us but \textbf{something} external.
The breakup happened during the first \textbf{week} of November ( right when our anniversary was coming up ).
It hit me really hard because with her I didn't need \textbf{anyone} else to socialize with.
I had \textbf{friends}, with whom I ’m still in touch, but I haven't had \textbf{anyone} else to socialize with at the level I did with her. ( In my \textbf{family}, I was raised in a \textbf{way} where we don't usually \textbf{talk} about our \textbf{feelings}. ) With her, I could tell her about my \textbf{day}, what I did, what I wanted to do.
She told me about her \textbf{life}, about her dreams, which also became mine, because before I met her I was totally lost, without dreams or goals, and she made me dream.
It ’s been about 10 months since the breakup, and honestly the only \textbf{thing} I ’ve missed is having that \textbf{kind} of \textbf{connection} again.
I don't miss her ; I miss what I could do with her and the fact that I could open up emotionally to \textbf{someone} else.
Also, because of how my \textbf{family} treated me during childhood, it ’s really hard for me to open up emotionally to other \textbf{people} and be sociable.
Sorry if this isn't well structured, but it ’s just what I ’m thinking in the \textbf{moment}.

% matched lemmas: anyone, anything, connection, day, end, family, feeling, friend, kind, life, moment, none, partner, people, person, someone, something, talk, thing, way, week, while
\end{textsample}
