\begin{textsample}{POS Dim 1 – generic\_gpt – Score 83.00 – generic\_gpt/t467\_gpt.txt}  \label{ex:f1_pos_004}
I don't really \textbf{know} how to \textbf{explain} this without \textbf{sounding} \textbf{dramatic}, but lately it \textbf{feels} \textbf{like} my \textbf{life} is just … empty \textbf{space} filled with \textbf{noise}.
I ’m technically “ not alone. ” I have \textbf{coworkers}, some \textbf{acquaintances}, a \textbf{family} that \textbf{texts} occasionally, \textbf{group} \textbf{chats} that \textbf{light} up with memes.
But \textbf{none} of it \textbf{feels} \textbf{like} it actually \textbf{touches} me.
It ’s \textbf{like} \textbf{everyone} is behind \textbf{glass} and I ’m waving from the \textbf{other} side, and they either don't \textbf{see} me or just \textbf{assume} I ’m \textbf{fine} because I can still \textbf{crack} a \textbf{joke} and \textbf{reply} with emojis.
The \textbf{weird} \textbf{thing} is I \textbf{used} to \textbf{think} loneliness meant having no one.
But it ’s \textbf{more} \textbf{like} having \textbf{people} around and still \textbf{feeling} \textbf{like} you ’re on mute.
I \textbf{go} through the \textbf{motions} : wake up, \textbf{work}, \textbf{pretend} to be \textbf{normal} in front of \textbf{others}, come \textbf{home}, \textbf{scroll} through \textbf{social} \textbf{media}, \textbf{watch} \textbf{other} \textbf{people} ’s \textbf{lives} \textbf{happen}.
Then I \textbf{lie} in \textbf{bed} with this \textbf{heavy} \textbf{feeling} in my chest, \textbf{like} I ’m \textbf{missing} \textbf{something} huge I can't even \textbf{name}.
I don't really \textbf{talk} about this in \textbf{real} \textbf{life}.
When I \textbf{try} to \textbf{open} up, it \textbf{feels} \textbf{like} I ’m burdening \textbf{people} or being “ too \textbf{much}. ” I ’ve had a few \textbf{moments} where I \textbf{started} to \textbf{say}, “ I ’ve been \textbf{feeling} really alone lately, ” and the \textbf{conversation} somehow slid back into \textbf{small} \textbf{talk} about \textbf{shows} or \textbf{work} or whatever.
I don't even blame them.
I just \textbf{feel} \textbf{stupid} for \textbf{trying}.
There ’s also this growing fear that I ’m slowly becoming \textbf{someone} who doesn't \textbf{know} how to \textbf{connect} anymore.
I overthink every \textbf{message} I \textbf{send}, every pause in \textbf{conversation}, every \textbf{time} \textbf{someone} doesn't \textbf{reply}.
I \textbf{replay} \textbf{interactions} in my \textbf{head} and pick them apart, wondering if I \textbf{sounded} \textbf{weird} or clingy.
Then I \textbf{pull} back a bit \textbf{more}, \textbf{tell} myself it ’s \textbf{easier} not to \textbf{expect} \textbf{anything}. \textbf{Days} blend together.
Sometimes I ’ll \textbf{go} the whole \textbf{weekend} without \textbf{using} my voice out \textbf{loud}, and I don't \textbf{notice} until I have to \textbf{talk} to \textbf{someone} and my throat \textbf{feels} tight and unused.
It ’s unsettling, \textbf{realizing} how \textbf{easy} it is to \textbf{disappear} from \textbf{other} \textbf{people} ’s \textbf{lives} without \textbf{anyone} really \textbf{noticing}, including your \textbf{own}.

% matched lemmas: acquaintance, anyone, anything, assume, bed, chat, connect, conversation, coworker, crack, day, disappear, dramatic, easy, everyone, expect, explain, family, feel, feeling, fine, glass, go, group, happen, head, heavy, home, interaction, joke, know, lie, life, light, like, loud, medium, message, miss, moment, more, motion, much, name, noise, none, normal, notice, open, other, own, people, pretend, pull, real, realize, replay, reply, say, scroll, see, send, show, small, social, someone, something, sound, space, start, stupid, talk, tell, text, thing, think, time, touch, try, use, watch, weekend, weird, work
\end{textsample}
