\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 52.00 – summary\_guided\_gpt/t1264\_gpt.txt}  \label{ex:f1_pos_029}
Some \textbf{weeks} I can \textbf{go} \textbf{days} without \textbf{speaking} to \textbf{anyone}.
I \textbf{go} to \textbf{work}, I \textbf{answer} emails, I do the basic “ how are you / good thanks ” \textbf{stuff}, but there ’s no \textbf{real} \textbf{contact}.
I come \textbf{home}, eat, \textbf{scroll}, \textbf{sleep}.
It \textbf{starts} to \textbf{feel} \textbf{like} I ’m just \textbf{watching} my \textbf{own} \textbf{life} from the \textbf{outside}, \textbf{like} it ’s \textbf{happening} to some \textbf{other} \textbf{person} I barely \textbf{know}.
When I ’m around \textbf{family}, I \textbf{put} on the “ I ’m \textbf{fine} ” \textbf{version} of myself.
I can \textbf{feel} that my loneliness \textbf{makes} \textbf{people} uncomfortable, \textbf{like} it ’s \textbf{something} \textbf{awkward} they don't \textbf{know} what to do with.
So it never really \textbf{gets} \textbf{talked} about.
No one is cruel or openly dismissive, but it just sort of … floats there, unacknowledged.
It leaves me \textbf{feeling} quietly unsupported rather than obviously abandoned, which somehow hurts in a \textbf{more} subtle \textbf{way}.
The \textbf{strange} \textbf{part} is I ’m very aware that, in theory, I ’m free to \textbf{change} this.
I \textbf{know} the \textbf{kinds} of \textbf{things} I could \textbf{try}, the steps I ’d probably \textbf{need} to take.
But I \textbf{feel} paralyzed.
It ’s \textbf{like} standing in front of a \textbf{door} that I \textbf{know} is unlocked and just … not being able to \textbf{turn} the handle.
That “ freedom ” \textbf{starts} to \textbf{feel} \textbf{like} its \textbf{own} \textbf{kind} of prison, because every \textbf{day} I don't \textbf{change} \textbf{anything}, I \textbf{end} up blaming myself.
I \textbf{feel} \textbf{like} I ’m wasting \textbf{time} and failing at \textbf{something} really basic that \textbf{everyone} else \textbf{seems} to manage without thinking.
On the \textbf{surface} I ’m functioning : I \textbf{get} up, I \textbf{work}, I pay my bills, I feed myself.
Underneath, I \textbf{feel} stuck, frozen by all the choices I could \textbf{make} but don't, and deeply disappointed in myself for not being braver.
I wish I had \textbf{someone} I could really lean on, but it doesn't \textbf{feel} \textbf{like} that ’s truly available.
So it all \textbf{feels} \textbf{like} it rests on me alone, and I ’m so tired of carrying it.
I ’m not \textbf{asking} for advice.
I just \textbf{needed} to \textbf{say} this out \textbf{loud} somewhere.
And if \textbf{anyone} else \textbf{feels} this \textbf{way} too, you ’re not the only one.

% matched lemmas: answer, anyone, anything, ask, awkward, change, contact, day, door, end, everyone, family, feel, fine, get, go, happen, home, kind, know, life, like, loud, make, more, need, other, outside, own, part, people, person, put, real, say, scroll, seem, sleep, someone, something, speak, start, strange, stuff, surface, talk, thing, time, try, turn, version, watch, way, week, work
\end{textsample}
