\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 54.00 – summary\_guided\_gpt/t776\_gpt.txt}  \label{ex:f1_pos_024}
I ’ve always had this fear of \textbf{ending} up alone, and lately it \textbf{feels} \textbf{like} I ’m living it.
On \textbf{paper}, I ’m pretty independent.
I ’m generally at peace in my \textbf{own} \textbf{space}, I don't mind being at \textbf{home}, and I can function just \textbf{fine} \textbf{day} to \textbf{day}.
But it ’s \textbf{like} the \textbf{moment} I \textbf{stop} distracting myself, the loneliness just slams into me. \textbf{Most} of my friendships have basically faded because I ’m always the one \textbf{reaching} out \textbf{first}.
If I don't \textbf{text} or \textbf{call}, \textbf{nothing} \textbf{happens}.
Over \textbf{time}, that \textbf{made} me \textbf{feel} \textbf{like} I was \textbf{forcing} my presence on \textbf{people}, so I \textbf{stopped} \textbf{initiating} as \textbf{much}.
The result is that now … there ’s almost \textbf{nothing}.
Just \textbf{silence}.
It ’s hard not to interpret that as proof that I don't really matter to \textbf{anyone}.
A little over two months ago, I \textbf{ended} a relationship.
I still \textbf{miss} him intensely.
There are \textbf{days} I have to fight the urge to unblock him and just hear his voice.
But I don't trust that he could really \textbf{change}, and I ’m \textbf{trying} to choose myself this \textbf{time}, even though it hurts.
So he stays blocked, and I \textbf{sit} with this \textbf{ache} that doesn't \textbf{seem} to \textbf{go} away.
My best \textbf{friend} was also an ex from years ago.
We \textbf{ended} up relying on each \textbf{other} emotionally a lot.
I \textbf{started} worrying that I was too \textbf{needy} and dependent on him.
He also \textbf{started} \textbf{working} \textbf{nights}, and it \textbf{felt} \textbf{like} our communication was \textbf{getting} strained.
Eventually we mutually decided to \textbf{go} no \textbf{contact} and blocked each \textbf{other}.
It \textbf{felt} \textbf{like} the “ mature ” decision at the \textbf{time}, but it also \textbf{felt} \textbf{like} cutting off one of the only \textbf{people} who really \textbf{knew} me.
Later, an \textbf{old} \textbf{friend} \textbf{told} me she \textbf{thought} he might still have romantic \textbf{feelings} for me.
That completely \textbf{messed} with my \textbf{head}.
Now I ’m \textbf{questioning} whether that friendship was ever really just friendship, or if he was just \textbf{hanging} around hoping for another chance.
It \textbf{makes} the loss \textbf{feel} different, almost tainted.
So in a short period, I ’ve lost the two \textbf{most} important \textbf{people} in my \textbf{life}.
I don't \textbf{know} if I should \textbf{try} to seek \textbf{answers} or just accept it and \textbf{move} on. \textbf{Right} now it just \textbf{feels} extremely hard, \textbf{like} I ’m standing in this empty \textbf{space} where my support system \textbf{used} to be, and I have no idea what to do next.

% matched lemmas: ache, answer, anyone, call, change, contact, day, end, feel, feeling, fine, first, force, friend, get, go, hang, happen, head, home, initiate, know, life, like, make, mess, miss, moment, most, move, much, needy, night, nothing, old, other, own, paper, people, question, reach, right, seem, silence, sit, space, start, stop, tell, text, think, time, try, use, work
\end{textsample}
