\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 55.00 – summary\_guided\_gpt/t555\_gpt.txt}  \label{ex:f1_pos_023}
I \textbf{ended} a long-term relationship a little \textbf{while} ago, and I \textbf{feel} \textbf{like} I lost \textbf{everything} in one \textbf{go}.
He wasn't just my boyfriend, he was my best \textbf{friend}, my emotional support, the one \textbf{person} I could actually \textbf{talk} to and \textbf{feel} safe with.
In a \textbf{life} and household that already \textbf{felt} \textbf{heavy} and difficult, he was \textbf{kind} of the only \textbf{light}.
Now that he ’s \textbf{gone}, it \textbf{feels} \textbf{like} \textbf{someone} switched that \textbf{light} off and I ’m just stumbling around in the dark.
I don't really have \textbf{anyone} I can \textbf{turn} to now.
I can't have \textbf{normal} \textbf{conversations} with my \textbf{family}, let alone \textbf{talk} to them about how I \textbf{feel}.
It just doesn't \textbf{feel} possible or safe to seek comfort from them.
So I \textbf{keep} it all \textbf{inside} and \textbf{pretend} I ’m \textbf{fine}. \textbf{Outside} of that, I basically only have two \textbf{people} in my \textbf{life}.
One \textbf{friend} I bonded with because we were both in relationships, but now we barely \textbf{see} each \textbf{other} or \textbf{talk}.
The \textbf{other} \textbf{friend} hardly \textbf{replies} anymore and has become really distant.
I can \textbf{feel} them both slipping away and I don't \textbf{know} how to \textbf{stop} it.
I ’m in university, and \textbf{everyone} always \textbf{talks} about this being “ the \textbf{time} of your \textbf{life}, ” but it doesn't \textbf{feel} \textbf{like} that for me at all.
I ’ve always struggled to \textbf{make} and \textbf{keep} \textbf{friends}.
I \textbf{feel} \textbf{awkward} and not very \textbf{social}, \textbf{like} I ’m just fundamentally \textbf{bad} at this.
It \textbf{feels} \textbf{like} it takes a very specific \textbf{kind} of \textbf{person} to tolerate me long term, and those \textbf{people} are rare.
I have \textbf{tried} to be \textbf{open} and \textbf{start} \textbf{conversations} at uni.
Sometimes it \textbf{seems} to \textbf{go} \textbf{okay} at \textbf{first}, but then it just … fizzles out. \textbf{People} don't follow up, don't \textbf{message}, or even avoid \textbf{sitting} next to me.
I don't \textbf{know} what I ’m doing wrong, or if there ’s just \textbf{something} about me that \textbf{puts} \textbf{people} off. \textbf{Most} \textbf{days} I just \textbf{go} to class, \textbf{sit} alone, eat lunch alone, and \textbf{go} \textbf{home} alone.
Sometimes I \textbf{go} an entire \textbf{day} barely \textbf{speaking} to \textbf{anyone}, maybe just a quick comment here or there.
I \textbf{feel} \textbf{like} a ghost \textbf{walking} around campus, \textbf{watching} \textbf{everyone} else form \textbf{groups}, \textbf{laugh}, and \textbf{make} memories \textbf{while} I just \textbf{exist} on the \textbf{edges}.
I \textbf{feel} out of \textbf{place} and I \textbf{keep} \textbf{asking} myself what the point of being there even is, when I ’m just so lonely all the \textbf{time}.

% matched lemmas: anyone, ask, awkward, bad, conversation, day, edge, end, everyone, everything, exist, family, feel, fine, first, friend, go, group, heavy, home, inside, keep, kind, know, laugh, life, light, like, make, message, most, normal, okay, open, other, outside, people, person, place, pretend, put, reply, see, seem, sit, social, someone, something, speak, start, stop, talk, time, try, turn, walk, watch, while
\end{textsample}
