\begin{textsample}{POS Dim 1 – summary\_guided\_gpt – Score 52.00 – summary\_guided\_gpt/t967\_gpt.txt}  \label{ex:f1_pos_028}
I \textbf{feel} \textbf{like} I ’m just … \textbf{existing} on mute.
I have this one \textbf{friend} I \textbf{hang} out with sometimes, but I ’m always the one who has to \textbf{text} \textbf{first}, always the one who suggests meeting up.
If I don't \textbf{reach} out, we just don't \textbf{talk}.
It \textbf{makes} me \textbf{feel} \textbf{like} they don't really \textbf{want} to \textbf{see} me, \textbf{like} I ’m just \textbf{something} they tolerate when I appear, not \textbf{someone} they ’d actually \textbf{miss}.
I ’m \textbf{trying} to push myself to \textbf{go} out alone, to \textbf{sit} in cafés or \textbf{walk} around so I ’m not always trapped \textbf{inside}, but it just \textbf{makes} me painfully aware of how \textbf{silent} my \textbf{life} is.
No one \textbf{asks} how my \textbf{day} was.
No one is \textbf{waiting} to hear about the little \textbf{things}.
The loneliness is so draining.
I cope by imagining being with \textbf{someone}, \textbf{making} up \textbf{conversations} in my \textbf{head}, or “ \textbf{watching} ” movies with YouTubers and \textbf{pretending} they ’re \textbf{friends} \textbf{sitting} next to me.
I \textbf{know} it ’s not \textbf{real}, but it fills the \textbf{silence} a bit.
Still, when the video \textbf{ends}, it ’s just me again. \textbf{Work} \textbf{makes} it \textbf{worse}. \textbf{Everyone} else \textbf{seems} to have partners, \textbf{families}, \textbf{people} to \textbf{go} \textbf{home} to.
They \textbf{talk} about their \textbf{weekend} \textbf{plans}, their kids, their relationships.
Then the \textbf{day} \textbf{ends} and they leave in pairs or \textbf{groups}, and I ’m the one walking out alone, \textbf{waiting} for the bus alone, \textbf{going} \textbf{home} to no one.
It \textbf{makes} me wonder what ’s wrong with me.
Am I too fat, too ugly, too \textbf{annoying}, too … \textbf{something}?
There ’s also this boy I have \textbf{feelings} for, but he always \textbf{seems} to find \textbf{someone} else to love.
I ’m just there on the sidelines, \textbf{watching} it \textbf{happen} again and again.
It hurts \textbf{more} than I \textbf{want} to admit.
I \textbf{try} to stay positive, to \textbf{keep} my brain \textbf{busy} with information, \textbf{shows}, \textbf{random} interests.
I fill my \textbf{time} hoping that one \textbf{day} I ’ll have \textbf{someone} to \textbf{talk} to about all of it.
But even in my \textbf{own} thoughts, I \textbf{feel} lonely.
It ’s \textbf{like} there ’s an echo where another \textbf{person} should be.

% matched lemmas: annoy, ask, bad, busy, conversation, day, end, everyone, exist, family, feel, feeling, first, friend, go, group, hang, happen, head, home, inside, keep, know, life, like, make, miss, more, own, people, person, plan, pretend, random, reach, real, see, seem, show, silence, silent, sit, someone, something, talk, text, thing, time, try, wait, walk, want, watch, weekend, work
\end{textsample}
