\begin{textsample}{NEG Dim 2 – generic\_gpt – Score -3.00 – generic\_gpt/t744\_gpt.txt}  \label{ex:f2_neg_006}
I ’ve been feeling this weird \textbf{mix} of invisible and too exposed at the same time.
On paper, I ’m not “ alone. ” I have coworkers, a few old friends I text every now and then, family chats that light up my phone.
But none of it feels like it really touches me.
It ’s like I ’m standing behind \textbf{glass} watching my own life happen.
I go through the motions : work, gym, scrolling, sleep.
I laugh at the right times, make small talk, answer “ I ’m good, you? ” without thinking.
Then I get home, close the door, and it hits me how quiet everything is.
Not just the room—my life.
There ’s no one who really expects me, no one I can send a random thought to without overthinking if I ’m being annoying.
What bothers me most is how replaceable I feel.
If I stopped showing up, I think \textbf{people} would notice for a bit, then just … adjust.
I don't feel like I ’m anyone ’s first choice, or even second.
More like background \textbf{noise}.
I ’ve tried joining clubs, going to events, talking more.
It always feels shallow, like I ’m auditioning for a \textbf{role} I never get.
I leave feeling more drained and more aware of how disconnected I am.
I don't even know what I ’m looking for exactly.
Just something that makes me feel like I actually exist to someone, beyond a name in a group chat or a face at a desk.

% matched lemmas: glass, mix, noise, people, role
\end{textsample}
