\begin{textsample}{NEG Dim 2 – summary\_guided\_gpt – Score -3.00 – summary\_guided\_gpt/t398\_gpt.txt}  \label{ex:f2_neg_021}
I ’m 30 and I feel like I ’ve been lonely my entire life.
It ’s not just “ I don't have plans this weekend ” lonely, it ’s this deep, constant \textbf{emptiness} that never really goes away.
I ’m so tired of living like this.
I wouldn't act on those thoughts because I have a family and kids who need me, but it feels like I ’m just … enduring life rather than living it.
Work doesn't help.
I can't seem to find a job that gives me real human interaction.
Even when I ’m technically “ with ” \textbf{people}, like working with clients, it feels like I ’m just performing a \textbf{role}.
It ’s all surface-level, \textbf{scripts} and small talk, nothing that fills that need for actual connection.
I was recently diagnosed as autistic, and it explains so much, but it also makes me feel kind of hopeless.
My whole life of struggling to make friends, to find \textbf{people} on my intellectual level, to feel understood—it suddenly makes sense, but it doesn't fix anything.
I still feel like I make no real difference in the world.
Like if I disappeared, everything would just keep going the same.
What scares me most is my kids.
If I can't form real connections, how am I supposed to teach them how to?
I don't want them to grow up feeling this same \textbf{emptiness}.
I know I ’m not alone in feeling lonely.
I see so many \textbf{people} saying they feel this way too.
But how does knowing that actually help when I still go to bed every night feeling like this?

% matched lemmas: emptiness, people, role, script
\end{textsample}
