\begin{textsample}{NEG Dim 2 – generic\_gpt – Score -3.00 – generic\_gpt/t1523\_gpt.txt}  \label{ex:f2_neg_014}
I don't really know how to explain this without sounding dramatic, but lately it feels like my life is happening behind a pane of \textbf{glass}.
From the outside, things look “ fine. ” I have a job, I respond to messages, I show up when I ’m supposed to. \textbf{People} would probably describe me as quiet but “ nice. ” I ’m not completely isolated.
I have \textbf{acquaintances}, a group chat that occasionally pings, coworkers who ask how my weekend was.
But it all feels so thin, like I ’m playing a \textbf{role} and everyone else is actually living.
What gets to me most is the lack of emotional closeness.
I don't have that person I can text when something small but important happens.
I don't have anyone who knows the full, messy version of me. \textbf{Conversations} stay on the surface : work, memes, “ how are you? ” followed by the \textbf{scripted} “ I ’m good, you? ” I can't remember the last time someone asked me how I really was and actually wanted the honest answer.
I ’ve tried to put myself out there.
I go to meetups, I reply in group chats, I ask \textbf{people} questions, I listen.
But I always end up feeling like the extra person in a group photo, the one who could be cropped out and nothing would change. \textbf{People} seem to already have their circles, their “ best friends, ” their shared histories.
I ’m the convenient add-on, never the person someone thinks of first.
What scares me is how normalized this is becoming for me.
I ’m getting used to eating alone, going places alone, having no one to debrief the day with.
I tell myself I prefer it that way because it hurts less than admitting I don't know how to bridge this \textbf{gap}.
There ’s this constant ache of wanting to be known and the equally strong fear that if I actually showed who I am, it would just confirm that I ’m forgettable or too much or not enough.
So I stay in this weird limbo : present but not really seen, surrounded by \textbf{people} but still somehow completely on my own.

% matched lemmas: acquaintance, conversation, gap, glass, people, role, script
\end{textsample}
