\begin{textsample}{NEG Dim 2 – generic\_gpt – Score -3.00 – generic\_gpt/t1634\_gpt.txt}  \label{ex:f2_neg_011}
I don't really know how to explain this without sounding dramatic, but lately it feels like my life is just … background \textbf{noise}.
I have \textbf{people} around me, technically.
Coworkers, some old friends I text every now and then, family chats that light up my phone.
But when I actually look at it, most of it is surface-level.
Memes, logistics, “ how ’s work? ” and “ busy, you? ” on repeat.
No one really asks how I am in a way that suggests they want an honest answer, and I ’m not sure I ’d know how to give one if they did.
I go through whole days where I don't say anything that feels like “ me. ” It ’s all autopilot small talk.
When I get home, it ’s just this heavy silence, like the air gets thicker.
I put on YouTube or a podcast just to have voices in the room, but it doesn't fix the feeling that I could vanish and it would mostly just be an inconvenience to a few \textbf{people} ’s schedules.
I ’ve tried reaching out more.
I ’ll message someone and stare at “ online ” next to their name while they don't reply, then watch them post on social media.
That weird \textbf{mix} of being invisible and still somehow too much.
It stings more than I want to admit.
What scares me is how normal this is starting to feel.
The weekends blur together : \textbf{errands}, scrolling, pretending I ’m fine.
I don't even know what I ’d talk about if someone genuinely wanted to know me.
I ’ve spent so long being “ okay ” for everyone else that I ’m not sure there ’s anything underneath it anymore.
I ’m not even sure what I ’m hoping for by writing this.
Maybe just to put it somewhere outside my own head for once.

% matched lemmas: errand, mix, noise, people
\end{textsample}
