\begin{textsample}{NEG Dim 2 – generic\_gpt – Score -4.00 – generic\_gpt/t2370\_gpt.txt}  \label{ex:f2_neg_001}
I ’ve been feeling this weird \textbf{mix} of invisible and “ too much ” at the same time, and I don't really know where to put it, so I ’m putting it here.
Most days I go through the motions : work, \textbf{errands}, scrolling, sleep.
I talk to \textbf{people}, but it all feels like background \textbf{noise}.
Coworkers, small talk, “ how was your weekend? ” — I answer, they answer, but it ’s like we ’re all actors reading from a \textbf{script}.
When I get home and close the door, it hits me how quiet it actually is.
I ’m not completely isolated.
I have \textbf{acquaintances}, a couple of old friends I text sometimes, family group chats.
But there ’s no one I feel like I can message and say, “ I feel really lonely right now, can you just stay on call with me? ” without worrying I ’m being needy or weird.
So I keep it to myself, and the distance just grows.
I keep thinking that if I were more interesting, more funny, more something, I ’d naturally fit into a group.
Instead, I feel like the extra piece in a puzzle set—technically fine, but not belonging anywhere.
I overthink every interaction : Did I talk too much?
Not enough?
Did I sound boring?
So I retreat, then feel lonelier, then get rusty at social stuff, which makes me more anxious next time.
It ’s like watching life happen through a \textbf{window}.
I can see everyone else laughing, dating, making plans, but there ’s this \textbf{glass} between me and all of it, and I can't figure out how to open it.

% matched lemmas: acquaintance, errand, glass, mix, noise, people, script, window
\end{textsample}
