\begin{textsample}{NEG Dim 3 – summary\_guided\_gpt – Score -4.00 – summary\_guided\_gpt/t2439\_gpt.txt}  \label{ex:f3_neg_022}
I \textbf{feel} lonelier now than I ever have in my life.
In 2024 I slowly drifted away from the people I used to call friends.
At first it was just less talking, less hanging out, then suddenly it was basically nothing.
In 2025 it got even worse.
I ’m almost completely disconnected from people now.
The weird part is that even when I did have a friend living nearby, I still \textbf{felt} lonely.
We barely had any direct interaction, and I always \textbf{felt} like I was on the outside looking in, like I was never really part of anything.
Most of my “ social life ” became online, and even that \textbf{felt} \textbf{shallow}.
To \textbf{cope} with feeling excluded and alone, I started drinking a lot.
It was the only thing that made the \textbf{emptiness} quiet down for a while.
Later I moved on to opioids.
They made the loneliness \textbf{feel} distant, like it was happening to someone else.
I eventually quit drinking, and I honestly miss it more than I want to admit.
I ’m using way fewer opioids now too, but without all that, everything \textbf{feels} raw and \textbf{exposed}.
I ’m sober and I ’m not happy about it.
I \textbf{feel} like I gave up the only thing that made life bearable, and I didn't get anything in return.
On \textbf{top} of all this, I \textbf{feel} like my biggest personal dream is slipping away.
It always \textbf{felt} like something blocked me every time I tried to move toward it.
Now it \textbf{feels} like it ’s fading for good, like it might never happen.
I ’m supposed to be thinking about university, but I \textbf{feel} lost and completely unprepared.
I don't know what I ’m doing or where I ’m going.
I just \textbf{feel} empty, \textbf{disconnected}, and stuck, and I don't know how to change any of it.

% matched lemmas: cope, disconnected, emptiness, expose, feel, shallow, top
\end{textsample}
