\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -6.00 – generic\_gpt/t744\_gpt.txt}  \label{ex:f3_neg_002}
I ’ve been \textbf{feeling} this weird \textbf{mix} of \textbf{invisible} and too \textbf{exposed} at the same time.
On paper, I ’m not “ alone. ” I have coworkers, a few old friends I text every now and then, family chats that light up my phone.
But none of it \textbf{feels} like it really touches me.
It ’s like I ’m standing behind glass watching my own life happen.
I go through the motions : work, gym, scrolling, sleep.
I laugh at the right times, make small talk, answer “ I ’m good, you? ” without thinking.
Then I get home, close the door, and it hits me how quiet everything is.
Not just the room—my life.
There ’s no one who really expects me, no one I can send a random thought to without overthinking if I ’m being annoying.
What bothers me most is how replaceable I \textbf{feel}.
If I stopped showing up, I think people would notice for a bit, then just … adjust.
I don't \textbf{feel} like I ’m anyone ’s first choice, or even second.
More like background noise.
I ’ve tried joining clubs, going to events, talking more.
It always \textbf{feels} \textbf{shallow}, like I ’m auditioning for a \textbf{role} I never get.
I leave \textbf{feeling} more drained and more aware of how \textbf{disconnected} I am.
I don't even know what I ’m looking for exactly.
Just something that makes me \textbf{feel} like I actually exist to someone, beyond a name in a group chat or a face at a desk.

% matched lemmas: disconnected, expose, feel, invisible, mix, role, shallow
\end{textsample}
