\begin{textsample}{NEG Dim 3 – summary\_guided\_gpt – Score -3.00 – summary\_guided\_gpt/t631\_gpt.txt}  \label{ex:f3_neg_029}
It ’s 1 AM and I ’m sitting alone in this forest, and it just \textbf{feels} like the most accurate reflection of my inner world right now : dark, quiet, empty, and sort of indifferent to whether I ’m here or not.
I keep thinking about how other people seem to be out there actually living.
Laughing with friends, building families, forming these deep connections that give their lives shape and meaning.
Meanwhile I ’m here, \textbf{feeling} like a ghost who somehow still has to show up to work, pay bills, and pretend I ’m fine.
I don't know if anyone really sees me, or if they just see the surface-level \textbf{version} I drag around to keep things functioning.
Life used to \textbf{feel} brighter.
Back in school and college there was this sense of possibility, of shared experiences, of being part of something.
I remember feeling hopeful, like the future was this big open space I could grow into.
Somewhere along the way, that feeling just…evaporated.
I left a big tech job to build my own thing, thinking it would give me freedom and purpose.
Instead, I ’ve become a slave to achievement, to metrics, to the next milestone.
I ’ve traded whatever joy and sense of self I had for this constant pressure to “ succeed. ” On paper, I ’m stable.
In reality, I \textbf{feel} hollow.
Materially okay, emotionally bankrupt.
Sometimes I walk through cemeteries and it hits me how brief and pointless this all seems.
Rows of names, dates, and that tiny dash in between.
That ’s it.
I wonder what they \textbf{worried} about, what they sacrificed, who they loved, and if they died \textbf{feeling} as unseen and unheard as I do now.
I don't really know why I ’m writing this except that I ’m alone out here and the weight of all of this \textbf{feels} too heavy to carry in silence.
Maybe putting it into words will carve out a tiny bit of space inside this \textbf{emptiness}.
Maybe it won't.
But at least, for a moment, it \textbf{feels} like I ’m not completely \textbf{invisible}.

% matched lemmas: emptiness, feel, invisible, version, worry
\end{textsample}
