\begin{textsample}{NEG Dim 3 – summary\_guided\_gpt – Score -4.00 – summary\_guided\_gpt/t2273\_gpt.txt}  \label{ex:f3_neg_021}
I don't even know how to say this without sounding like a monster, but I ’m just so tired of my own life.
I ’ve been married for 25 years.
My wife is chronically ill with multiple serious conditions.
All four of our kids have special needs, and our youngest is nonverbal autistic.
For the last 16 years I ’ve been the only one working.
For the last five or so, I ’ve also been doing about 90 % of the cooking and cleaning on \textbf{top} of that.
It \textbf{feels} like my “ \textbf{role} ” at home is to take care of everything, never disagree, never complain, and never ask my kids to do anything.
If I ask for help, I ’m told I ’m asking too much.
If I ask for really small things, like my wife getting up a little earlier so we can share breakfast or a cup of coffee before I go to work, it turns into a problem.
I ’m made to \textbf{feel} like even that is unreasonable.
I \textbf{feel} like a glorified servant in my own house.
The only place I \textbf{feel} respected or valued is at work, which is kind of messed up because work \textbf{feels} like a vacation compared to being at home.
At work people listen to me, they say thank you, they treat me like I matter.
At home I just \textbf{feel} … \textbf{invisible} unless something needs to be done.
I ’m not depressed or suicidal.
I ’m not on the \textbf{edge} of doing something drastic.
I ’m just \textbf{exhausted}.
I ’m full of resentment I don't know what to do with.
I \textbf{feel} completely silenced, like I ’m not allowed to have needs or opinions because everyone else ’s needs are so big and obvious.
I work out a few times a week and I smoke weed after work to \textbf{cope} and stay emotionally stable.
It helps take the \textbf{edge} off, but I wish I could \textbf{feel} happy or even just content without needing that.
I wish home didn't \textbf{feel} like a place I ’m constantly bracing myself for.
I don't even know what I ’m looking for by posting this.
I just needed to say it somewhere.

% matched lemmas: cope, edge, exhaust, feel, invisible, role, top
\end{textsample}
