\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -6.00 – generic\_gpt/t2480\_gpt.txt}  \label{ex:f3_neg_003}
I ’ve been \textbf{feeling} this weird \textbf{mix} of \textbf{invisible} and too \textbf{exposed} at the same time.
On paper, I ’m “ fine ” — job, small apartment, a couple of acquaintances I sometimes see.
But I don't \textbf{feel} like I actually exist in anyone ’s mind when I ’m not physically there.
No one texts just to check in.
If I don't reach out, days go by in complete silence except for work emails and random notifications.
When I do see people, I \textbf{feel} like I ’m playing a \textbf{role} : the “ okay ” \textbf{version} of myself who can make small talk and laugh at the right spots.
Meanwhile there ’s this heavy, dull ache underneath, like I ’m watching my own life from the outside.
I leave gatherings \textbf{feeling} more alone than before, because it just highlights how \textbf{shallow} most of my connections are.
I ’ve tried joining clubs, going to events, chatting online.
It ’s like there ’s a glass wall — I can see everyone, hear them, but I can't actually get through to the part where you become important to each other.
I \textbf{worry} that I ’m just fundamentally forgettable.
What scares me is how normal this has started to \textbf{feel}.
Like this is just how my life is now : presentable on the surface, hollow underneath, and no one really noticing the difference.

% matched lemmas: expose, feel, invisible, mix, role, shallow, version, worry
\end{textsample}
