\begin{textsample}{NEG Dim 3 – summary\_guided\_gpt – Score -3.00 – summary\_guided\_gpt/t2564\_gpt.txt}  \label{ex:f3_neg_026}
I ’m 60, and only about eight months ago did I finally let myself say the words “ I ’m transgender ” out loud in my own head.
I ’ve wanted to be a woman for more than a decade, but I kept it buried under layers of denial, religion, and duty.
I grew up in a strict Catholic family and then spent 44 years in the Army.
That ’s a lifetime of being immersed in “ be a man, be tough, don't show weakness. ” I got very good at playing the \textbf{role} everyone expected of me.
I ’ve been married for 30 years and we have three adult sons.
From the outside, I probably look like the stereotypical older, conservative father and husband.
Inside, it ’s a different story.
I ’m transfeminine, and I don't see a realistic way to ever come out.
My wife has serious physical and mental health issues.
I love her and I ’m \textbf{terrified} of what my coming out would do to her – I \textbf{worry} about divorce, or even something worse happening to her if the shock and stress were too much.
It \textbf{feels} like the cost to her would be unbearable, and I can't bring myself to risk it.
I ’m almost certain my wife, my mother, and most of my siblings wouldn't accept me as trans.
Some of my sons might, and most of my nieces and nephews probably would – one of them is transmasc, so I know there ’s some understanding there.
But the core people who have defined my life for decades?
I don't think they ’d see me as anything but a disappointment or a stranger.
So I ’ve basically resigned myself to living out the rest of my life as this persona I ’ve constructed.
The “ real ” me will stay hidden, untouched, unknown.
I \textbf{feel} like I ’m locked in a room inside my own life, watching someone else live it.
On the outside I function, but internally I \textbf{feel} profoundly alone, like there ’s this essential part of me that will never be seen or held by anyone.
I don't have a solution.
I don't really expect one.
Writing this is just a small attempt to let that hidden part of me speak for a moment, to push back against the feeling that I ’m completely alone in here.
I ’m not sure it will help, but it \textbf{felt} like I had to try.

% matched lemmas: feel, role, terrify, worry
\end{textsample}
