\begin{textsample}{NEG Dim 3 – human – Score -2.00 – human/t1128\_human.txt}  \label{ex:f3_neg_034}
I 'm a pretty cool guy, atleast thats what i think.
I cannot exactly say that i dont have friends and all, i get along with people just fine and I 've noticed a lot of people \textbf{feel} attracted towards me, like you know they want to talk to me and all.
But the thing is, all of the people i know, my"friends","family"whatever, everyone seems to maintain a certain boundary line with me.
It \textbf{feels} less like having people of my own, and more like people watching me afar.
I dont know how to express this feeeling, but i \textbf{feel} like people are just standing it a round circle and im doing tricks in the middle for their entertainment.
For example, nobody wished me on my 19th birthday.
That was a big blow to my face bacause it made me realise how less important to these"friends"i am.
I 've started to think that i was nothing more that some crowd.
As ikept growing up, i kept seeing people go further and further from me.
It 's like, they wont leave, but stand at a distance and cheer for me.
Honestly all I 've wanted in this life is a brother.
A friend. who would come chill on my room like he owns it.
Whom I wouldn't have to maintain distance from or \textbf{worry} about"what he will think"because i know he wont judge me.
I can run to at 3 am at midnight if i need to.
But i dont know, nobody seems to step up for that \textbf{role}.
So yeah, here i am, with a hell bunch of"friends"around me and i still \textbf{feel} alone.
I dont know what went wrong.
I dont know if I 'm overthinking.
And sorry if this post is too long, tbh im just venting here cus apperently, i dont have anyone to vent to.

% matched lemmas: feel, role, worry
\end{textsample}
