\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -1.00 – generic\_gpt/t1218\_gpt.txt}  \label{ex:f3_neg_017}
I don't really know how to explain this without sounding dramatic, but lately it feels like I ’m disappearing in slow motion.
On paper, I ’m “ fine. ” I have a job, I answer emails, I show up to meetings, I say “ yeah, weekend was good, you? ” and people nod and move on.
I \textbf{scroll} group chats, occasionally react with a thumbs-up, but I can't remember the last time I actually felt connected to anyone.
It ’s like I ’m always slightly behind a pane of glass watching everyone else live in real time.
I used to have friends I ’d message just to share some random thought.
Now I stare at the chat box, type something, delete it, and convince myself they ’re too busy or I ’d just be annoying.
Days go by and the only \textbf{notifications} I get are spam and work stuff.
I tell myself I ’m “ introverted ” or “ independent, ” but the silence feels less like peace and more like neglect.
The worst part is how it messes with how I see myself.
When no one really knows you beyond small talk, you start wondering if there ’s even anything worth knowing.
I ’ve become weirdly self-conscious about everything—my voice, my laugh, the way I stand—like I ’m rehearsing for an audience that never actually shows up.
I don't even know what I ’m hoping for posting this.
Maybe just to put into words that I exist, that I ’m here, even if it feels like no one would really notice if I wasn't.

% matched lemmas: notification, scroll
\end{textsample}
