\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -7.00 – generic\_gpt/t1217\_gpt.txt}  \label{ex:f3_neg_001}
I ’ve been \textbf{feeling} this strange \textbf{mix} of \textbf{invisible} and \textbf{exposed} lately, like I ’m walking around with “ alone ” written on my forehead but no one actually sees it.
On paper, I ’m not isolated.
I have coworkers, a couple of old friends I text sometimes, family I talk to in group chats.
But everything \textbf{feels} surface-level, like I ’m playing a \textbf{role} in conversations instead of actually being there.
I can be in a room full of people and still \textbf{feel} like a ghost hovering around the \textbf{edges}.
What hits hardest is the lack of being known.
No one really knows what my days are like, what I ’m afraid of, what I ’m hoping for.
I don't even know who I ’d call if something genuinely good or genuinely bad happened.
I ’d probably just sit with it alone, scroll my phone, maybe type something out and delete it.
I ’ve tried to “ put myself out there ” like everyone says—joined a couple of online communities, tried small talk at work, went to a meetup once.
I always end up \textbf{feeling} like an outsider, like everyone else got a manual on how to connect that I somehow missed.
The worst part is how it starts to \textbf{feel} like a personality trait instead of a situation.
Like “ lonely ” is just who I am now.
It ’s \textbf{exhausting} pretending it doesn't bother me, then coming home to the quiet and realizing how loud the \textbf{emptiness} actually is.

% matched lemmas: edge, emptiness, exhaust, expose, feel, invisible, mix, role
\end{textsample}
