\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -2.00 – generic\_gpt/t1756\_gpt.txt}  \label{ex:f3_neg_006}
I don't really know how to explain this without sounding dramatic, but lately it feels like I ’m living next to my own life instead of in it.
On paper, I ’m “ fine. ” I have a job, I reply to messages, I show up when I ’m supposed to.
People would probably describe me as “ quiet but nice. ” But there ’s this constant sense that I ’m just orbiting around everyone else, like I ’m close enough to see them but too far to actually be part of anything.
The weird thing is I ’m not completely isolated.
I have \textbf{acquaintances}, coworkers, a couple of people I can text.
But it all feels shallow.
Conversations stay on the surface : work, \textbf{weather}, memes.
When I try to say something real, I feel like I ’m making things awkward, so I pull back and go back to nodding and smiling.
Nights are the worst.
I come home, eat, \textbf{scroll}, maybe watch something, and it ’s just this heavy silence.
I keep my \textbf{phone} nearby like it ’s a lifeline, but it almost never lights up unless it ’s a \textbf{notification} from some app.
I tell myself I should reach out first, but I get stuck in this loop of “ they ’re busy ” and “ they don't actually want to talk to me. ” What scares me most is how normal this is starting to feel.
Like I ’m slowly getting used to being emotionally invisible.
I can't tell if I ’m withdrawing because I ’m lonely, or lonely because I keep withdrawing.
It ’s just this dull, constant ache I carry around, and I don't really know what to do with it anymore.

% matched lemmas: acquaintance, notification, phone, scroll, weather
\end{textsample}
