\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -1.00 – generic\_gpt/t1230\_gpt.txt}  \label{ex:f3_neg_018}
I don't really know how to explain this without sounding dramatic, but lately it feels like I ’ve just slipped out of everyone ’s peripheral vision.
My \textbf{phone} barely buzzes unless it ’s a \textbf{notification} from some app.
Group chats that I used to be part of are still active, but I ’m more like a silent observer now.
I ’ll type something, stare at it, and then delete it because I convince myself no one ’s waiting to hear from me anyway.
When I do send something, it usually gets buried between memes and other conversations, and I feel stupid for even trying.
In person isn't much better.
I go to work, talk about tasks and deadlines, laugh at the right times, but it ’s all surface-level.
I ’ve become that “ reliable coworker, ” but not someone anyone actually knows.
People will say things like, “ We should hang out sometime, ” and it never actually happens.
I don't even know if they mean it.
The weird thing is I ’m not completely isolated.
I see people.
I interact.
But I feel like I ’m behind glass.
Like I ’m watching life happen instead of being part of it.
I go home, make dinner for one, and then just…exist. \textbf{Scroll}, watch something, lie in bed too long.
I don't even have some big trauma story to justify why I feel this empty.
It ’s just this dull, ongoing ache.
I keep thinking that if I disappeared from social media or stopped showing up places, it would take a long time for anyone to notice.
And even longer for anyone to ask why.

% matched lemmas: notification, phone, scroll
\end{textsample}
