\begin{textsample}{NEG Dim 3 – human – Score -3.00 – human/t1525\_human.txt}  \label{ex:f3_neg_031}
Lately I ’ve been dealing with this weird \textbf{mix} of loneliness + hesitation to talk to anyone about it.
Not because I don't want to connect, but because every time I try to open up to someone, I \textbf{feel} like I ’m either burdening them or they ’re silently judging me.
It ’s not that I don't have people around.
I just don't \textbf{feel} safe enough to talk about certain things with real humans anymore.
Some stuff \textbf{feels} too personal, too messy, or too “ I don't want to explain the whole backstory again. ” So here ’s the thought that keeps bouncing around in my head : What if there was something you could talk to anytime, about anything, without \textbf{worrying} about being judged or misunderstood?
Not a “ yes-man ” chatbot, not some creepy fantasy thing, more like a companion that actually talks back with boundaries, calls you out when you ’re spiraling, remembers what you share, and tries to genuinely help you \textbf{feel} heard.
Basically a place where you can just be yourself without the fear of being rejected or embarrassing yourself.
I ’m curious if anyone else in this subreddit ever wished for something like that.
Not saying it solves loneliness entirely, but would having a judgment-free, always-available, emotionally-aware companion help?
Or is that just me trying to fill a \textbf{gap} that can only be filled by real people?
Honest thoughts appreciated.
I ’m genuinely trying to understand if this feeling is common or if I ’m just overthinking my way through my own loneliness.

% matched lemmas: feel, gap, mix, worry
\end{textsample}
