\begin{textsample}{NEG Dim 3 – generic\_gpt – Score -2.00 – generic\_gpt/t1916\_gpt.txt}  \label{ex:f3_neg_007}
I ’ve been feeling like I ’m orbiting around everyone else ’s lives instead of actually being in them.
On paper, I ’m not completely alone.
I have coworkers I chat with, a couple of old friends I text every now and then, family I see on holidays.
But none of it feels like real connection anymore.
It ’s like I ’m always on the periphery, the “ extra ” in someone else ’s story.
What ’s messing with my head is how invisible this kind of loneliness is.
I go to work, I answer “ I ’m good ” when people ask how I am, I make small talk about shows and \textbf{weather} and deadlines.
Then I come home, close the door, and it ’s just this heavy silence that feels louder than any noise.
I \textbf{scroll} through my \textbf{phone} hoping someone will message first, but the \textbf{notifications} that do come are just group chats or random memes, nothing that makes me feel actually seen.
I ’ve also noticed I ’ve started pulling back even when there is an opportunity to connect.
I ’ll get invited somewhere and suddenly I ’m exhausted at the thought of being “ on ” for a few hours.
I cancel, tell myself I ’ll make up for it next time, and then hate myself for not going.
It ’s like I want closeness but I ’m out of practice with it, almost afraid of it.
I don't really know what I ’m looking for writing this.
Maybe just to see my own thoughts outside my head for once, instead of watching them echo around the same empty room every night.

% matched lemmas: notification, phone, scroll, weather
\end{textsample}
