\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 7.00 – summary\_guided\_gpt/t1439\_gpt.txt}  \label{ex:f3_pos_023}
I ’m 21 and for as long as I can remember I ’ve had this feeling that I don't want to live past 30.
It used to be more of a vague thought in the background, but since my ex died it ’s become so much stronger and scarier.
I still thought of him as my boyfriend.
I \textbf{loved} him so much, even though our \textbf{relationship} really messed me up and left me with a \textbf{lot} of emotional damage and self-esteem \textbf{issues} that I still carry.
His family was really supportive at first, but now they ’re upset with me and somehow I ’ve become this person in the middle of their conflicts.
They come to me to vent or expect me to help fix \textbf{things} between them, but no one seems to think, “ Maybe I should ask how she ’s doing. ” It feels like I ’m just here to absorb everyone else ’s \textbf{pain} and drama.
My \textbf{friends} don't really reach out unless I text first.
If I stop talking, everything just goes quiet.
I don't have a car, a job, money, or a place of my own.
I feel like I have nothing going for me and no real future to look forward to.
On \textbf{top} of that, my body feels like it ’s falling apart.
I ’m exhausted all the \textbf{time}, my physical \textbf{health} is a mess, and emotionally I ’m all over the place.
I have BPD and sometimes I can manage it okay, but other \textbf{times} it completely runs my life.
My \textbf{relationship} with my family is strained too, so I don't really feel like I have a safe place anywhere.
I can't eat properly, I can't sleep, I can't relax or enjoy the \textbf{things} I used to like.
I ’m trying to cope, but I keep wondering what the point of any of this is.
I feel so alone, and it honestly scares me how alone I am.

% matched lemmas: friend, health, issue, lot, love, pain, relationship, thing, time, top
\end{textsample}
