\begin{textsample}{POS Dim 3 – generic\_gpt – Score 3.00 – generic\_gpt/t732\_gpt.txt}  \label{ex:f3_pos_034}
I ’ve been feeling like I ’m slowly disappearing from everyone ’s lives, including my own.
I have people around me, technically.
Coworkers, a few old \textbf{friends} I text now and then, family chats that light up my phone.
But I feel like a background character in all of it.
Conversations stay on the surface.
I crack jokes, ask questions, listen to their \textbf{problems}, but when it ’s my turn to be honest, I freeze up or change the subject.
I don't even know how to talk about what ’s going on in my head without feeling like I ’m being “ too much. ” What ’s weird is that I actually crave connection so badly it hurts, but at the same \textbf{time}, I ’m exhausted by even the \textbf{idea} of socializing.
I ’ll turn down invitations and then feel lonely as soon as I ’m alone.
I scroll through social media and see people hanging out, building memories, having “ their people, ” and I feel like I missed some invisible sign-up sheet \textbf{years} ago.
I also feel like I don't have a “ role ” in anyone ’s life.
I ’m not someone ’s go-to person.
If I disappeared, people would notice eventually, but I don't think it would really change their day-to-day.
That thought keeps looping in my mind at night when everything is quiet.
I don't know how to fix this.
I don't even know where to start.
I ’m tired of pretending I ’m fine when I ’m not, but I ’m also scared that if I show how lonely I really feel, people will pull away even more.
So I just keep going through the motions and hoping something shifts, but most days it all feels the same.

% matched lemmas: friend, idea, problem, time, year
\end{textsample}
