\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t2197\_human.txt}  \label{ex:f3_pos_014}
Recently, I became more and more confident on the \textbf{idea} that I might have \textbf{depression}, but I never got diagnosed.
Among the questions, I answered a 10/10 for how lonely I felt lately.
It is not a \textbf{problem} of being by myself, I do enjoy my own \textbf{time}.
But as someone that has never dated, I am starting to feel more and more as an impostor.
Everyone talks about their \textbf{relationships}, or even just situationships, how do you relate when you never had something like that?
I am starting to feel guilty, ashamed of my desires, for my need for intimacy.
I crave the touch of another human, but also the connection, it ’s gotten to the point that I can't do anything to satisfy myself, because I end up crying.
Turns out the people I speak most comfortably with are men around 4 to 20 \textbf{years} older than me ( 20f ), it ’s concerning.
I can't stop thinking, why?
What is the reason that I only seem to be glad talking to them?
I have no daddy \textbf{issues}, and no they are not people taking advantage of me, they are professors or colleagues.
With my best \textbf{friend}, we often joke about how much of a loser I would be if I were a man because of my interests, but to be honest, is there really any difference?
I am still a loser even if I am a woman.
The last manga I read was Inside Mari by Shuzo Oshimi, and I related so deeply i had to take some \textbf{time} to think.
Today I saw someone that used to be my \textbf{friend} back in middle school, I didn't reach out, neither did they.

% matched lemmas: depression, friend, idea, issue, problem, relationship, time, year
\end{textsample}
