\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t810\_human.txt}  \label{ex:f3_pos_008}
( This is translated with GPT because I don't speak English very well ) I ’m ( 20M ) and today I feel lonelier than usual.
Today is my birthday and it feels strange.
Only one person congratulated me, and none of my family has.
On \textbf{top} of that, I ’ve been sick with the flu for 4 days, so I don't even have the energy to do anything.
I ’ve lived a lonely life all these \textbf{years}, and it ’s something I ’ve gotten used to.
About 3 \textbf{years} ago, I met a girl on Discord in a community a \textbf{friend} created.
We were \textbf{friends} for about a \textbf{year}, and then we became long-distance partners.
It was a beautiful \textbf{relationship} that lasted a \textbf{year}.
But the \textbf{relationship} ended on her side, while I still \textbf{loved} her and wanted to continue, since the \textbf{problem} wasn't between us but something external.
The breakup happened during the first week of November ( right when our anniversary was coming up ).
It hit me really hard because with her I didn't need anyone else to socialize with.
I had \textbf{friends}, with whom I ’m still in touch, but I haven't had anyone else to socialize with at the level I did with her. ( In my family, I was raised in a \textbf{way} where we don't usually talk about our feelings. ) With her, I could tell her about my day, what I did, what I wanted to do.
She told me about her life, about her dreams, which also became mine, because before I met her I was totally lost, without dreams or goals, and she made me dream.
It ’s been about 10 months since the breakup, and honestly the only \textbf{thing} I ’ve missed is having that \textbf{kind} of connection again.
I don't miss her ; I miss what I could do with her and the \textbf{fact} that I could open up emotionally to someone else.
Also, because of how my family treated me during childhood, it ’s really hard for me to open up emotionally to other people and be sociable.
Sorry if this isn't well structured, but it ’s just what I ’m thinking in the moment.

% matched lemmas: fact, friend, kind, love, problem, relationship, thing, top, way, year
\end{textsample}
