\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 6.00 – summary\_guided\_gpt/t1371\_gpt.txt}  \label{ex:f3_pos_027}
I feel like I ’m living this weird split life where, on paper, \textbf{things} look almost ideal, and yet I ’m crushed by one missing piece.
I ’m in my 30s now.
I somehow managed to buy a house even though I don't make much.
I have a handful of long-term \textbf{friends} who are genuinely good people.
My job is stable and really aligned with my values, which I know is rare.
I ’ve also got some significant \textbf{health} \textbf{problems}, but I ’m very motivated about managing them and I ’m doing the best I can there.
The \textbf{problem} is that I don't have a romantic partner, and that emptiness feels like it eclipses everything else.
Love has always been a huge \textbf{thing} for me.
My first \textbf{love} was when I was 12, and it was intense in a \textbf{way} that still echoes 20 \textbf{years} later.
It ’s like that experience hard-wired me to need that \textbf{kind} of connection.
I don't mean “ sort of want it, ” I mean it feels like a core emotional need that just never stops aching.
I ’ve been in therapy.
I use DBT skills.
I spend \textbf{time} with my \textbf{friends}, I do \textbf{things} I enjoy, I try to build a meaningful life in every \textbf{way} I can.
My therapist and I have gone over and over whether there ’s some other imbalance or \textbf{issue} I ’m missing, and we keep coming back to the same conclusion : this need for romantic companionship is just extremely strong for me.
And nothing I do seems to touch the \textbf{depression} that comes from that absence.
I don't seem able to “ fill the \textbf{gap} ” with other forms of connection, no matter how hard I try or how much I intellectually understand that I ’m not supposed to rely on one \textbf{thing} for happiness.
I ’m feeling desperate and stuck.
Has anyone else been here and found anything that actually helped?
Any perspectives or approaches I might not have tried yet?

% matched lemmas: depression, friend, gap, health, issue, kind, love, problem, thing, time, way, year
\end{textsample}
