\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 6.00 – summary\_guided\_gpt/t452\_gpt.txt}  \label{ex:f3_pos_028}
I ’m 20 and I feel like my life has been on pause for as long as I can remember.
Everyone my age seems to be out there actually living – studying, going out with their \textbf{friends}, going on trips, dating, having all these “ normal ” experiences – and I ’m just … here.
Stuck.
I have chronic illnesses on \textbf{top} of \textbf{depression} and \textbf{anxiety}, and I ’m sick a \textbf{lot}.
Hospital stays are such a regular part of my life that they almost feel more “ normal ” than anything else.
Because of all this, I never really got to have a \textbf{friend} group, or parties, or any \textbf{kind} of romantic \textbf{relationship}.
All the typical teen/young adult stuff just passed me by.
Social media makes it worse.
I see ex-classmates and ex-friends posting their memories, their nights out, their \textbf{relationships}, and it feels like I ’m watching from behind glass.
It hurts more than I can explain.
It just feels so unfair.
I scroll and it ’s like I ’m being reminded over and over that I have “ absolutely no life, ” that I ’m just here to suffer while everyone else gets to actually live.
This has been my reality since I was a kid, so it ’s not even like I remember a \textbf{time} when \textbf{things} were truly different.
I feel empty and left behind, like I ’m \textbf{years} behind everyone else with no \textbf{way} to catch up.
I don't even know what to do anymore.
Is there anything I can genuinely do to escape this?
To stop feeling like my existence is just hospitals, illness, and watching other people ’s lives from the outside?

% matched lemmas: anxiety, depression, friend, kind, lot, relationship, thing, time, top, way, year
\end{textsample}
