\begin{textsample}{POS Dim 3 – generic\_gpt – Score 2.00 – generic\_gpt/t662\_gpt.txt}  \label{ex:f3_pos_040}
I ’ve been feeling this weird combination of invisible and exposed lately.
On paper, I ’m not “ alone. ” I have coworkers I chat with, family I text, a couple of old \textbf{friends} I send memes to.
But everything feels like it ’s happening behind glass.
I can see the motions of connection, but I don't really feel touched by any of it.
What gets me is how ordinary everything looks from the outside.
I go to work, I respond to messages, I say “ yeah, I ’m good, just busy. ” No one questions it.
Part of me actually prefers that, because I have no \textbf{idea} how to explain this \textbf{kind} of emptiness without sounding dramatic or ungrateful.
I think what I miss is feeling known.
Not just “ how ’s work? ” or “ seen this show? ” but the \textbf{kind} of familiarity where someone notices when your voice sounds off, or remembers the small \textbf{things} you said weeks ago.
I can't remember the last \textbf{time} I felt that from anyone, and I ’m starting to forget what it ’s like.
I also know I ’m part of the \textbf{problem}.
I hold back.
I overthink every message.
I convince myself I ’m annoying, or that people are only being polite.
So I retreat, then feel more disconnected, then retreat more.
It ’s like I ’m building my own cage and then complaining about the bars.
I don't even know what I ’m hoping for by writing this.
Maybe just to put it somewhere outside my own head for once.

% matched lemmas: friend, idea, kind, problem, thing, time
\end{textsample}
