\begin{textsample}{POS Dim 3 – human – Score 7.00 – human/t323\_human.txt}  \label{ex:f3_pos_003}
I am 20 \textbf{years} old and I have been depressed for the last 3–4 \textbf{years}.
Even after coming out of \textbf{depression}, it has left a big impact on me and has made my physical \textbf{health} worse.
I don't know whether I am still depressed or not, but I still get negative thoughts sometimes, and I have almost lost my emotions or feelings.
Talking about my recent \textbf{situation}, I ’m really not feeling good.
I really need someone to understand me—someone who can take care of me or at least care about what disappoints me.
I have literally lacked \textbf{support}, \textbf{love}, and care from my family.
I was ditched by my best \textbf{friends}, and slowly I lost even having a good \textbf{friend}.
When I fell into my \textbf{depression} phase, my \textbf{friends} stepped away from me at my lowest point.
After \textbf{friends} and family, I have my boyfriend, but I feel that he gives more importance to his \textbf{friends} than to me.
He takes me for granted, and he has done that many \textbf{times}.
He always disappoints me, which hurts a \textbf{lot}.
He doesn't understand me, especially when it comes to his \textbf{friends}.
He even disappointed me on my birthday.
I don't find him supportive anymore.
I feel so lonely because I have lacked \textbf{love} and importance from my family, lacked loyalty from my best \textbf{friends}, and now I’mIacking understanding from my boyfriend.
I don't know what action I should take or how I should treat him back for this.
Overall, I am really disappointed with my life and feel extremely lonely.
I truly need someone to understand me and care about me.

% matched lemmas: depression, friend, health, lot, love, situation, support, time, year
\end{textsample}
