\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t443\_human.txt}  \label{ex:f3_pos_007}
This New Year ’s Eve has been really rough leading up to it, and now ’s finally the day I ’ve been dreading.
I have BPD, \textbf{depression}, and \textbf{anxiety}, and through high school I was in and out of school ; slowly all the “ \textbf{friends} ” I made disappeared and left me behind.
So I don't have really any \textbf{friends}, two including my long-distance boyfriend.
He provides me a \textbf{lot} of comfort, but he ’s traveling and busy with \textbf{friends}, so it ’s been pretty quiet, and it sets me into panic.
I really tried to make plans with my \textbf{friend} to distract from this sadness and let go, but she would rather be going out with her other \textbf{friends}.
I can't remember the last \textbf{time} I felt carefree and was just having a blast and forgetting my \textbf{problems} for one day.
I feel so selfish for getting upset at those around me ; I hate to come across as “ woe is me ” and “ I have it so horrible ” when I know there are bigger \textbf{problems} out there.
It just feels so heavy on my heart ; :( I feel like a loser.
I 'm 19 ( 20 in May ), and growing up, I had such a picturesque imagination of how becoming a teenager would be … going out with \textbf{friends}, partying, laughing, living life to the fullest and I just feel so robbed of this experience I wanted so badly.
I know I 'm catastrophizing this whole \textbf{situation}, but I just wish I was somebody else for this day ; it hurts too much to be in my skin.
I know \textbf{lots} of people spend their New \textbf{Year} 's alone, and IM trying to be okay with it but im spiraling bad.
Sorry for any confusion in my rant, thank you for listening <3

% matched lemmas: anxiety, depression, friend, lot, problem, situation, time, year
\end{textsample}
