\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t918\_human.txt}  \label{ex:f3_pos_006}
I want to start off by saying I have mental \textbf{health} \textbf{issues} that probably make my thoughts and epiphany ’s more negative than anything else.
I am 25 \textbf{years} old now.
They say around that age your frontal lobe is pretty much a cake that has been baked.
You start to think differently about \textbf{things} and logic is more prevalent than ever.
Which to me brings a whole other set of challenges.
I ’ve realized that everything takes work.
And I mean everything.
You want your partner to apologize in a meaningful \textbf{way} verbally and reassure you that the \textbf{issue} will not persist?
Yeah that takes a seemingly endless trail of conversation and trial and error and you are supposed to feel fulfilled at the end.
You want people to treat you equally at work or treat you fairly?
Yeah that takes another rabbit hole of risk and setting boundaries ( more endless talking and explaining ).
You want to be successful financially?
Yeah you ’ll have to do more trail and error and putting yourself out there and keeping your head up despite rejection countless \textbf{times} or maybe even lose more money than you had to begin with.
You want to feel like you have free will and indulge in happiness if possible?
You will have to make \textbf{time} for it and it better be free if you haven't done the last step I just listed.
I cannot get past the \textbf{fact} that there is nothing effortlessly fulfilling and for YOU.
You have to “ force ” it.
I am so tired.
Just thinking of that makes me sleepy.
I just want one \textbf{thing} to work out eight minimal effort.
Just one \textbf{thing}.
I want at least one \textbf{thing} to just find me and regain my faith that life is beautiful.
Some \textbf{things} just find you.
A reason.
In my past I ’ve done a \textbf{lot} of substances.
Daily.
It did the trick until it created \textbf{problems} not even that could be my saving grace.
Much like everyone else that chooses that route.
It is short lived and it will kill you faster than brining you to peace unless we wanna argue that death is actually the best peace you can find on planet earth.
Thank you if you read this.
I wonder if others feel the same.

% matched lemmas: fact, health, issue, lot, problem, thing, time, way, year
\end{textsample}
