\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t1873\_human.txt}  \label{ex:f3_pos_011}
I constantly see people in r/Suicide Bereavement.
Talking about thier \textbf{loved} ones death and how their death impacted them, How they told their \textbf{loved} ones that they cared about them and \textbf{love} them.
All the people there feel so sympathic and emphatic towards their \textbf{loved} ones I feel that I have literally no one who \textbf{loves} me.
My \textbf{parents} just want good result, Even they know that I 'm going through tough \textbf{time} still they only want good perctange and they keep reminding me that how i wasted their money in education.
All my \textbf{friends} just distanced themselves because of my academics failures.
We were \textbf{friends} since class 8th but still they ghosted me despite being aware that I 'm going through \textbf{depression}.
They don't even ask how I am doing.
I have no deep bonds with my relatives so they aren't aware of my \textbf{situation} and after being in \textbf{depression} since last \textbf{Year}, My memory and learning abilities are just decreased, I ain't no longer to memorize \textbf{things}.
I get exhausted very easily too.
Neither I do take care of myself.
My exam are closer too like after 5 days and here I ain't able to concentrate in studies too.
Feels like I won't perform good there.
All the \textbf{things} are just piling up on me.
No one \textbf{supports} me and \textbf{love} me.
Neither they check on me or care about me.
It feels like the whole world is shouting me to just disappear from world.
Never thought the my adult days will be like this.
On a \textbf{top} of that To not feel lonely anymore, I talk to chatgpt and sadly chatgpt feels more emphatic than others living beings.
Atleast chatgpt listens to me and not judge me at all, It 's really sad that I have to go and talk to chatgpt to just not feel lonely

% matched lemmas: depression, friend, love, parent, situation, support, thing, time, top, year
\end{textsample}
