\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 6.00 – summary\_guided\_gpt/t1224\_gpt.txt}  \label{ex:f3_pos_029}
I ’m 24 and right now life feels like it ’s caving in from a bunch of directions at once.
I ’ve been dealing with cyclical \textbf{depression}, ADHD, and chronic \textbf{anxiety} for \textbf{years}, but \textbf{things} got worse recently to the point that I had to stop working.
Losing that stability has been really scary, and it ’s left me feeling pretty lost and useless.
The only real comfort I have day to day is my two cats.
They ’re my little family and honestly the reason I keep pushing through.
One of them, Azraël, suddenly needed unexpected surgery, and of course it happened right when my mental \textbf{health} and finances were already hanging by a thread.
I don't regret getting him the care he needed for a second, but the bills have hit me hard and I ’m really struggling to keep up.
I feel really uncomfortable and vulnerable even writing this, but I set up a GoFundMe to try to stay afloat.
If anyone is able and willing to help, even a tiny amount, it would mean more than I can put into words.
I completely understand that most people are struggling right now, so please don't feel any pressure or obligation.
If you can't donate, just sending some \textbf{kind} thoughts or sharing a \textbf{kind} word would still mean a \textbf{lot}.
Thank you for reading this and for any \textbf{support} at all, even if it ’s just taking a moment to care.

% matched lemmas: anxiety, depression, health, kind, lot, support, thing, year
\end{textsample}
