\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t1991\_human.txt}  \label{ex:f3_pos_020}
I know it ’s unhealthy and I need help but I swear feeling lonely and sad feels great sometimes.
Does anyone else get the shiver down their body? ( Mine is in my sides usually ) Sometimes I think about being lonely.
How I ’m 22 and I ’ve yet to find \textbf{love}, and how I don't think I will.
There are other \textbf{issues} in my life but \textbf{love} has always been the biggest struggle for me.
And sometimes I think about it so much that I can physically feel the sadness.
Am I addicted to it?
I don't really think so, but I ’d be lying if I said I was avoiding fixing myself.
It ’s like I don't want to put in the effort of finding \textbf{love} the hard \textbf{way}.
I tell myself certain \textbf{things} to keep myself here because all my life I ’ve just been the outcast.
In every \textbf{way}.
In more \textbf{ways} than just \textbf{love}.
I know it can't iust be me.
Also … a side tangent for anyone who cares.
I know 22 is still young but for me it ’s not.
Im not just single … I ’ve also never had a \textbf{relationship}.
The \textbf{pain} of seeing everyone around you find and fall out of \textbf{love} is a \textbf{lot} to bear.
I wish I could have breakups, I wish I had young \textbf{love}, I wish I could have experiences.
But the \textbf{fact} that no one even gives me the chance to fuck up in the first place just makes me feel terrible.
And it ’s been so long now that I ’m sitting here writing this, for no apparent reason.
I ’m not the only one who feels like this, I know it.
Honestly I just thought it ’d be neat to see what other people feel.
We may not be so different.

% matched lemmas: fact, issue, lot, love, pain, relationship, thing, way
\end{textsample}
