\begin{textsample}{POS Dim 3 – human – Score 8.00 – human/t1439\_human.txt}  \label{ex:f3_pos_001}
I ( 21f ) have been struggling with my life for \textbf{years} now.
I always knew I wanted to pass away before I made it to 30.
But what rlly pushed me want to sooner is the recent passing of my boyfriend.
We were together for over 3 \textbf{years} but we broke up in the beginning of the \textbf{year}.
Yes, I still call him my bf because we still deeply \textbf{loved} each other.
But during our \textbf{relationship}, he did \textbf{things} that still hurt me today and affects the \textbf{way} I see see myself.
His family have been supportive but they 're all upset with me rn bc they want to me a referee for their personal \textbf{situations}.
No one texts me first or ask how I 'm doing, I have to be the one.
I feel like I can't keep up with them and I try so hard not to mess up.
Any slip up I make, I feel like I just ruined it.
My \textbf{friends} don't text me unless I text them as well.
I have no car, no money, no job, and I don't have my own place either.
I have nothing going on for me.
My body feels like it 's shutting down and I have a \textbf{lot} of \textbf{health} \textbf{problems}.
I 'm physically exhausted, my emotions are all over the place, and I feel mentally insane.
I have borderline personality disorder. have better control of it but have days where I can't be calm.
My family and I don't see eye to eye and we all have a \textbf{lot} of \textbf{issues}.
Can't eat.
Can't sleep.
Can't relax.
I can't enjoy \textbf{things} that I used to.
I 'm trying but at what cost?
What 's the point?
It 's just me and that 's scary.

% matched lemmas: friend, health, issue, lot, love, problem, relationship, situation, thing, way, year
\end{textsample}
