\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 6.00 – summary\_guided\_gpt/t323\_gpt.txt}  \label{ex:f3_pos_026}
I ’m 20 and I feel like I ’ve been stuck in the same dark place for 3–4 \textbf{years} now.
The \textbf{depression} just never really went away.
I still have all these negative thoughts, I feel emotionally numb most of the \textbf{time}, and even my physical \textbf{health} has gotten worse.
I ’m tired all the \textbf{time}, and it feels like my body is just as exhausted as my mind.
What hurts the most is how alone I feel in all of this.
My family has never really given me the care or \textbf{support} I needed.
It ’s like my feelings don't matter, like I ’m just … there.
My best \textbf{friends}, the people I thought would always be there, abandoned me when I was at my lowest.
Now I don't really have any good \textbf{friends} left.
It feels like everyone just slowly drifted away when I needed them the most.
I ’m in a \textbf{relationship}, but even that makes me feel lonely.
My boyfriend always seems to prioritize his \textbf{friends} over me.
I feel taken for granted, like I ’m just an option.
He keeps disappointing me, even on days that should matter, like my birthday.
He doesn't really understand me, especially when it comes to how I feel about his friendships and how they make me feel so unimportant.
I don't know how I ’m supposed to respond to his behavior anymore.
Part of me wants to leave, but another part is scared of being even more alone.
I just wish I had someone who truly understood me and actually cared, someone who wouldn't make me feel like I ’m asking for too much just by wanting to be \textbf{loved} and prioritized.

% matched lemmas: depression, friend, health, love, relationship, support, time, year
\end{textsample}
