\begin{textsample}{POS Dim 3 – generic\_gpt – Score 3.00 – generic\_gpt/t1198\_gpt.txt}  \label{ex:f3_pos_032}
I don't really know how to talk about this in real life, so I ’m dumping it here instead.
Lately it feels like my life is happening behind glass.
I ’m “ around ” people a \textbf{lot} — coworkers, acquaintances, even family — but I still feel like I ’m on mute.
I go through the motions, smile, make small talk, crack a joke when it ’s expected, but it all feels like acting.
When I go home, it ’s like I disappear from the world and nobody notices.
What messes with my head is that on paper, I ’m not isolated.
I have people I could text, group chats I ’m technically part of, social media where people “ like ” my posts.
But when I actually think about who I could call at 2 a.m. if I was falling apart, the list is basically no one.
And I ’m not sure if that ’s because there really isn't anyone, or because I ’ve trained myself not to reach out.
I keep thinking there must be something wrong with me that other people can sense.
Like there ’s this invisible “ do not get close ” sign I ’m carrying around.
I watch other people form friendships so easily — they meet once and suddenly they ’re hanging out, going on trips, sharing inside jokes.
I can know someone for \textbf{years} and still feel like a background character in their life.
Sometimes I try to initiate \textbf{things} : suggest meeting up, send a message, comment on something.
Most of the \textbf{time} it fizzles, or we hang out once and it never becomes a regular \textbf{thing}.
After a while, it ’s hard not to take it personally.
I start overanalyzing everything I say, assuming I ’m boring or annoying or just … forgettable.
The worst part is how it affects how I see myself.
When you ’re alone with your thoughts all the \textbf{time}, they get louder.
I question whether I deserve close \textbf{relationships} at all, or if this is just how my life is going to be.
I don't really have a point to this.
I just needed to say it somewhere.

% matched lemmas: lot, relationship, thing, time, year
\end{textsample}
