\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 7.00 – summary\_guided\_gpt/t353\_gpt.txt}  \label{ex:f3_pos_021}
I don't even know where to start.
I feel completely trapped and alone.
I ’m married with kids and I ’m seriously considering divorce, but I have almost nothing.
I make about \$300 every two weeks, I have nowhere to go with my children, and I have untreated medical \textbf{issues} that make it hard to work, but also somehow I ’m “ not sick enough ” to qualify for disability.
It feels like I ’m stuck in this tiny, suffocating box with no doors.
For 12 \textbf{years} his \textbf{friends} and family have treated me like garbage.
They talk down to me, ignore me, or act like I ’m the \textbf{problem}, and he never, ever defends me.
Recently he literally yelled at me just for talking to one of his \textbf{friends}, then threw a can at me.
His \textbf{friends} said he “ did nothing wrong. ” He hasn't hit me, but he ’s punched holes in walls and doors.
I feel constantly on edge, waiting for the next outburst.
On \textbf{top} of that, he ’s been lying to everyone about our \textbf{relationship}.
He told his \textbf{friends} we had an “ open marriage ” and that it was my \textbf{idea}, and that it was basically all for my benefit.
In reality, he was cheating on me with multiple women, even when I was pregnant.
The “ open ” \textbf{thing} only came up so he wouldn't have to hide it anymore.
I only tried seeing someone myself last \textbf{year}, after he finally “ allowed ” it, and somehow his \textbf{friends} still blamed me.
I never really wanted to marry him.
I said as much back then, but my family approved of the marriage and \textbf{kind} of pushed it, even when I had my doubts.
Now here I am, \textbf{years} later, feeling like a burden to everyone, like I ruined my own life and my kids ’ lives.
I ’m severely depressed.
I don't have anyone I can really talk to in my real life.
I feel invisible, like my \textbf{pain} doesn't matter to anyone.
I don't even know what I ’m hoping for by posting this.
Maybe I just needed to say it somewhere.

% matched lemmas: friend, idea, issue, kind, pain, problem, relationship, thing, top, year
\end{textsample}
