\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t1771\_human.txt}  \label{ex:f3_pos_013}
I ( 25F ) don't really know how to comprehend this \textbf{situation} I 'm in.
My entire life basically blew up recently.
Firstly, my mental \textbf{health} went extremely downhill.
I had a huge episode of OCD or maybe \textbf{anxiety} (? ) that has completely taken all my joy away from me.
None of my hobbies appeal to me anymore.
And I have also considered"exiting".
Secondly, I just finished college and have somehow found myself a NEET with no prospects, mobility or social skills.
This makes everyday so difficult and torturous.
Now, the relevant aspect to this sub is that I 'm also feeling utterly lonely.
My few \textbf{friends} are either ( understandably ) busy or tired of \textbf{supporting} me.
Sometimes I even take the initiative to avoid them because I 'm ashamed of who I have become.
This is a big \textbf{problem} because I feel like I need people and want them around.
I get so sad when there 's no one to even talk to.
But how, on god 's green earth, do I reconcile the urgent need for company with the \textbf{fact} that I really need to work on myself to be worthy of such company?
How can I say I want people around me when everyone currently deserves better?
I think there is a loooong list of \textbf{things}.
Need to go to therapy at long last.
Need to get a job somehow.
Need to do a hundred more \textbf{things} probably..
I just... have so much to do, and I don't know how I 'll do it all alone.

% matched lemmas: anxiety, fact, friend, health, problem, situation, support, thing
\end{textsample}
