\begin{textsample}{POS Dim 3 – generic\_gpt – Score 3.00 – generic\_gpt/t1893\_gpt.txt}  \label{ex:f3_pos_033}
I don't really know how to talk about this in real life, so I ’m dumping it here.
Lately I ’ve had this weird feeling that I ’m both “ around people ” and somehow completely not *with* anyone.
I go to work, I respond to messages, I show up to \textbf{things} when I ’m invited, but it all feels like I ’m playing a character who ’s loosely based on me.
People laugh at my jokes, we talk about TV shows or work drama, and then I go home and it ’s like someone hits mute on my life.
The silence hits hardest right before bed.
That ’s when I notice I haven't had a single conversation all day where I felt genuinely understood, or even really seen.
It ’s not like I ’m isolated in the obvious way—no one would look at my life and say I ’m “ alone”—but I feel emotionally homeless a \textbf{lot} of the \textbf{time}.
I ’ve tried to fix it in different \textbf{ways}.
I ’ve overshared with acquaintances and then felt stupid and exposed.
I ’ve pulled back and tried to be “ low maintenance ” so I don't scare people away.
I ’ve joined group chats, Discord servers, hobby groups.
I ’m physically present but mentally pressed up against the glass, watching everyone else connect while I hover on the edges.
What messes with my head is the \textbf{idea} that if I disappeared, people would notice for a bit, maybe send a “ hey, where ’d you go? ” message, and then just…adjust.
I don't feel like anyone ’s “ person. ” I ’m just an optional extra.
I can't tell if the \textbf{problem} is me not letting people in, or people not really wanting to.
Or maybe I ’m just fundamentally hard to attach to and I ’m only now fully realizing it.

% matched lemmas: idea, lot, problem, thing, time, way
\end{textsample}
