\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t1481\_human.txt}  \label{ex:f3_pos_017}
Huge vent I ( 21f ) feel like there 's so point for me to fight for the life I want.
Nothing works out for me and I feel like I can't get a break.
The last few \textbf{years} have just been shitty but nothing rlly broke me apart until my boyfriend 's recent passing.
Our plans, our dreams, our nightly chocolate milks, and our morning cuddles, are all gone.
I don't have my dad 's \textbf{support} through this \textbf{time}.
My boyfriend 's family have all been supportive and encouraging.
I would \textbf{love} to move near them but my mom feels like I 'm replacing mt family with them ( she likes to twist my words around ).
I 've never had a good \textbf{relationship} with them and the events that happened this \textbf{year} and \textbf{years} before, have rlly put a strain in my \textbf{relationship} with them.
I also have Borderline Personality Disorder which makes it 10x harder for me and them to be on the same level.
I feel like I 'm a \textbf{problem}, I 'm horrible to be around, no one understands me, I feel mentally insane, alone, angry yet sad.
It just never ends and being home just adds so much on me..
I also got diagnosed with PCOS recently and like rlly?
I NEEDED that too?
I have arthritis everywhere in my body and it crushes my dream to be an artist bc of the \textbf{pain} in my hands.
There 's just so much more but I hate to sound whiny.
I just can't handle all of this on me and nothing is taking huge toll on me more than my boyfriends death.
I don't want to continue my life without him more than I already have.
I feel like I 'm suffocating in my own mental suffering..
I don't think it 's worth it to keep living with my insanity....

% matched lemmas: love, pain, problem, relationship, support, time, year
\end{textsample}
