\begin{textsample}{POS Dim 3 – generic\_gpt – Score 3.00 – generic\_gpt/t776\_gpt.txt}  \label{ex:f3_pos_031}
I don't really know how to say this without sounding dramatic, but I feel like I ’m disappearing while technically still being “ around ” people.
On paper, I ’m not isolated.
I have coworkers I talk to every day, family I text with sometimes, a few old \textbf{friends} I send memes to.
But none of it feels like it actually reaches me.
It ’s like everything is happening behind glass.
I can see people, hear them, laugh at the right moments, but there ’s no sense of being known or needed.
Most of my interactions feel like I ’m playing a character I ’ve built over the \textbf{years}.
I know what version of myself each person expects, and I just slide into that role automatically.
The “ funny coworker, ” the “ responsible one ” in the family, the “ good listener ” in group chats.
It works well enough that nobody suspects anything is wrong.
But when it ’s over and I ’m alone again, I feel this weird emptiness, like I ’ve just finished a performance and I ’m back in an empty theater.
What makes it worse is that I don't even know what the “ real ” version of me is anymore.
When I try to be more honest or vulnerable, it either comes out awkward or I immediately regret it and shut down.
I worry people will think I ’m too much, too needy, too negative.
So I keep everything on the surface and then feel resentful that nobody sees what ’s under it.
I also have this constant fear of being an inconvenience.
I ’ll type out a message asking someone to hang out and then delete it because I convince myself they ’re just being polite when they say we should meet up.
I wait for people to initiate plans, but then I ’m hurt when they don't.
It ’s like I ’m trapped in this loop of wanting connection but being too scared to actually reach for it.
Nights are the worst.
That ’s when the silence feels loud.
I scroll through social media, seeing people posting about \textbf{friends}, \textbf{relationships}, little everyday moments with others.
I know a \textbf{lot} of it is curated, but it still hits this raw nerve.
I start wondering if there ’s just something fundamentally off about me that makes people keep me at arm ’s length.
I don't know what I ’m expecting by writing this.
I just needed to put into words that I feel incredibly lonely, even when I ’m not technically alone.

% matched lemmas: friend, lot, relationship, year
\end{textsample}
