\begin{textsample}{POS Dim 3 – human – Score 6.00 – human/t1239\_human.txt}  \label{ex:f3_pos_019}
I 'm over thirty.
I 've began my gender transition back in 2023 and it was the best decision ever, self-hate and related mental \textbf{issues} are officially a \textbf{thing} of the past, but today several \textbf{issues} consume me.
For one the anti-trans international climate, I fear for my life every day.
On the other hand...
Severe loneliness.
I 've been single since 2017 and I can't take it anymore.
I 've been doing what every breathing human being says you have to do, I joined clubs, I went to therapy, I 've improved myself, I hit the gym regularly, I reinforced doing my hobbies, I 've met a \textbf{lot} of people and made \textbf{lots} of \textbf{friends} but...
Nothing.
Everyone around me has a special person, wife, husband, boyfriend or girlfriend, everyone BUT me.
Everyone ( who already are in years-long \textbf{relationships} ) just vomits the clichés of"\textbf{love} will find you when you least expect it!""\textbf{love} is just around the corner"Sorry but no, I 'm autistic of the introverted type, I 've walked \textbf{way} out of my legit comfort zone being more extroverted, I tried to engage more people I 'm interested in ( to no avail ), I 've also tried giving up and not looking for anyone and nothing...
What is the point of living if I 'm going to live every fucking day alone? \textbf{friends} can barely get \textbf{time} on their agendas to do stuff and honestly... with 9 \textbf{years} of singleness I...
I don't know what to do. i feel lonely to the point of becoming a reccurent thought that fuels suicidal thoughts...
I already requested my therapist to make the paperwork to get an appointment with a psychiatrist to see if I can combat \textbf{depression} but... pills and \textbf{friends} ain't enough...
Why does everyone else get to enjoy \textbf{love} but not me?
I legit try not to compare but literally, everyone around me...
I can't live like this

% matched lemmas: depression, friend, issue, lot, love, relationship, thing, time, way, year
\end{textsample}
