\begin{textsample}{POS Dim 3 – summary\_guided\_gpt – Score 6.00 – summary\_guided\_gpt/t1472\_gpt.txt}  \label{ex:f3_pos_030}
I ’m 30, live in rural western PA, financially stable, own my home, and I actually \textbf{love} my job as a field service tech.
On paper, I know I ’m in a good spot.
But I feel incredibly alone.
In 2020 I went through a really traumatic breakup.
My ex cheated on me, got pregnant, and told me I was the father.
I believed her, got attached to the \textbf{idea}, and then a DNA test proved I wasn't.
That whole \textbf{situation} wrecked me.
Since then I ’ve had serious trust \textbf{issues}.
I became bitter, angry, and honestly not a pleasant person to be around.
Because of that, I ended up losing my two best \textbf{friends}.
We had a falling out and they ’ve made it clear they want nothing to do with me anymore.
I ’ve tried to fix it, but they refuse to reconcile.
So now it ’s just…me.
Work and home.
That ’s my whole life.
Only in the last \textbf{year} have I started to feel ready to date again.
I ’ve gone on a few dates, but there was no real connection.
I struggle with severe social \textbf{anxiety}, and my job keeps me really busy, so meeting people is hard.
Online dating feels like shouting into the void.
In-person, I freeze up or overthink everything.
I ’m lonely as hell.
I see people my age getting married, having kids, going on trips with \textbf{friends}, and I feel this constant FOMO, like life is passing me by while I ’m stuck on the sidelines.
I just want a girlfriend, someone to share \textbf{things} with, to come home to, to feel like I ’m not doing all of this alone.
I don't really know what I ’m looking for by posting this.
Maybe I just needed to get it off my chest.

% matched lemmas: anxiety, friend, idea, issue, love, situation, thing, year
\end{textsample}
