\begin{textsample}{POS Dim 3 – generic\_gpt – Score 2.00 – generic\_gpt/t2251\_gpt.txt}  \label{ex:f3_pos_037}
I don't really know how to explain this to people in my life, so I ’m dumping it here instead.
I ’m surrounded by people but I feel like I ’m behind glass all the \textbf{time}.
I go to work, make small talk, even crack jokes, and everyone would probably describe me as “ fine ” or “ chill. ” But I go home and it ’s like everything goes silent inside my head except this heavy awareness that nobody really knows me, and I ’m not sure anyone wants to.
I ’ve had \textbf{friends}, \textbf{relationships}, all of that.
But even when I ’m physically with someone, I feel this weird distance, like I ’m playing a version of myself that ’s easier to digest.
I edit what I say so I don't sound too needy, too intense, too negative.
Then I end up feeling fake, but when I try to be more honest, people slowly drift away or get uncomfortable.
It ’s starting to feel like I ’m fundamentally out of sync with everyone else.
I watch people talk about their “ group ” or “ best \textbf{friend} ” or “ person ” and I can't even imagine what it ’s like to feel that secure with someone.
I ’ve moved around a \textbf{lot}, so there ’s no childhood \textbf{friend} who “ gets me, ” no long-term social circle.
Just a \textbf{lot} of people I used to know.
What scares me most is how normal this has started to feel.
I wake up, go through the motions, distract myself with screens until I ’m tired enough to sleep.
I tell myself it ’s not that bad, that I ’m used to it.
But every so often it hits me how much of my life I ’m spending feeling like this, and I don't really know what to do with that.

% matched lemmas: friend, lot, relationship, time
\end{textsample}
