\begin{textsample}{POS Dim 3 – human – Score 8.00 – human/t1371\_human.txt}  \label{ex:f3_pos_002}
The first \textbf{time} I ever felt in \textbf{love}, it was someone I met when I was 12.
Even now 20 \textbf{years} later, I think about him and how much influence that one \textbf{year} had on me. \textbf{Love} is one of the most fulfilling emotions in my life.
When I look at the life that I ’ve built for myself, I ’m proud of how much I ’ve pulled through.
My life has everything I could possibly ask for, it ’s damn near perfect.
I was able to buy myself a house even though I just make a couple dollars above minimum wage, I ’m still \textbf{friends} with people from childhood and all of them are genuinely good people, I have a stable career field that is in line with my values and needs.
I have a \textbf{lot} of \textbf{health} \textbf{problems}, but I have the will to improve my \textbf{health} as much as I can.
Also, if it wasn't for my \textbf{health} \textbf{problems}, I would be in \textbf{top} shape with the amount of effort I put in.
The only \textbf{thing} I don't have is a romantic partner.
It makes me severely depressed.
I feel like nothing helps.
I ’ve done intensive outpatient for \textbf{depression}.
I will make \textbf{time} to do activities that I enjoy, prioritize spending \textbf{time} with \textbf{friends}.
Practice DBT skills.
Even after a \textbf{lot} of therapy sessions, my therapist \textbf{kind} of came down to the conclusion that it doesn't appear that I ’m imbalanced in some other area of my life causing me to be this sad about not having romantic partner.
But my instinctual emotional need for romantic companionship is just really strong.
I hate it.
I want it to end.
I want it to stop.
I can't stand it.
I literally keep trying to lean into other \textbf{things} to make up for how much this hurts me, but it doesn't work.
I don't know what to do with myself.
I don't know if anybody has some crazy \textbf{ideas} that I haven't considered.

% matched lemmas: depression, friend, health, idea, kind, lot, love, problem, thing, time, top, year
\end{textsample}
